### 2016-04-23 paper/main.tex
structure grows

\documentclass[draft,oneside]{scrartcl}

\usepackage[utf8]{inputenc}

\usepackage{epigraph}
\usepackage[autostyle,german=guillemets]{csquotes}
\usepackage[ngerman, english]{babel}
\usepackage[style=numeric,backend=biber]{biblatex}

\addbibresource{bibliography.bib}

\begin{document}

\setlength{\epigraphwidth}{0.7\textwidth}
\setquotestyle{german}

\title{A \emph{Grimm} idea}
\subtitle{Exploring graphs with pebbles}
\author{Christoph Welzel}
\maketitle

\begin{abstract}
  In this paper we re-present and explain an approach on exploring large
  undirected graphs with the help of markers, so called pebbles, for vertices.
  We focus on the central ideas of this approach and explain why it is possible
  to traverse any graph with $n$ vertices with $\Theta(\log \log n)$ pebbles
  and the same amount of memory.
\end{abstract}

\epigraph{\enquote{Aber, Bruder Wichsstiefel, wo hinaus geht der Weg?} %
  \enquote{Ich weiß es nicht}, antwortete der Jäger, %
  \enquote{ich habe mich in dem Wald verirrt.}}%
  {\emph{Die Stiefel von Büffelleder}\\Brüder Grimm}
\section{Introduction}
Traversing large graphs is an interesting challenge. In times of the internet
web crawlers have to traverse immense graphs but also regarding complexity
theory this is an interesting problem. First we will informally introduce two
complexity classes to illustrate the importance of graph traversal from a
complexity point of view: $L$ as the class of problems that can be solved by
a deterministic Turing machine with additional memory of logarithmic amount
of the input. And $SL$ as the class of problems that can be solved with the
same space requirements but by a non-deterministic symmetrical Turing machine,
where symmetrical means that for every computation step of the Turing machine
there is a computation step to undo the previous one. As it turns out checking
if two vertices $s$ and $t$ are connected in an undirected graph is a problem
that is complete for $SL$. This problem is often refered to as
$\mathrm{USTCON}$ and \citeauthor{logspacealg} showed in \cite{logspacealg}
that $\mathrm{USTCON}\in L$ which collapsed $SL$ into $L$, hence $SL = L$.
In the following we will present the results from \cite{pebbles} where another
mechanism of graph exploration is used: with the use of pebbles which are small
pieces of memory that can be dropped on and collected from the vertex the
agent currently traverses it is possible to traverse a graph with $n$ vertices
with $\mathcal{O}(\log\log n)$ memory and the same amount of pebbles.
Furthermore we will explain why there is no smaller amount of memory or pebbles
to generally obtain the same guarantee to traverse all $n$ vertices.

\epigraph{Und als der volle Mond aufgestiegen war, so nahm Hänsel sein %
Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten wie %
neu geschlagene Batzen und zeigten ihnen den Weg.}%
{\emph{Hänsel und Gretel}\\Brüder Grimm}
\section{Pebbel-Machines}

\setquotestyle{english}
\printbibliography
\end{document}

### 2016-04-26 paper/main.tex
started writing up

@@
 \usepackage[style=numeric,backend=biber]{biblatex}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{todonotes}
 
 \addbibresource{bibliography.bib}
+
+\DeclareMathOperator{\din}{\delta_{\mathit{in}}}
+\DeclareMathOperator{\dout}{\delta_{\mathit{out}}}
 
@@
 
-\epigraph{\enquote{Aber, Bruder Wichsstiefel, wo hinaus geht der Weg?} %
-  \enquote{Ich weiß es nicht}, antwortete der Jäger, %
-  \enquote{ich habe mich in dem Wald verirrt.}}%
-  {\emph{Die Stiefel von Büffelleder}\\Brüder Grimm}
+% \epigraph{\enquote{Aber, Bruder Wichsstiefel, wo hinaus geht der Weg?} %
+%   \enquote{Ich weiß es nicht}, antwortete der Jäger, %
+%   \enquote{ich habe mich in dem Wald verirrt.}}%
+%   {\emph{Die Stiefel von Büffelleder}\\Brüder Grimm}
+
+\epigraph{Und als der volle Mond aufgestiegen war, so nahm Hänsel sein %
+Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten %
+wie neu geschlagene Batzen und zeigten ihnen den Weg.}%
+{\emph{Hänsel und Gretel}\\Brüder Grimm}
+
+\setquotestyle{english}
 \section{Introduction}
@@
 mechanism of graph exploration is used: with the use of pebbles which are small
-pieces of memory that can be dropped on and collected from the vertex the
-agent currently traverses it is possible to traverse a graph with $n$ vertices
-with $\mathcal{O}(\log\log n)$ memory and the same amount of pebbles.
-Furthermore we will explain why there is no smaller amount of memory or pebbles
-to generally obtain the same guarantee to traverse all $n$ vertices.
+pieces of memory that can be dropped on and collected from the vertex as an
+agent traverses the graph. As we will show it is possible to traverse a graph
+with $n$ vertices with $\mathcal{O}(\log\log n)$ memory and the same amount of
+pebbles. Furthermore we will explain why there is no smaller amount of memory
+or pebbles to generally obtain the same guarantee to traverse all $n$ vertices.
 
-\epigraph{Und als der volle Mond aufgestiegen war, so nahm Hänsel sein %
-Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten wie %
-neu geschlagene Batzen und zeigten ihnen den Weg.}%
-{\emph{Hänsel und Gretel}\\Brüder Grimm}
-\section{Pebbel-Machines}
+\section{Preliminaries}
+For the course of this paper we assume the following: Firstly, the vertices can
+not be distinguished by the traversing agent. But as the agent moves on a
+vertex it can compute its degree. Secondly, the edges attached to the vertex
+can be locally distinguished and are enumerated with the indices
+$\left\{0,\dots,d_{v}-1\right\}$ where $d_{v}$ denotes the degree of the vertex
+$v$. We refer to the \enquote{index} of the edge as its \emph{port}. Note that
+every edge thus has two different ports and furthermore that there is no
+relation between the ports is assumed. Additionally the degree of the
+considered graphs are assumed to be limited by a constant $\Delta$.
+
+\section{Pebble machines}
+We are now ready to introduce the model of pebble machines formally. It closely
+follows the notion of Turing machines but adds mechanisms to model the
+movements of the agent. The presented model of pebble machines thus have
+\begin{enumerate}
+  \item a finite set of states $Q$
+  \item a finite set of final states $F\subseteq Q$
+  \item a finite set of distinguishable pebbles $P$
+  \item a length of the used memory tape $m$
+  \item a computation function $\delta$
+  \item a function that describes the movement onto a vertex
+    $\din$
+  \item a function that describes the leaving of a vertex $\dout$
+  \item an inital state $q_{0}$
+\end{enumerate}
+where formally the computation function models the behaviour of the pebble
+machine as follows:
+\begin{equation*}
+  \delta\colon (Q\setminus F)\times\left\{0,1\right\}\rightarrow
+  Q\times\left\{0,1\right\}\times\left\{L,R\right\}
+\end{equation*}
+with the typical understanding of the computation of a Turing machine.
+As an agent traverses a vertex it is aware of the pebbles it carries
+around, it observes the set of pebbles on the vertex and the degree of the
+vertex and it furthermore aware of the port that it entered through.
+Thus we use
+\begin{equation*}
+  \din\colon Q\times 2^{P}\times 2^{P}\times
+  \left\{0,\dots,\Delta - 1\right\}\times\left\{0,\dots,\Delta - 1\right\}
+  \rightarrow Q
+\end{equation*}
+to model this behaviour. And finally as the agent leaves a vertex it leaves
+a set of pebbles behind, picks up another set and chooses the port it leaves
+through. We choose to model this behaviour as
+\begin{equation*}
+  \dout\colon Q
+  \rightarrow 2^{P}\times 2^{P}\times \left\{0,\dots,\Delta - 1\right\}
+\end{equation*}
+Of course we also demand consistency of the pebbles, i.e. that if the agent
+carried $P_{1}\subseteq P$ and found $P_{2}\subseteq P$ it is necessary that
+$P_{1}$ and $P_{2}$ are disjoint and furthermore that if the agent leaves
+carrying $P'_{1}$ and leaving $P'_{2}$ behind those sets are disjoint and
+$P_{1}\cup P_{2} = P'_{1}\cup P'_{2}$.
+
+In order to describe the movement of an agent we introduce the notion of an
+exploration sequence as $e_{0}, e_{1},\dots$ which models relative movements
+as follows. We use a sequence of variables $l_{0},l_{1},\dots$ which denotes
+the port a vertex was entered through. And the next vertex is determined as the
+one connected to the port $(l_{i} + e_{i}) \mod d_{v_{i}}$. We define
+$l_{0} = 0$ and the notion $(e_{0},\dots,e_{k})^{\ast}$ for periodic sequences.
+It can be shown that a periodic sequence produces a closed walk through a
+graph. The proof for this relies on the finiteness of the graph and
+\todo{argue why this is a closed walk}
+
+From the result of \cite{logspacealg} which showed that there is a
+$\mathcal{O}(\log n)$ algorithm to solve $\mathrm{USTCON}$ and which precisely
+states the following:
 

### 2016-04-29 paper/main.tex
added further stuff

@@
 \end{abstract}
-
-% \epigraph{\enquote{Aber, Bruder Wichsstiefel, wo hinaus geht der Weg?} %
-%   \enquote{Ich weiß es nicht}, antwortete der Jäger, %
-%   \enquote{ich habe mich in dem Wald verirrt.}}%
-%   {\emph{Die Stiefel von Büffelleder}\\Brüder Grimm}
 
@@
 relation between the ports is assumed. Additionally the degree of the
-considered graphs are assumed to be limited by a constant $\Delta$.
+considered graphs are assumed to be limited by a constant $\Delta$ and that
+there are only a finite amount of vertices.
 
@@
 It can be shown that a periodic sequence produces a closed walk through a
-graph. The proof for this relies on the finiteness of the graph and
-\todo{argue why this is a closed walk}
+graph. Therefore we argue that there is only a finite amount of triples of the
+form $(v,l,i)$ exists where currently the agent is on vertex $v$, entered this
+vertex through port $l$ and is currently at index $i$ of the exploration
+sequence. For two triples $(v',l',i')$ and $(v'',l'',i'')$ that both lead to
+$(v,l,i)$ it is easy to see, that $(v',l',i') = (v'',l'',i'')$. Thus, for every
+triple there is a unique predecessor and successor which implies due to the
+finiteness of the triples $(v,l,i)$ and that the agent moves infinitely it
+follows that the first triple has to be valid infinitly often. This means a
+periodic exploration sequence yields a closed walk. \todo{maybe enclose in
+proof environment}
 
-From the result of \cite{logspacealg} which showed that there is a
-$\mathcal{O}(\log n)$ algorithm to solve $\mathrm{USTCON}$ and which precisely
-states the following:
+One result of \cite{logspacealg} states: 
+\todo{add theorem boxes and definition boxes}
+
+There is an algorithm $M\in L$ which produces a universal exploration sequence
+for every regular graph with $n$ vertices.
+
+From which we can conclude very easily the following Lemma which produces a
+universal exploration sequence
 

### 2016-04-29 paper/main.tex
started proof on of M' (should consider throwing it out)

@@
 
+\newtheorem{thm}{Theorem}
+\newtheorem{lem}{Lemma}
+
 \addbibresource{bibliography.bib}
@@
 \DeclareMathOperator{\dout}{\delta_{\mathit{out}}}
+\DeclareMathOperator{\Tid}{T_{\text{id}}}
+\DeclareMathOperator{\Tsteps}{T_{\text{steps}}}
+\DeclareMathOperator{\Twalk}{T_{\text{walk}}}
+\DeclareMathOperator{\Thead}{T_{\text{head}}}
 
@@
 It can be shown that a periodic sequence produces a closed walk through a
-graph. Therefore we argue that there is only a finite amount of triples of the
-form $(v,l,i)$ exists where currently the agent is on vertex $v$, entered this
-vertex through port $l$ and is currently at index $i$ of the exploration
+graph.
+\begin{proof}
+  We argue that there is only a finite amount of triples of the
+  form $(v,l,i)$ where currently the agent is on vertex $v$, entered
+  this vertex through port $l$ and is currently at index $i$ of the exploration
   sequence. For two triples $(v',l',i')$ and $(v'',l'',i'')$ that both lead to
-$(v,l,i)$ it is easy to see, that $(v',l',i') = (v'',l'',i'')$. Thus, for every
-triple there is a unique predecessor and successor which implies due to the
-finiteness of the triples $(v,l,i)$ and that the agent moves infinitely it
-follows that the first triple has to be valid infinitly often. This means a
-periodic exploration sequence yields a closed walk. \todo{maybe enclose in
-proof environment}
+  $(v,l,i)$ it is easy to see, that $(v',l',i') = (v'',l'',i'')$. Thus, for
+  every triple there is a unique predecessor and successor which implies due to
+  the finiteness of the triples $(v,l,i)$ and that the agent moves infinitely
+  it follows that the first triple has to be valid infinitly often. This means
+  a periodic exploration sequence yields a closed walk.
+\end{proof}
 
-One result of \cite{logspacealg} states: 
-\todo{add theorem boxes and definition boxes}
-
+From the following result of \cite{logspacealg} we present how we can obtain
+an $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine that finds a closed
+walk of at least $n$ distinct vertices in any graph with bounded degree.
+\begin{thm}
+  \label{thm:logalg}
 There is an algorithm $M\in L$ which produces a universal exploration sequence
 for every regular graph with $n$ vertices.
+\end{thm}
+First we argue that we can use this algorithm to find a universal exploration
+sequence of the form $e=(e_{0},\dots,e_{k})^{\ast}$ that traverses $n$ distinct
+vertices for any 3-regular graph and requires only $\mathcal{O}(\log n)$
+memory. Therefore we rely on the traversal sequence of $M$ from Theorem
+\ref{thm:logalg} and take from that the first $k:=3n\cdot c$ indices where
+$c$ denotes the number of configurations of $M$. We can now be assured that
+$e$ actually is a universal traversal sequence for any 3-regular graph because
+otherwise $M$ would have already looped in a strict subset of vertices of some
+3-regular graph. This contradicts that $M$ produces a universal exploration
+sequence for any graph with $n$ vertices.
 
-From which we can conclude very easily the following Lemma which produces a
-universal exploration sequence
+We can now find the $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine we
+are looking for.
+\begin{thm}
+  \label{thm:pebblewalk}
+  There is a $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine which
+  explores every given graph $G$ with bounded degree $\Delta$ either completly
+  or at least loops on $n$ distinct vertices.
+\end{thm}
+\begin{proof}
+  The main idea is to use the adapted algorithm $A$ to find for an
+  universal exploration sequence for a 3-regular graph from above. Therefore
+  we take $G$ and transform it to a 3-regular graph on which $A$ finds the
+  corresponding universal exploration sequence. The transformation replaces
+  any node $v$ with degree $d$ by $3d$ nodes which then form a circle where
+  every nodes has degree $3$. The edges of $v$ are moved to nodes in the
+  circle. Specifically the edge with port $i$ is replaced by 3 edges which are
+  attached to $(v,i), (v,i+d), (v,i+2d)$. (Note that the other
+  vertex attached to the edge is replaced by the same construction and therfore
+  offers enough ports for the newly introduced edges.) The following picture
+  illustrates this construction:\todo{add picture}
+
+  This simulation yields at most $3\Delta n^{2}$ many nodes and can be emulated
+  with $\mathcal{O}(1)$ many memory space since it is only needed to store
+  the second component of the inserted nodes which is bounded by $3\Delta$.
+  Furthermore $A$ can be run on this constructed Graph and only needs
+  $\mathcal{0}(\log n)$ space since $\mathcal{O}(\log(3\Delta n^{2})) =
+  \mathcal{O}(\log(3) + \log(\Delta) + 2\log(n)) = \mathcal{O}(\log n)$.
+  Which yields the required $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble
+  machine.
+\end{proof}
+
+In order to obtain the desired boundary of $\log\log n$ space and $\log\log n$
+pebbles we show that a pebble machine can be simulated by storing its tape
+content by pebbles that are placed on a closed walk.
+\begin{thm}
+  For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by
+  a $(cs,p + c,m)$ pebble machine that simulates the walk of $M$ or explores
+  $G$.
+\end{thm}
+\begin{proof}
+  The main idea of this simulation is to store the tape of $M$ by pebbles
+  placed on a closed walk in the graph. We show that every node on this closed
+  walk can be given an index and a pebble placed on a node represents the
+  binary representation of the index as the content of $M$'s tape. Again we
+  refer to the following picture for illustration: \todo{add picture}
+  We will first introduce the algorithms used to implement the simulation and
+  afterwards we will argue why this simulation respects the given space
+  boundarys.  Let $M_{\text{Walk}}$ be a pebble machine that yields a closed
+  walk on $G$. (Such a pebble machine exists due to Theorem
+  \ref{thm:pebblewalk}.) In order to manage the simulation we use some
+  variables: $\Tid, \Tsteps, \Twalk, \Thead$ where $\Tid$ is used to identify
+  the index of a vertex on the walk of $M_{\text{Walk}}$, $\Twalk$ is the tape
+  content of $M_{\text{Walk}}$ which can therefore be restarted by setting
+  $\Twalk$ to 0, $\Tsteps$ counts the number of steps taken by
+  $M_{\text{Walk}}$, and $\Thead$ stores where $M$'s head is positioned.
+  Furthermore we need some pebbles to mark certain vertices of the closed walk:
+  $p_{\text{start}}, p_{\text{tmp}}, p_{\text{next}}$ and additionally the
+  pebbles that are placed on the walk to store $M$'s tape content
+  $P_{M} = \left\{p_{1},p_{2},\dots\right\}$.
+  Now the different procedures used for the simulation can be presented:
+  \begin{description}
+    \item[Step():] Simulates on step according to $M_{\text{Walk}}$ and
+      increases $\Tsteps$.
+    \item[FindPebble($p_{i}$):] Executes \emph{Step()} until the pebble $p_{i}$
+      is observed.
+    \item[Restart():] Goes to the beginning of the closed walk by
+      \emph{FindPebble($p_{\text{start}}$)} and sets $\Tsteps,\Tid,\Twalk$ to 0
+    \item[NextDistinctVertex()] Finds the next distinct vertex of the walk. If
+      there are no more vertices on the walk (we will see that this can be
+      computed since the used walk is of constant size) it simply executes
+      \emph{Restart()}. Otherwise it does one step and drops $p_{\text{tmp}}$
+      to mark this vertex. It then stores the current amount of steps as well
+      as the current state of $M_{\text{Walk}}$ (introducing two auxiliary
+      variables $\Tsteps',\Twalk'$). It then restarts $M_{\text{Walk}}$ and
+      moves to $p_{\text{tmp}}$ by \emph{FindPebble($p_{\text{tmp}}$)}. If
+      it used the same amount of steps as stored in $\Tsteps'$ then this is the
+      first occurence of the vertex in the closed walk and therefore it is a
+      new distinct vertex and $\Tid$ can be increased. Otherwise the context of
+      $M_{\text{Walk}}$ is restored and the next vertex is checked.
+    \item[GetPebbleId($p_{i}$):] Finds the index of the vertex $p_{i}$ is
+      placed on. Beginning from the start of the closed walk
+      (found by executing \emph{Restart()} it moves along distinct vertices
+      (by using \emph{NextDistinctVertex()}) and returns $\Tid$ as soon as
+      $p_{i}$ is observed.
+    \item[PutPebbleAtId($p_{i},\mathit{id}$):] Puts pebble $p_i$ at a certain
+      index. First it picks up $p_{i}$ and restarts the walk. Then it executes
+      $\mathit{id}$ times \emph{NextDistinctVertex()} and drops $p_{i}$.
+    \item[ReadBit():] Reads the $\Thead$'s bit of $M$'s tape. $\Thead$ gives
+      the position of the bit that should be read. The walk of
+      $M_{\text{walk}}$ is only considered to a certain length (as we will see
+      later) which also determines the blocks in which $M$'s tape is separated.
+      (The index of a vertex is used to encode one block.) Therefore we can use
+      this length of the walk which pebble encodes the corresponding block
+      which is obtained.  And then the actually needed bit of the index is
+      returned.
+    \item[WriteBit($b$):] Writes $b$ to $\Thead$'s bit of $M$'s tape. First
+      $\Thead$'s bit is obtained (by \emph{ReadBit()}). And if it is actually
+      changed the corresponding pebble is moved to store the new value of the
+      memory cell. Thus, if the bit is flipped from 0 to 1 we increase $p_{i}$
+      where $i$ is the encoded memory cell index by $2^{\Thead\bmod m_{1}}$
+      where $m_{1}$ encodes the length of the considered walk. And if the bit
+      is flipped from 1 to 0 we decrease $p_{i}$'s index by
+      $2^{\Thead\bmod m_{1}}$.
+  \end{description}
+  These are the procedures used to simulate $M$. We will now discuss the space
+  boundarys and afterwards conclude with showing how the simulation actually
+  operates. Recall that $M$ is a $(s,p,2m)$ pebble machine. For the simulating
+
+\end{proof}
 

### 2016-04-30 paper/main.tex
finished first version of simulation proof

@@
   every triple there is a unique predecessor and successor which implies due to
-  the finiteness of the triples $(v,l,i)$ and that the agent moves infinitely
-  it follows that the first triple has to be valid infinitly often. This means
-  a periodic exploration sequence yields a closed walk.
+  the finiteness of the triples $(v,l,i)$ and because the agent moves
+  infinitely that the first triple has to be valid infinitly often.
+  This means a periodic exploration sequence yields a closed walk.
 \end{proof}
@@
   \mathcal{O}(\log(3) + \log(\Delta) + 2\log(n)) = \mathcal{O}(\log n)$.
-  Which yields the required $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble
+  Which yields the desired $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble
   machine.
@@
 \begin{thm}
+  \label{thm:simulation}
   For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by
@@
 \begin{proof}
+  In this proof we will focus on the simulation and we leave out a thorough
+  analysis of the space requirements of the simulation since it is rather
+  technical but does not add a lot to the idea. Nevertheless we encourage
+  interested readers to see \cite{pebbles} for the details.
+
   The main idea of this simulation is to store the tape of $M$ by pebbles
@@
   walk can be given an index and a pebble placed on a node represents the
-  binary representation of the index as the content of $M$'s tape. Again we
-  refer to the following picture for illustration: \todo{add picture}
-  We will first introduce the algorithms used to implement the simulation and
-  afterwards we will argue why this simulation respects the given space
-  boundarys.  Let $M_{\text{Walk}}$ be a pebble machine that yields a closed
-  walk on $G$. (Such a pebble machine exists due to Theorem
-  \ref{thm:pebblewalk}.) In order to manage the simulation we use some
+  binary representation of the index as the content of $M$'s tape. Therefore we
+  first off introduce a variable $m_{1}$ which is dependent on the simulated
+  pebble machine $M$ (further requirements on $m_{1}$ and how to obtain it
+  can be seen in \cite{pebbles}). We will now take the tape of $M$ and separate
+  it into $2m/m_{1}$ blocks of the size $m_{1}$. And each of these blocks is
+  encoded by the placement of a pebble on a closed walk $\omega$. So we use
+  pebble $p_{0}$ to encode the first $m_{1}$ bits, the pebble $p_{1}$ used to
+  encode the next $m_{1}$ bits and so forth. Thus, the pebble $p_{i}$ encodes
+  the bits $im_{1},\dots,(i+1)m_{1}-1$. It is therefore necessary that every
+  pebble can encode $2^{m_1}$ different states. Therefore we use a closed walk
+  $\omega$ which visits at least $2^{m_1}$ distinct vertices yielding $2^{m_1}$
+  many \enquote{states} for each pebble (by its placement on this closed walk).
+  Therefore we can use the binary representation of the indices of the nodes
+  on which the pebbles are placed as the content of the encoded memory block.
+  The following picture gives an illustration of this.\todo{add picture}
+
+  In the following we show how this simulation can be managed.
+  Let $M_{\text{Walk}}$ be pebble machine that yields $\omega$ on $G$.
+  $M_{\text{Walk}}$ can be implemented as $(\mathcal{O}(1),0,\mathcal{m_1})$
+  pebble machine by Theorem \ref{thm:pebblewalk}.
+  In order to manage the simulation we use some
   variables: $\Tid, \Tsteps, \Twalk, \Thead$ where $\Tid$ is used to identify
@@
   pebbles that are placed on the walk to store $M$'s tape content
-  $P_{M} = \left\{p_{1},p_{2},\dots\right\}$.
+  $P_{M} = \left\{p_{0},p_{1},\dots,p_{2m/m_{1}-1}\right\}$.
   Now the different procedures used for the simulation can be presented:
@@
     \item[NextDistinctVertex()] Finds the next distinct vertex of the walk. If
-      there are no more vertices on the walk (we will see that this can be
-      computed since the used walk is of constant size) it simply executes
+      there are no more vertices on the walk (which means that already
+      $2^{m_1}$ distinct vertices have been traversed; the number of distinct
+      vertices on the walk is given by $\Tid$) it simply executes
       \emph{Restart()}. Otherwise it does one step and drops $p_{\text{tmp}}$
@@
     \item[ReadBit():] Reads the $\Thead$'s bit of $M$'s tape. $\Thead$ gives
-      the position of the bit that should be read. The walk of
-      $M_{\text{walk}}$ is only considered to a certain length (as we will see
-      later) which also determines the blocks in which $M$'s tape is separated.
-      (The index of a vertex is used to encode one block.) Therefore we can use
-      this length of the walk which pebble encodes the corresponding block
-      which is obtained.  And then the actually needed bit of the index is
-      returned.
+      the position of the bit that should be read. Therefore the pebble
+      $p_{\lfloor \Thead/m_{1}\rfloor}$ encodes this bit. The \enquote{state}
+      of this pebble can be obtained with
+      \emph{GetPebbleId($p_{\lfloor \Thead/m_{1}\rfloor}$)} and from the
+      encoded value the $(\Thead\mod m_{1})$-th bit is the one under $M$'s
+      head.
     \item[WriteBit($b$):] Writes $b$ to $\Thead$'s bit of $M$'s tape. First
-      $\Thead$'s bit is obtained (by \emph{ReadBit()}). And if it is actually
-      changed the corresponding pebble is moved to store the new value of the
-      memory cell. Thus, if the bit is flipped from 0 to 1 we increase $p_{i}$
-      where $i$ is the encoded memory cell index by $2^{\Thead\bmod m_{1}}$
-      where $m_{1}$ encodes the length of the considered walk. And if the bit
-      is flipped from 1 to 0 we decrease $p_{i}$'s index by
-      $2^{\Thead\bmod m_{1}}$.
+      $\Thead$'s bit is obtained (by \emph{ReadBit()}). Additionally we
+      identify the encoding pebble $p_{i}$ as already seen for
+      \emph{ReadBit()} and let be $j = \Thead\mod m_{1}$ the offset of the bit
+      within the memory block. If the bit actually flips the value of the
+      memory block changes by $2^j$ (for the flip from 1 to 0 the value
+      decreases and for the flip from 0 to 1 it increases). Therefore $p_{i}$
+      is put either $2^j$ indices up or down which can be easily done by using
+      \emph{PutPebbleAtId(\dots)}.
   \end{description}
-  These are the procedures used to simulate $M$. We will now discuss the space
-  boundarys and afterwards conclude with showing how the simulation actually
-  operates. Recall that $M$ is a $(s,p,2m)$ pebble machine. For the simulating
-
+  These are the procedures used to simulate $M$'s tape. Furthermore we keep
+  $M$'s states in the state space of the simulation. To conclude the simulation
+  we have to consider what happens if $M$ moves from the current vertex to
+  another vertex $v'$. Then the pebble $p_{tmp}$ is dropped on $v'$ and the
+  pebbles are moved to the same index they have in $\omega$ for a new closed
+  walk $\omega'$ (obtained by $M_{\text{Walk}}$ simulated starting in $v'$;
+  this walk is also ensured to have at least $2^{m_1}$ distinct vertices).
 \end{proof}
+As Theorem \ref{thm:pebblewalk} yields a $(c,0,c\cdot\log n)$ pebble machine
+that explores a given graph we can now repeatedly apply the simulation
+from Theorem \ref{thm:simulation} (precisely $\log\log n$ times) and end up
+with a $(c'^{\log\log n}\cdot c, \log\log n\cdot c',
+\frac{c}{2^{\log\log n}}\log n) =
+(c'^{\log\log n}\cdot c, \log\log n\cdot c', c)$ pebble machine exploring the
+graph.
 

### 2016-04-30 paper/main.tex
all the proofs, conclusion and then we have to get rid of stuff

@@
 \usepackage{todonotes}
+\usepackage{mdframed}
 
@@
 
+\section{Graph exploration}
 In order to describe the movement of an agent we introduce the notion of an
@@
 
+\section{Barriers}
+In the following we will discuss the limits of the exploration approach with
+pebbles. Specifically, we will argue that we can construct 3-regular graphs
+that any agent with $p$ pebbles cannot traverse. Such graphs are called
+$p$-barriers.
+Note that connecting a 3-regular graph might violate its 3-regularity.
+Therefore we rely on having a distinguishable edge $e$ in the 3-regular graph
+which we can delete to connect the vertices $e$ connected to the
+\enquote{outside}. This preserves the 3-regularity.
+With a given $p$-barrier $H$ we can construct a trap for an agent with $p$
+pebbles as follows:
+\todo{add picture}
+
+The construction of barriers is inductively and therefore requires that the
+base case can be constructed directly. Fortunately Theorem 4 in \cite{0barrier}
+yields a graph which can be adapted by connecting two identical copies to a
+0-barrier (for details we refer again to \cite{pebbles}). With this in mind we
+introduce a gadget construction for a given $r$-barrier $B$ as it can be seen
+in figure \ref{fig:gadget}\todo{add figure}. Replacing edges of a graph with
+such gadgets enforces, in a sense, \enquote{locality} of pebbles. We call
+the verices that are connected by the gadget macro-vertices and if a $r+1$
+pebble machine stands on a macro vertex we can safely be assured that all
+pebbles are either carried by the agent or are placed within the adjacent
+gadgets because otherwise the agent has left a pebble across of an $r$-barrier
+and crossed the barrier with $r$ pebbles contradicting that it is in fact an
+$r$-barrier. This observation can be used to construct an $r$-barrier given
+a $(r-1)$-barrier is known.
+\begin{thm}
+  With a given $(r-1)$-barrier for an agent $A$ a $r$-barrier can be
+  constructed.
+\end{thm}
+\begin{proof}
+  We will present only the key ideas of this proof since it involves a
+  few technicalities which do not add much to the general understanding
+  and are therefore omitted. Given a subset of pebbles of cardinality $r$
+  we can construct an $r$-barrier for this subset by using the given
+  $(r-1)$-barrier to enforce locality of the pebbles. We can then project
+  $A$'s behaviour to an agent $B$ which is a pebble machine without pebbles
+  and has a state for every configuration (which includes the placing of the
+  pebbles as well as state and tape content) of $A$. $B$ now moves over the
+  macro-vertices as $A$ moves through the gadgets. But $B$ has no pebbles and
+  thus, it is applicable to the 0-barrier. Projecting this construct back to
+  the gadget construction yields an $r$-barrier for $A$ and the chosen subset
+  of pebbles. Connecting now such $r$-barriers for all possible subsets of
+  pebbles gives the desired $r$-barrier because $A$ always fails to traverse
+  the $r$-barrier particular constructed for the pebble set used by $A$.
+\end{proof}
+By constructing such barriers it is possible to find for every agent
+with $s$ states and $p$ pebbles (note that here the tape of the agent is
+encoded in the states) it is possible to give a trap where the amount of
+vertices can be bound by $\mathcal{O}(s^{8^{p+1}})$. Which can be used to
+show that every agent with sub-logarithmic bits of memory needs at least
+$\Omega(\log\log n)$ many pebbles to explore at least $n$ vertices.
+
 \setquotestyle{english}

### 2016-05-01 paper/main.tex
added tikz pictures

@@
 \usepackage{mdframed}
+\usepackage{wrapfig}
 
@@
 \newtheorem{lem}{Lemma}
+\newtheorem{ex}{Exercise}
 
@@
 \begin{document}
+
+\input{tikz/settings}
 
@@
 \end{thm}
+\begin{wrapfigure}{r}{0.6\textwidth}
+  \caption{Illustration how to transform any graph to a 3-regular graph.}
+  \label{fig:3reg}
+  \resizebox{0.6\textwidth}{!}{\input{tikz/regsim}}
+\end{wrapfigure}
 \begin{proof}
@@
   vertex attached to the edge is replaced by the same construction and therfore
-  offers enough ports for the newly introduced edges.) The following picture
-  illustrates this construction:\todo{add picture}
-
-  This simulation yields at most $3\Delta n^{2}$ many nodes and can be emulated
-  with $\mathcal{O}(1)$ many memory space since it is only needed to store
-  the second component of the inserted nodes which is bounded by $3\Delta$.
-  Furthermore $A$ can be run on this constructed Graph and only needs
-  $\mathcal{0}(\log n)$ space since $\mathcal{O}(\log(3\Delta n^{2})) =
-  \mathcal{O}(\log(3) + \log(\Delta) + 2\log(n)) = \mathcal{O}(\log n)$.
-  Which yields the desired $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble
-  machine.
+  offers enough ports for the newly introduced edges.) Figure \ref{fig:3reg}
+  illustrates this construction.  This simulation yields at most
+  $3\Delta n^{2}$ many nodes and can be emulated with $\mathcal{O}(1)$ many
+  memory space since it is only needed to store the second component of the
+  inserted nodes which is bounded by $3\Delta$. Furthermore $A$ can be run on
+  this constructed Graph and only needs $\mathcal{0}(\log n)$ space since
+  $\mathcal{O}(\log(3\Delta n^{2})) = \mathcal{O}(\log(3) + \log(\Delta) +
+  2\log(n)) = \mathcal{O}(\log n)$. Which yields the desired
+  $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine.
 \end{proof}
@@
 \end{thm}
+\begin{figure}
+  \caption{Illustration how to simulate the tape of a pebble machine by
+  placing pebbles on a closed walk where $m_{1} = 3$. Note that the first
+  $2^{m_{1}}=2^{3}=8$ distinct vertices are used for the simulation but the
+  walk can be longer (as indicated by the dotted connection from $7$ to $0$).}
+  \label{fig:tapesim}
+  \begin{center}
+    \resizebox{0.6\textwidth}{!}{\input{tikz/tapesim}}
+  \end{center}
+\end{figure}
 \begin{proof}
@@
   on which the pebbles are placed as the content of the encoded memory block.
-  The following picture gives an illustration of this.\todo{add picture}
+  Figure \ref{fig:tapesim} illustrates this.
 
@@
 which we can delete to connect the vertices $e$ connected to the
-\enquote{outside}. This preserves the 3-regularity.
-With a given $p$-barrier $H$ we can construct a trap for an agent with $p$
-pebbles as follows:
-\todo{add picture}
+\enquote{outside}. This preserves the 3-regularity. The interested reader might
+then enjoy the following exercise:
+\begin{ex}
+  Given a $p$-barrier with $m$ vertices for a agent $A$ with $p$ pebbles.
+  Construct a trap for $A$ (with $2m+4$ vertices). 
+\end{ex}
 

### 2016-05-01 tikz/regsim.tex
added tikz pictures

\begin{tikzpicture}
  \node[node] (m1) {$v_{1}$};
  \node[node] (m2) [right = 4cm of m1] {$v_{2}$};
  \node[node] (m3) [right = 4cm of m2] {$v_{3}$};

  \draw[edge] (m1) to node[below,very near start] {0} node[above,very near end] {1} (m2);
  \draw[edge] (m2) to node[above,very near start] {0} node[below,very near end] {0} (m3);

  \node[node] (r11) [below = 6cm of m1] {$(v_{1},0)$};
  \node[node] (r12) [above = 2cm of r11] {$(v_{1},1)$};
  \node[node] (r13) [below = 2cm of r11] {$(v_{1},2)$};

  \node[node] (l11) [below = 6cm of m3] {$(v_{3},0)$};
  \node[node] (l12) [above = 2cm of l11] {$(v_{3},1)$};
  \node[node] (l13) [below = 2cm of l11] {$(v_{3},2)$};

  \node       (anker) [below = 6.5cm of m2] {};
  \node[node] (mid0) [above right = 1cm and 1cm of anker] {$(v_{2},0)$};
  \node[node] (mid1) [below right = 1cm and 1cm of anker] {$(v_{2},1)$};
  \node[node] (mid2) [below = 3cm of anker] {$(v_{2},2)$};
  \node[node] (mid3) [below left = 1cm and 1cm of anker] {$(v_{2},3)$};
  \node[node] (mid4) [above left = 1cm and 1cm of anker] {$(v_{2},4)$};
  \node[node] (mid5) [above = 3cm of anker] {$(v_{2},5)$};

  \draw[edge] (r11) to node[left,near end] {1} node[right,near start] {0} (r12);
  \draw[edge] (r11) to node[left,near end] {0} node[right,near start] {1} (r13);
  \draw[edge,bend right] (r12.south west) to node[left,very near end] {1} node[left, very near start] {0} (r13.north west);

  \draw[edge] (l11) to node[left,near end] {1} node[right,near start] {0}(l12);
  \draw[edge] (l11) to node[left,near end] {0} node[right,near start] {1}(l13);
  \draw[edge,bend left] (l12.south east) to node[left,very near end] {1} node[left, very near start] {0} (l13.north east);

  \draw[edge] (mid0) to node[right,near start] {0} node[right,near end] {1} (mid1);
  \draw[edge] (mid1) to node[right,near start] {0} node[right,near end] {1} (mid2);
  \draw[edge] (mid2) to node[left,near start] {0} node[left,near end] {1} (mid3);
  \draw[edge] (mid3) to node[left,near start] {0} node[left,near end] {1} (mid4);
  \draw[edge] (mid4) to node[left,near start] {0} node[left,near end] {1} (mid5);
  \draw[edge] (mid5) to node[right,near start] {0} node[right,near end] {1} (mid0);

  \draw[edge] (mid0) to node[very near start, above] {2} node[very near end, above] {2} (l11);
  \draw[edge] (mid2) to node[very near start, above] {2} node[very near end, above] {2} (l13);
  \draw[edge,bend left=10] (mid4) to node[very near start, below] {2} node[very near end, above] {2} (l12);

  \draw[edge] (mid1) to node[very near start, above] {2} node[very near end, above] {2} (r11);
  \draw[edge] (mid3) to node[very near start, above] {2} node[very near end, above] {2} (r13);
  \draw[edge] (mid5) to node[very near start, below] {2} node[very near end, above] {2} (r12);

\end{tikzpicture}

### 2016-05-01 tikz/settings.tex
added tikz pictures

\usetikzlibrary{patterns, arrows, cd, positioning, backgrounds, fit, decorations.pathmorphing, shapes.misc, calc, matrix, decorations.pathreplacing}
\tikzset{%
  node/.style={draw, minimum size=12mm, inner sep=0mm, circle, fill=gray!50},
  edge/.style={thick},
  move/.style={->},
  brace/.style={
    decorate,
    decoration={brace,amplitude=10pt,mirror},
  },
  table nodes/.style={
    rectangle,
    draw=black,
    align=center,
    minimum height=7mm,
    text depth=0.5ex,
    text height=2ex,
    inner xsep=0pt,
    outer sep=0pt
  },
  table/.style={
    matrix of nodes,
    row sep=\pgflinewidth,
    column sep=\pgflinewidth,
    nodes={
      table nodes
    }
  }
}

### 2016-05-01 paper/main.tex
first paper version to present

@@
 \section{Pebble machines}
-We are now ready to introduce the model of pebble machines formally. It closely
+We are now ready to introduce the model of pebble machines. It closely
 follows the notion of Turing machines but adds mechanisms to model the
@@
 \end{thm}
-\begin{wrapfigure}{r}{0.6\textwidth}
+\begin{wrapfigure}{r}{0.5\textwidth}
   \caption{Illustration how to transform any graph to a 3-regular graph.}
   \label{fig:3reg}
-  \resizebox{0.6\textwidth}{!}{\input{tikz/regsim}}
+  \resizebox{0.5\textwidth}{!}{\input{tikz/regsim}}
 \end{wrapfigure}
@@
 \end{thm}
-\begin{figure}
-  \caption{Illustration how to simulate the tape of a pebble machine by
-  placing pebbles on a closed walk where $m_{1} = 3$. Note that the first
-  $2^{m_{1}}=2^{3}=8$ distinct vertices are used for the simulation but the
-  walk can be longer (as indicated by the dotted connection from $7$ to $0$).}
-  \label{fig:tapesim}
-  \begin{center}
-    \resizebox{0.6\textwidth}{!}{\input{tikz/tapesim}}
-  \end{center}
-\end{figure}
 \begin{proof}
@@
   Figure \ref{fig:tapesim} illustrates this.
+  \begin{figure}[h!]
+    \caption{Illustration how to simulate the tape of a pebble machine by
+      placing pebbles on a closed walk where $m_{1} = 3$. Note that the first
+      $2^{m_{1}}=2^{3}=8$ distinct vertices are used for the simulation but the
+    walk can be longer (as indicated by the dotted connection from $7$ to $0$).}
+    \label{fig:tapesim}
+    \begin{center}
+      \resizebox{0.6\textwidth}{!}{\input{tikz/tapesim}}
+    \end{center}
+  \end{figure}
 
@@
   Let $M_{\text{Walk}}$ be pebble machine that yields $\omega$ on $G$.
-  $M_{\text{Walk}}$ can be implemented as $(\mathcal{O}(1),0,\mathcal{m_1})$
+  $M_{\text{Walk}}$ can be implemented as $(\mathcal{O}(1),0,\mathcal{O}(m_{1}))$
   pebble machine by Theorem \ref{thm:pebblewalk}.
@@
 
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \caption{Gadget construction that ensures locality of pebbles.}
+  \label{fig:gadget}
+  \resizebox{0.4\textwidth}{!}{\input{tikz/gadget}}
+\end{wrapfigure}
 The construction of barriers is inductively and therefore requires that the
 base case can be constructed directly. Fortunately Theorem 4 in \cite{0barrier}
-yields a graph which can be adapted by connecting two identical copies to a
-0-barrier (for details we refer again to \cite{pebbles}). With this in mind we
+yields a graph which can be adapted to a 0-barrier. With this in mind we
 introduce a gadget construction for a given $r$-barrier $B$ as it can be seen
-in figure \ref{fig:gadget}\todo{add figure}. Replacing edges of a graph with
+in Figure \ref{fig:gadget}. Replacing edges of a graph with
 such gadgets enforces, in a sense, \enquote{locality} of pebbles. We call
@@
 pebbles are either carried by the agent or are placed within the adjacent
-gadgets because otherwise the agent has left a pebble across of an $r$-barrier
-and crossed the barrier with $r$ pebbles contradicting that it is in fact an
-$r$-barrier. This observation can be used to construct an $r$-barrier given
-a $(r-1)$-barrier is known.
+\enquote{edges} because otherwise the agent has left a pebble across of an
+$r$-barrier and crossed the barrier with $r$ pebbles contradicting that it is
+in fact an $r$-barrier. This observation can be used to construct an
+$r$-barrier given a $(r-1)$-barrier is known.
 \begin{thm}
@@
   we can construct an $r$-barrier for this subset by using the given
-  $(r-1)$-barrier to enforce locality of the pebbles. We can then project
+  $(r-1)$-barrier. By the above described gadget construction we can enforce
+  the locality of the used $r$ pebbles. We can then project
   $A$'s behaviour to an agent $B$ which is a pebble machine without pebbles
@@
   pebbles gives the desired $r$-barrier because $A$ always fails to traverse
-  the $r$-barrier particular constructed for the pebble set used by $A$.
+  the $r$-barrier particularly constructed for the pebble set used by $A$.
 \end{proof}
@@
 
+\section{Conclusion}
+In this paper re-presented the idea of pebble machines for graph exploration
+as discussed in \cite{pebbles}. For this we focused on conwaying the essential
+ideas and constructions rather than explore the technical details. The main
+result clearly is the simulation of memory of pebble machines by encoding
+memory blocks by pebbles and that these pebbles keep a state by their placement
+along a closed walk.
+
 \setquotestyle{english}

### 2016-05-01 tikz/gadget.tex
first paper version to present

\begin{tikzpicture}
  \node[node] (0) {$v$};
  \node[node,above right=of 0] (1) {};
  \node[node,above left=of 0] (2) {};
  \node[node,below=of 0] (3) {};

  \draw[edge] (0) to (1);
  \draw[edge] (0) to (2);
  \draw[edge] (0) to (3);

  \node[node,below=5cm of 0] (0') {$v$};
  \node[node,above right=of 0'] (1') {};
  \node[node,above left=of 0'] (2') {};
  \node[node,below=of 0'] (3') {};

  \draw[edge,on background layer] (0') to node[draw,midway,fill=gray,shape=rectangle] {$B$} (1');
  \draw[edge,on background layer] (0') to node[draw,midway,fill=gray,shape=rectangle] {$B$} (2');
  \draw[edge,on background layer] (0') to node[draw,midway,fill=gray,shape=rectangle] {$B$} (3');
\end{tikzpicture}

### 2016-05-02 presentation/main.tex
started presentation

--- 2016-04-30 paper/main.tex
@@
-\documentclass[draft,oneside]{scrartcl}
+\documentclass{beamer}
 
 \usepackage[utf8]{inputenc}
+\usepackage{epigraph}
 
-\usepackage{epigraph}
-\usepackage[autostyle,german=guillemets]{csquotes}
-\usepackage[ngerman, english]{babel}
-\usepackage[style=numeric,backend=biber]{biblatex}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{todonotes}
-\usepackage{mdframed}
+\usetheme{metropolis}
 
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}{Lemma}
-
-\addbibresource{bibliography.bib}
-
-\DeclareMathOperator{\din}{\delta_{\mathit{in}}}
-\DeclareMathOperator{\dout}{\delta_{\mathit{out}}}
-\DeclareMathOperator{\Tid}{T_{\text{id}}}
-\DeclareMathOperator{\Tsteps}{T_{\text{steps}}}
-\DeclareMathOperator{\Twalk}{T_{\text{walk}}}
-\DeclareMathOperator{\Thead}{T_{\text{head}}}
+\title{A Grimm idea}
+\subtitle{Exploring graphs with pebbles}
+\author{Christoph Welzel}
+\institute{Logik und Theorie diskreter Systeme, RWTH Aachen}
 
 \begin{document}
-
-\setlength{\epigraphwidth}{0.7\textwidth}
-\setquotestyle{german}
-
-\title{A \emph{Grimm} idea}
-\subtitle{Exploring graphs with pebbles}
-\author{Christoph Welzel}
 \maketitle
-
-\begin{abstract}
-  In this paper we re-present and explain an approach on exploring large
-  undirected graphs with the help of markers, so called pebbles, for vertices.
-  We focus on the central ideas of this approach and explain why it is possible
-  to traverse any graph with $n$ vertices with $\Theta(\log \log n)$ pebbles
-  and the same amount of memory.
-\end{abstract}
-
+\begin{frame}
+  \frametitle{}
   \epigraph{Und als der volle Mond aufgestiegen war, so nahm Hänsel sein %
@@
   {\emph{Hänsel und Gretel}\\Brüder Grimm}
-
-\setquotestyle{english}
-\section{Introduction}
-Traversing large graphs is an interesting challenge. In times of the internet
-web crawlers have to traverse immense graphs but also regarding complexity
-theory this is an interesting problem. First we will informally introduce two
-complexity classes to illustrate the importance of graph traversal from a
-complexity point of view: $L$ as the class of problems that can be solved by
-a deterministic Turing machine with additional memory of logarithmic amount
-of the input. And $SL$ as the class of problems that can be solved with the
-same space requirements but by a non-deterministic symmetrical Turing machine,
-where symmetrical means that for every computation step of the Turing machine
-there is a computation step to undo the previous one. As it turns out checking
-if two vertices $s$ and $t$ are connected in an undirected graph is a problem
-that is complete for $SL$. This problem is often refered to as
-$\mathrm{USTCON}$ and \citeauthor{logspacealg} showed in \cite{logspacealg}
-that $\mathrm{USTCON}\in L$ which collapsed $SL$ into $L$, hence $SL = L$.
-In the following we will present the results from \cite{pebbles} where another
-mechanism of graph exploration is used: with the use of pebbles which are small
-pieces of memory that can be dropped on and collected from the vertex as an
-agent traverses the graph. As we will show it is possible to traverse a graph
-with $n$ vertices with $\mathcal{O}(\log\log n)$ memory and the same amount of
-pebbles. Furthermore we will explain why there is no smaller amount of memory
-or pebbles to generally obtain the same guarantee to traverse all $n$ vertices.
-
-\section{Preliminaries}
-For the course of this paper we assume the following: Firstly, the vertices can
-not be distinguished by the traversing agent. But as the agent moves on a
-vertex it can compute its degree. Secondly, the edges attached to the vertex
-can be locally distinguished and are enumerated with the indices
-$\left\{0,\dots,d_{v}-1\right\}$ where $d_{v}$ denotes the degree of the vertex
-$v$. We refer to the \enquote{index} of the edge as its \emph{port}. Note that
-every edge thus has two different ports and furthermore that there is no
-relation between the ports is assumed. Additionally the degree of the
-considered graphs are assumed to be limited by a constant $\Delta$ and that
-there are only a finite amount of vertices.
-
-\section{Pebble machines}
-We are now ready to introduce the model of pebble machines formally. It closely
-follows the notion of Turing machines but adds mechanisms to model the
-movements of the agent. The presented model of pebble machines thus have
-\begin{enumerate}
-  \item a finite set of states $Q$
-  \item a finite set of final states $F\subseteq Q$
-  \item a finite set of distinguishable pebbles $P$
-  \item a length of the used memory tape $m$
-  \item a computation function $\delta$
-  \item a function that describes the movement onto a vertex
-    $\din$
-  \item a function that describes the leaving of a vertex $\dout$
-  \item an inital state $q_{0}$
-\end{enumerate}
-where formally the computation function models the behaviour of the pebble
-machine as follows:
-\begin{equation*}
-  \delta\colon (Q\setminus F)\times\left\{0,1\right\}\rightarrow
-  Q\times\left\{0,1\right\}\times\left\{L,R\right\}
-\end{equation*}
-with the typical understanding of the computation of a Turing machine.
-As an agent traverses a vertex it is aware of the pebbles it carries
-around, it observes the set of pebbles on the vertex and the degree of the
-vertex and it furthermore aware of the port that it entered through.
-Thus we use
-\begin{equation*}
-  \din\colon Q\times 2^{P}\times 2^{P}\times
-  \left\{0,\dots,\Delta - 1\right\}\times\left\{0,\dots,\Delta - 1\right\}
-  \rightarrow Q
-\end{equation*}
-to model this behaviour. And finally as the agent leaves a vertex it leaves
-a set of pebbles behind, picks up another set and chooses the port it leaves
-through. We choose to model this behaviour as
-\begin{equation*}
-  \dout\colon Q
-  \rightarrow 2^{P}\times 2^{P}\times \left\{0,\dots,\Delta - 1\right\}
-\end{equation*}
-Of course we also demand consistency of the pebbles, i.e. that if the agent
-carried $P_{1}\subseteq P$ and found $P_{2}\subseteq P$ it is necessary that
-$P_{1}$ and $P_{2}$ are disjoint and furthermore that if the agent leaves
-carrying $P'_{1}$ and leaving $P'_{2}$ behind those sets are disjoint and
-$P_{1}\cup P_{2} = P'_{1}\cup P'_{2}$.
-
-\section{Graph exploration}
-In order to describe the movement of an agent we introduce the notion of an
-exploration sequence as $e_{0}, e_{1},\dots$ which models relative movements
-as follows. We use a sequence of variables $l_{0},l_{1},\dots$ which denotes
-the port a vertex was entered through. And the next vertex is determined as the
-one connected to the port $(l_{i} + e_{i}) \mod d_{v_{i}}$. We define
-$l_{0} = 0$ and the notion $(e_{0},\dots,e_{k})^{\ast}$ for periodic sequences.
-It can be shown that a periodic sequence produces a closed walk through a
-graph.
-\begin{proof}
-  We argue that there is only a finite amount of triples of the
-  form $(v,l,i)$ where currently the agent is on vertex $v$, entered
-  this vertex through port $l$ and is currently at index $i$ of the exploration
-  sequence. For two triples $(v',l',i')$ and $(v'',l'',i'')$ that both lead to
-  $(v,l,i)$ it is easy to see, that $(v',l',i') = (v'',l'',i'')$. Thus, for
-  every triple there is a unique predecessor and successor which implies due to
-  the finiteness of the triples $(v,l,i)$ and because the agent moves
-  infinitely that the first triple has to be valid infinitly often.
-  This means a periodic exploration sequence yields a closed walk.
-\end{proof}
-
-From the following result of \cite{logspacealg} we present how we can obtain
-an $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine that finds a closed
-walk of at least $n$ distinct vertices in any graph with bounded degree.
-\begin{thm}
-  \label{thm:logalg}
-There is an algorithm $M\in L$ which produces a universal exploration sequence
-for every regular graph with $n$ vertices.
-\end{thm}
-First we argue that we can use this algorithm to find a universal exploration
-sequence of the form $e=(e_{0},\dots,e_{k})^{\ast}$ that traverses $n$ distinct
-vertices for any 3-regular graph and requires only $\mathcal{O}(\log n)$
-memory. Therefore we rely on the traversal sequence of $M$ from Theorem
-\ref{thm:logalg} and take from that the first $k:=3n\cdot c$ indices where
-$c$ denotes the number of configurations of $M$. We can now be assured that
-$e$ actually is a universal traversal sequence for any 3-regular graph because
-otherwise $M$ would have already looped in a strict subset of vertices of some
-3-regular graph. This contradicts that $M$ produces a universal exploration
-sequence for any graph with $n$ vertices.
-
-We can now find the $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine we
-are looking for.
-\begin{thm}
-  \label{thm:pebblewalk}
-  There is a $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine which
-  explores every given graph $G$ with bounded degree $\Delta$ either completly
-  or at least loops on $n$ distinct vertices.
-\end{thm}
-\begin{proof}
-  The main idea is to use the adapted algorithm $A$ to find for an
-  universal exploration sequence for a 3-regular graph from above. Therefore
-  we take $G$ and transform it to a 3-regular graph on which $A$ finds the
-  corresponding universal exploration sequence. The transformation replaces
-  any node $v$ with degree $d$ by $3d$ nodes which then form a circle where
-  every nodes has degree $3$. The edges of $v$ are moved to nodes in the
-  circle. Specifically the edge with port $i$ is replaced by 3 edges which are
-  attached to $(v,i), (v,i+d), (v,i+2d)$. (Note that the other
-  vertex attached to the edge is replaced by the same construction and therfore
-  offers enough ports for the newly introduced edges.) The following picture
-  illustrates this construction:\todo{add picture}
-
-  This simulation yields at most $3\Delta n^{2}$ many nodes and can be emulated
-  with $\mathcal{O}(1)$ many memory space since it is only needed to store
-  the second component of the inserted nodes which is bounded by $3\Delta$.
-  Furthermore $A$ can be run on this constructed Graph and only needs
-  $\mathcal{0}(\log n)$ space since $\mathcal{O}(\log(3\Delta n^{2})) =
-  \mathcal{O}(\log(3) + \log(\Delta) + 2\log(n)) = \mathcal{O}(\log n)$.
-  Which yields the desired $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble
-  machine.
-\end{proof}
-
-In order to obtain the desired boundary of $\log\log n$ space and $\log\log n$
-pebbles we show that a pebble machine can be simulated by storing its tape
-content by pebbles that are placed on a closed walk.
-\begin{thm}
-  \label{thm:simulation}
-  For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by
-  a $(cs,p + c,m)$ pebble machine that simulates the walk of $M$ or explores
-  $G$.
-\end{thm}
-\begin{proof}
-  In this proof we will focus on the simulation and we leave out a thorough
-  analysis of the space requirements of the simulation since it is rather
-  technical but does not add a lot to the idea. Nevertheless we encourage
-  interested readers to see \cite{pebbles} for the details.
-
-  The main idea of this simulation is to store the tape of $M$ by pebbles
-  placed on a closed walk in the graph. We show that every node on this closed
-  walk can be given an index and a pebble placed on a node represents the
-  binary representation of the index as the content of $M$'s tape. Therefore we
-  first off introduce a variable $m_{1}$ which is dependent on the simulated
-  pebble machine $M$ (further requirements on $m_{1}$ and how to obtain it
-  can be seen in \cite{pebbles}). We will now take the tape of $M$ and separate
-  it into $2m/m_{1}$ blocks of the size $m_{1}$. And each of these blocks is
-  encoded by the placement of a pebble on a closed walk $\omega$. So we use
-  pebble $p_{0}$ to encode the first $m_{1}$ bits, the pebble $p_{1}$ used to
-  encode the next $m_{1}$ bits and so forth. Thus, the pebble $p_{i}$ encodes
-  the bits $im_{1},\dots,(i+1)m_{1}-1$. It is therefore necessary that every
-  pebble can encode $2^{m_1}$ different states. Therefore we use a closed walk
-  $\omega$ which visits at least $2^{m_1}$ distinct vertices yielding $2^{m_1}$
-  many \enquote{states} for each pebble (by its placement on this closed walk).
-  Therefore we can use the binary representation of the indices of the nodes
-  on which the pebbles are placed as the content of the encoded memory block.
-  The following picture gives an illustration of this.\todo{add picture}
-
-  In the following we show how this simulation can be managed.
-  Let $M_{\text{Walk}}$ be pebble machine that yields $\omega$ on $G$.
-  $M_{\text{Walk}}$ can be implemented as $(\mathcal{O}(1),0,\mathcal{m_1})$
-  pebble machine by Theorem \ref{thm:pebblewalk}.
-  In order to manage the simulation we use some
-  variables: $\Tid, \Tsteps, \Twalk, \Thead$ where $\Tid$ is used to identify
-  the index of a vertex on the walk of $M_{\text{Walk}}$, $\Twalk$ is the tape
-  content of $M_{\text{Walk}}$ which can therefore be restarted by setting
-  $\Twalk$ to 0, $\Tsteps$ counts the number of steps taken by
-  $M_{\text{Walk}}$, and $\Thead$ stores where $M$'s head is positioned.
-  Furthermore we need some pebbles to mark certain vertices of the closed walk:
-  $p_{\text{start}}, p_{\text{tmp}}, p_{\text{next}}$ and additionally the
-  pebbles that are placed on the walk to store $M$'s tape content
-  $P_{M} = \left\{p_{0},p_{1},\dots,p_{2m/m_{1}-1}\right\}$.
-  Now the different procedures used for the simulation can be presented:
-  \begin{description}
-    \item[Step():] Simulates on step according to $M_{\text{Walk}}$ and
-      increases $\Tsteps$.
-    \item[FindPebble($p_{i}$):] Executes \emph{Step()} until the pebble $p_{i}$
-      is observed.
-    \item[Restart():] Goes to the beginning of the closed walk by
-      \emph{FindPebble($p_{\text{start}}$)} and sets $\Tsteps,\Tid,\Twalk$ to 0
-    \item[NextDistinctVertex()] Finds the next distinct vertex of the walk. If
-      there are no more vertices on the walk (which means that already
-      $2^{m_1}$ distinct vertices have been traversed; the number of distinct
-      vertices on the walk is given by $\Tid$) it simply executes
-      \emph{Restart()}. Otherwise it does one step and drops $p_{\text{tmp}}$
-      to mark this vertex. It then stores the current amount of steps as well
-      as the current state of $M_{\text{Walk}}$ (introducing two auxiliary
-      variables $\Tsteps',\Twalk'$). It then restarts $M_{\text{Walk}}$ and
-      moves to $p_{\text{tmp}}$ by \emph{FindPebble($p_{\text{tmp}}$)}. If
-      it used the same amount of steps as stored in $\Tsteps'$ then this is the
-      first occurence of the vertex in the closed walk and therefore it is a
-      new distinct vertex and $\Tid$ can be increased. Otherwise the context of
-      $M_{\text{Walk}}$ is restored and the next vertex is checked.
-    \item[GetPebbleId($p_{i}$):] Finds the index of the vertex $p_{i}$ is
-      placed on. Beginning from the start of the closed walk
-      (found by executing \emph{Restart()} it moves along distinct vertices
-      (by using \emph{NextDistinctVertex()}) and returns $\Tid$ as soon as
-      $p_{i}$ is observed.
-    \item[PutPebbleAtId($p_{i},\mathit{id}$):] Puts pebble $p_i$ at a certain
-      index. First it picks up $p_{i}$ and restarts the walk. Then it executes
-      $\mathit{id}$ times \emph{NextDistinctVertex()} and drops $p_{i}$.
-    \item[ReadBit():] Reads the $\Thead$'s bit of $M$'s tape. $\Thead$ gives
-      the position of the bit that should be read. Therefore the pebble
-      $p_{\lfloor \Thead/m_{1}\rfloor}$ encodes this bit. The \enquote{state}
-      of this pebble can be obtained with
-      \emph{GetPebbleId($p_{\lfloor \Thead/m_{1}\rfloor}$)} and from the
-      encoded value the $(\Thead\mod m_{1})$-th bit is the one under $M$'s
-      head.
-    \item[WriteBit($b$):] Writes $b$ to $\Thead$'s bit of $M$'s tape. First
-      $\Thead$'s bit is obtained (by \emph{ReadBit()}). Additionally we
-      identify the encoding pebble $p_{i}$ as already seen for
-      \emph{ReadBit()} and let be $j = \Thead\mod m_{1}$ the offset of the bit
-      within the memory block. If the bit actually flips the value of the
-      memory block changes by $2^j$ (for the flip from 1 to 0 the value
-      decreases and for the flip from 0 to 1 it increases). Therefore $p_{i}$
-      is put either $2^j$ indices up or down which can be easily done by using
-      \emph{PutPebbleAtId(\dots)}.
-  \end{description}
-  These are the procedures used to simulate $M$'s tape. Furthermore we keep
-  $M$'s states in the state space of the simulation. To conclude the simulation
-  we have to consider what happens if $M$ moves from the current vertex to
-  another vertex $v'$. Then the pebble $p_{tmp}$ is dropped on $v'$ and the
-  pebbles are moved to the same index they have in $\omega$ for a new closed
-  walk $\omega'$ (obtained by $M_{\text{Walk}}$ simulated starting in $v'$;
-  this walk is also ensured to have at least $2^{m_1}$ distinct vertices).
-\end{proof}
-As Theorem \ref{thm:pebblewalk} yields a $(c,0,c\cdot\log n)$ pebble machine
-that explores a given graph we can now repeatedly apply the simulation
-from Theorem \ref{thm:simulation} (precisely $\log\log n$ times) and end up
-with a $(c'^{\log\log n}\cdot c, \log\log n\cdot c',
-\frac{c}{2^{\log\log n}}\log n) =
-(c'^{\log\log n}\cdot c, \log\log n\cdot c', c)$ pebble machine exploring the
-graph.
-
-\section{Barriers}
-In the following we will discuss the limits of the exploration approach with
-pebbles. Specifically, we will argue that we can construct 3-regular graphs
-that any agent with $p$ pebbles cannot traverse. Such graphs are called
-$p$-barriers.
-Note that connecting a 3-regular graph might violate its 3-regularity.
-Therefore we rely on having a distinguishable edge $e$ in the 3-regular graph
-which we can delete to connect the vertices $e$ connected to the
-\enquote{outside}. This preserves the 3-regularity.
-With a given $p$-barrier $H$ we can construct a trap for an agent with $p$
-pebbles as follows:
-\todo{add picture}
-
-The construction of barriers is inductively and therefore requires that the
-base case can be constructed directly. Fortunately Theorem 4 in \cite{0barrier}
-yields a graph which can be adapted by connecting two identical copies to a
-0-barrier (for details we refer again to \cite{pebbles}). With this in mind we
-introduce a gadget construction for a given $r$-barrier $B$ as it can be seen
-in figure \ref{fig:gadget}\todo{add figure}. Replacing edges of a graph with
-such gadgets enforces, in a sense, \enquote{locality} of pebbles. We call
-the verices that are connected by the gadget macro-vertices and if a $r+1$
-pebble machine stands on a macro vertex we can safely be assured that all
-pebbles are either carried by the agent or are placed within the adjacent
-gadgets because otherwise the agent has left a pebble across of an $r$-barrier
-and crossed the barrier with $r$ pebbles contradicting that it is in fact an
-$r$-barrier. This observation can be used to construct an $r$-barrier given
-a $(r-1)$-barrier is known.
-\begin{thm}
-  With a given $(r-1)$-barrier for an agent $A$ a $r$-barrier can be
-  constructed.
-\end{thm}
-\begin{proof}
-  We will present only the key ideas of this proof since it involves a
-  few technicalities which do not add much to the general understanding
-  and are therefore omitted. Given a subset of pebbles of cardinality $r$
-  we can construct an $r$-barrier for this subset by using the given
-  $(r-1)$-barrier to enforce locality of the pebbles. We can then project
-  $A$'s behaviour to an agent $B$ which is a pebble machine without pebbles
-  and has a state for every configuration (which includes the placing of the
-  pebbles as well as state and tape content) of $A$. $B$ now moves over the
-  macro-vertices as $A$ moves through the gadgets. But $B$ has no pebbles and
-  thus, it is applicable to the 0-barrier. Projecting this construct back to
-  the gadget construction yields an $r$-barrier for $A$ and the chosen subset
-  of pebbles. Connecting now such $r$-barriers for all possible subsets of
-  pebbles gives the desired $r$-barrier because $A$ always fails to traverse
-  the $r$-barrier particular constructed for the pebble set used by $A$.
-\end{proof}
-By constructing such barriers it is possible to find for every agent
-with $s$ states and $p$ pebbles (note that here the tape of the agent is
-encoded in the states) it is possible to give a trap where the amount of
-vertices can be bound by $\mathcal{O}(s^{8^{p+1}})$. Which can be used to
-show that every agent with sub-logarithmic bits of memory needs at least
-$\Omega(\log\log n)$ many pebbles to explore at least $n$ vertices.
-
-\setquotestyle{english}
-\printbibliography
+\end{frame}
 \end{document}

### 2016-05-02 presentation/main.tex
worked on presentation

@@
 \usepackage{epigraph}
+\usepackage{tikz}
+
+\input{tikz/settings}
 
 \usetheme{metropolis}
+\metroset{numbering=fraction}
 
@@
 \begin{frame}
+  \frametitle{Motivation}
+  \begin{itemize}
+    \item Traversing Brobdingnagian graphs
+    \item[$\rightarrow$] Web crawlers
+    \item Agent moves over vertices along edges
+    \item[$\Rightarrow$] Memory efficient agents
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Agents}
+  \begin{quotation}
+    Und als der volle Mond aufgestiegen war, so nahm Hänsel sein
+    Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten
+    wie neu geschlagene Batzen und zeigten ihnen den Weg.
+  \end{quotation}
+  \vspace{-0.5cm}
+  \flushright{Brüder Grimm}
+  \vspace{-0.5cm}
+  \flushright{\emph{Hänsel und Gretel}}
+  \begin{itemize}
+    \item Agent carries set of markers $\rightarrow$ pebbles
+    \item Leave pebbles on vertices
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Brobdignagian graphs}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item Indistinguishable vertices
+      \item Bounded degree ($\Delta$)
+      \item Edges can locally enumerated $\left\{0,\dots,\Delta-1\right\}$ (Port)
+      \item Agent is aware of:
+        \begin{enumerate}
+          \item Degree  of vertex
+          \item Pebbles placed on vertex
+          \item Pebbles carried by agent
+          \item Port    agent entered vertex
+        \end{enumerate}
+    \end{itemize}
+    \column{0.5\textwidth}
+    \begin{center}
+      \resizebox{\textwidth}{!}{\input{tikz/portex}}
+    \end{center}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Exploration sequence}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item Describe movement of agent by relative turns
+      \item $e_{1},\dots, e_{n}$
+      \item For a vertex $v$ with degree $d_{v}$ which is entered on port $p$
+        is left through port $p + e_{i}\mod p$
+      \item<2->[$\rightarrow$] Example:
+        $\only<3-3>{\colorbox{green}}{1}\;,\only<4-4>{\colorbox{green}}{3}\;,
+        \only<5-5>{\colorbox{green}}{2}\;,\only<6-6>{\colorbox{green}}{2}$
+    \end{itemize}
+    \column{0.5\textwidth}
+    \begin{center}
+      \resizebox{\textwidth}{!}{\input{tikz/moveex}}
+    \end{center}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
   \frametitle{}
-  \epigraph{Und als der volle Mond aufgestiegen war, so nahm Hänsel sein %
-    Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten %
-  wie neu geschlagene Batzen und zeigten ihnen den Weg.}%
-  {\emph{Hänsel und Gretel}\\Brüder Grimm}
 \end{frame}

### 2016-05-02 tikz/moveex.tex
worked on presentation

\begin{tikzpicture}
  \node[minimum size=12mm,inner sep=0mm, circle] (8) {};
  \node[node,right=of 8] (6) {};
  \node[node,right=of 6] (7) {};
  \node[node,below=of 8] (0) {};
  \node[node,below=of 6] (1) {};
  \node[node,below=of 7] (2) {};
  \node[node,below=of 0] (3) {};
  \node[node,below=of 1] (4) {};
  \node[node,below=of 2] (5) {};
  \node[node,above right=0.5cm and 1cm of 2] (8) {};
  \node[node,below right=0.5cm and 1cm of 2] (9) {};

  \draw[edge] (0) to node[very near start, above] {0} node[very near end, above] {1} (1);
  \draw[edge] (1) to node[very near start, below] {0} node[very near end, above] {1} (2);
  \draw[edge,bend right] (2.north west) to node[very near start, right] {0} node[very near end, above] {2} (0);
  \draw[edge] (0) to node[very near start, right] {1} node[very near end, left ] {0} (3);
  \draw[edge] (3) to node[very near start, above] {1} node[very near end, below] {1} (4);
  \draw[edge] (4) to node[very near start, below] {0} node[very near end, below] {1} (5);
  \draw[edge] (5) to node[very near start, above] {0} node[very near end, below] {2} (1);
  \draw[edge] (1) to node[very near start, left ] {3} node[very near end, left ] {2} (6);
  \draw[edge] (6) to node[very near start, above] {0} node[very near end, above] {1} (7);
  \draw[edge] (8) to node[very near start, above] {0} node[very near end, right] {0} (7);
  \draw[edge] (8) to node[very near start, above] {1} node[very near end, right] {2} (5);
  \draw[edge] (9) to node[very near start, below] {1} node[very near end, below] {3} (5);
  \draw[edge,bend right=20] (9) to node[very near start, below] {0} node[very near end, below] {1} (6);

  \begin{scope}[on background layer]%
      \node [fit=(0)] (layer) {};%
  \end{scope}
  \begin{scope}[on background layer]%
      \node [fit=(4)] (layer) {};%
  \end{scope}
  \only<3-3>{\begin{scope}[on background layer]%
      \node [fit=(0), fill=green!50] (layer) {};%
  \end{scope}}
  \only<4-4>{\begin{scope}[on background layer]%
      \node [fit=(3), fill=green!50] (layer) {};%
  \end{scope}}
  \only<5-5>{\begin{scope}[on background layer]%
      \node [fit=(4), fill=green!50] (layer) {};%
  \end{scope}}
  \only<6-6>{\begin{scope}[on background layer]%
      \node [fit=(3), fill=green!50] (layer) {};%
  \end{scope}}
  \only<7-7>{\begin{scope}[on background layer]%
      \node [fit=(4), fill=green!50] (layer) {};%
  \end{scope}}

\end{tikzpicture}

### 2016-05-02 tikz/portex.tex
worked on presentation

\begin{tikzpicture}
  \node[node] (m1) {$v_{1}$};
  \node[node,right=2cm of m1] (m2) {$v_{2}$};

  \node[above left=of m1] (e1) {};
  \node[below=of m1] (e2) {};

  \node[above right=of m2] (e3) {};
  \node[below=of m2] (e4) {};

  \draw[edge] (m1) to node[very near start, above] {0} (e1);
  \draw[edge] (m1) to node[near start, left] {2} (e2);

  \draw[edge] (m2) to node[very near start, above] {1} (e3);
  \draw[edge] (m2) to node[near start, right] {2} (e4);

  \draw[edge] (m1) to node[very near start, below] {1} node[very near end, above] {0} (m2);
\end{tikzpicture}

### 2016-05-03 presentation/main.tex
presentation right before simulation

@@
 \usepackage{tikz}
+\usepackage{todonotes}
 
@@
       \item Bounded degree ($\Delta$)
-      \item Edges can locally enumerated $\left\{0,\dots,\Delta-1\right\}$ (Port)
+      \item Edges can locally enumerated $\left\{0,\dots,\Delta-1\right\}$
+        (Port)
       \item Agent is aware of:
@@
 \begin{frame}
-  \frametitle{}
+  \frametitle{Closed walk}
+  \begin{theorem}
+    A exploration sequence $(e_{1},\dots,e_{k})^{\ast}$ produces a closed walk.
+  \end{theorem}
+  \begin{itemize}
+    \item Introduce triple $(v,l,i)$ with vertex $v$ is entered
+      through port $l$ and $e_{i}$ is the next turn
+    \item Note that there is exactly one $(v,l,i) \leadsto (v',l',i')$
+    \item Furthermore assume $t_{1} = (v',l',i') \leadsto (v,l,i)$ and
+      $t_{2} = (v'',l'',i'') \leadsto (v,l,i)$:
+      \begin{itemize}
+        \item $t_{1}$ and $t_{2}$ both entered $v$ through $l$: $v' = v''$
+        \item $t_{1}$ and $t_{2}$ lead that $i$ is the next turn: $i' = i''$
+        \item $l' + e_{i'} \mod d_{v'} = l'' + e_{i''} \mod d_{v''}$ and
+          $l',l''\leq d_{v'} = d_{v''}$: $l' = l''$
+      \end{itemize}
+    \item Only finite triples, thus projection to vertices yields closed walk
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Exploring pebble machine}
+  \alt<+>{
+    \begin{theorem}[Reingold]
+      There is an algorithm $A$ with $\mathcal{O}(n)$ space requirement producing
+      a universal exploration sequence for every regular graph with $n$ vertices.
+    \end{theorem}
+  }{
+    \begin{theorem}
+      Thus, there is $(\mathcal{O}(1), 0, \mathcal{O}(\log n)$ that moves
+      along a closed walk with $n$ distinct vertices (or explores the whole
+      graph).
+    \end{theorem}
+  }
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item<3-> Establish 3-regularity
+        \begin{itemize}
+          \item Transform $v$ to $3\cdot d_{v}$ distinct vertices
+          \item TODO: ADD BOUNDARY
+        \end{itemize}
+      \item<5-> Use $A$ and take first $k = 3n\cdot c$ ($c$ number of
+        configurations $M_{A}$)
+    \end{itemize}
+    \column{0.5\textwidth}
+    \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Tape simulation via pebbles}
 \end{frame}

### 2016-05-03 tikz/settings.tex
presentation walks, pebble simulation

@@
     inner xsep=0pt,
-    outer sep=0pt
+    outer sep=0pt,
+    inner sep=0pt
   },
@@
     matrix of nodes,
-    row sep=\pgflinewidth,
-    column sep=\pgflinewidth,
+    row sep=-0.5pt,
+    column sep=-0.5pt,
     nodes={

### 2016-05-03 tikz/tapesimint.tex
presentation walks, pebble simulation

\begin{tikzpicture}
  \matrix (tape) [table, text width=7mm, name=tape]
    { 1 & 1 & 0 & 0 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\};

  \node[above=of tape-1-1.west] (s1) {};
  \node[below=of tape-1-1.west] (s2) {};

  \node[above=of tape-1-3.east] (s3) {};
  \node[below=of tape-1-3.east] (s4) {};

  \node[above=of tape-1-6.east] (s5) {};
  \node[below=of tape-1-6.east] (s6) {};

  \node[above=of tape-1-9.east] (s7) {};
  \node[below=of tape-1-9.east] (s8) {};

  \node[above=of tape-1-12.east] (s9) {};
  \node[below=of tape-1-12.east] (s10) {};

  \uncover<2-2>{\draw[brace] (tape-1-12.north east) -- node[yshift=6mm] {$m = 12$} (tape-1-1.north west);}
  \uncover<3->{\draw[brace] (s9.center) -- node[yshift=6mm] {$m = 12$} (s1.center);}

  \uncover<3->{
    \draw[dashed] (s1) to (s2);
    \draw[dashed] (s3) to (s4);
    \draw[dashed] (s5) to (s6);
    \draw[dashed] (s7) to (s8);
    \draw[dashed] (s9) to (s10);
  }

  \uncover<3-3>{
    \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-3.south east);

    \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-6.south east);

    \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-9.south east);

    \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-12.south east);
  }
  \uncover<4-4>{
    \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm]  {$p_{0}$} (tape-1-3.south east);

    \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm]  {$p_{1}$} (tape-1-6.south east);

    \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm]  {$p_{2}$} (tape-1-9.south east);

    \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$p_{3}$} (tape-1-12.south east);
  }
\end{tikzpicture}

### 2016-05-03 tikz/tapesimpebsep.tex
presentation walks, pebble simulation

--- 2016-05-03 tikz/tapesimint.tex
@@
     { 1 & 1 & 0 & 0 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\};
-
-  \node[above=of tape-1-1.west] (s1) {};
-  \node[below=of tape-1-1.west] (s2) {};
-
-  \node[above=of tape-1-3.east] (s3) {};
-  \node[below=of tape-1-3.east] (s4) {};
-
-  \node[above=of tape-1-6.east] (s5) {};
-  \node[below=of tape-1-6.east] (s6) {};
-
-  \node[above=of tape-1-9.east] (s7) {};
-  \node[below=of tape-1-9.east] (s8) {};
-
-  \node[above=of tape-1-12.east] (s9) {};
-  \node[below=of tape-1-12.east] (s10) {};
-
-  \uncover<2-2>{\draw[brace] (tape-1-12.north east) -- node[yshift=6mm] {$m = 12$} (tape-1-1.north west);}
-  \uncover<3->{\draw[brace] (s9.center) -- node[yshift=6mm] {$m = 12$} (s1.center);}
-
-  \uncover<3->{
-    \draw[dashed] (s1) to (s2);
-    \draw[dashed] (s3) to (s4);
-    \draw[dashed] (s5) to (s6);
-    \draw[dashed] (s7) to (s8);
-    \draw[dashed] (s9) to (s10);
-  }
-
-  \uncover<3-3>{
-    \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-3.south east);
-
-    \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-6.south east);
-
-    \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-9.south east);
-
-    \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$m_{1} = 3$} (tape-1-12.south east);
-  }
-  \uncover<4-4>{
   \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm] {$p_{0}$} (tape-1-3.south east); 
-
   \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm] {$p_{1}$} (tape-1-6.south east); 
-
   \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm] {$p_{2}$} (tape-1-9.south east); 
-
   \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$p_{3}$} (tape-1-12.south east); 
-  }
 \end{tikzpicture}

### 2016-05-03 tikz/tapesimpesep.tex
presentation walks, pebble simulation

\begin{tikzpicture}
  \node[minimum size=12mm,inner sep=0mm, circle] (8) {};
  \node[node,right=of 8,label={100:$p_{0}$}] (6) {$6$};
  \node[node,right=of 6] (7) {$7$};
  \node[node,below=of 8,label={100:$p_{3}$}] (0) {$0$};
  \node[node,below=of 6] (1) {$1$};
  \node[node,below=of 7,label={$p_{1}$}] (2) {$2$};
  \node[node,below=of 0,label={45:$p_{2}$}] (3) {$3$};
  \node[node,below=of 1] (4) {$4$};
  \node[node,below=of 2] (5) {$5$};

  \draw[move] (0) to (1);
  \draw[move] (1) to (2);
  \draw[move,bend left] (2.south west) to (0);
  \draw[move] (0) to (3);
  \draw[move] (3) to (4);
  \draw[move] (4) to (5);
  \draw[move] (5) to (1);
  \draw[move] (1) to (6);
  \draw[move] (6) to (7);
  \draw[dashed, move, decorate,
  decoration={snake,amplitude=0.5cm, segment length=3cm}, bend right=55]
  (7.north west) to (0);

  \matrix (tape) [left=of 0, table, text width=7mm, name=tape]
    { 1 & 1 & 0 & 0 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\};
  \draw[brace] (tape-1-1.south west) -- node[yshift=-6mm] {$p_{0}$} (tape-1-3.south east); 
  \draw[brace] (tape-1-4.south west) -- node[yshift=-6mm] {$p_{1}$} (tape-1-6.south east); 
  \draw[brace] (tape-1-7.south west) -- node[yshift=-6mm] {$p_{2}$} (tape-1-9.south east); 
  \draw[brace] (tape-1-10.south west) -- node[yshift=-6mm] {$p_{3}$} (tape-1-12.south east); 
\end{tikzpicture}

### 2016-05-03 tikz/tapesimsep.tex
presentation walks, pebble simulation

\begin{tikzpicture}
  \matrix (tape) [table, text width=7mm, name=tape]
    { 1 & 1 & 0 & 0 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 0 \\};

  \node[above=of tape-1-3.east] (s1) {};
  \node[below=of tape-1-3.east] (s2) {};
  \draw[brace] (tape-1-3.north east) -- node[yshift=6mm] {$m_{1} = 3$} (tape-1-1.north west);
  \draw[dashed] (s1) to (s2);

  \node[above=of tape-1-6.east] (s3) {};
  \node[below=of tape-1-6.east] (s4) {};
  \draw[brace] (tape-1-6.north east) -- node[yshift=6mm] {$m_{1} = 3$} (tape-1-4.north west);
  \draw[dashed] (s3) to (s4);

  \node[above=of tape-1-9.east] (s5) {};
  \node[below=of tape-1-9.east] (s6) {};
  \draw[brace] (tape-1-9.north east) -- node[yshift=6mm] {$m_{1} = 3$} (tape-1-7.north west);
  \draw[dashed] (s5) to (s6);

  \node[above=of tape-1-12.east] (s7) {};
  \node[below=of tape-1-12.east] (s8) {};
  \draw[brace] (tape-1-12.north east) -- node[yshift=6mm] {$m_{1} = 3$} (tape-1-10.north west);
  \draw[dashed] (s7) to (s8);
\end{tikzpicture}

### 2016-05-04 presentation/main.tex
presentation walks, pebble simulation
yay
presentation

@@
 \usepackage{tikz}
-\usepackage{todonotes}
+\usepackage{csquotes}
 
@@
 \metroset{numbering=fraction}
+
+\DeclareMathOperator{\din}{\delta_{\mathit{in}}}
+\DeclareMathOperator{\dout}{\delta_{\mathit{out}}}
+\DeclareMathOperator{\Tid}{T_{\text{id}}}
+\DeclareMathOperator{\Tsteps}{T_{\text{steps}}}
+\DeclareMathOperator{\Twalk}{T_{\text{walk}}}
+\DeclareMathOperator{\Thead}{T_{\text{head}}}
 
@@
       \item<2->[$\rightarrow$] Example:
-        $\only<3-3>{\colorbox{green}}{1}\;,\only<4-4>{\colorbox{green}}{3}\;,
-        \only<5-5>{\colorbox{green}}{2}\;,\only<6-6>{\colorbox{green}}{2}$
+        $\alt<3-3>{\colorbox{green}{1}}{\colorbox{white!0}{1}},
+        \alt<4-4>{\colorbox{green}{3}}{\colorbox{white!0}{3}},
+        \alt<5-5>{\colorbox{green}{2}}{\colorbox{white!0}{2}},
+        \alt<6-6>{\colorbox{green}{2}}{\colorbox{white!0}{2}}$
     \end{itemize}
@@
     \begin{theorem}[Reingold]
-      There is an algorithm $A$ with $\mathcal{O}(n)$ space requirement producing
-      a universal exploration sequence for every regular graph with $n$ vertices.
+      There is an algorithm $A$ with $\mathcal{O}(n)$ space requirement
+      producing a universal exploration sequence for every regular graph with
+      $n$ vertices.
     \end{theorem}
@@
     \begin{theorem}
-      Thus, there is $(\mathcal{O}(1), 0, \mathcal{O}(\log n)$ that moves
+      Thus, there is $(\mathcal{O}(1), 0, \mathcal{O}(\log n))$ that moves
       along a closed walk with $n$ distinct vertices (or explores the whole
@@
   \frametitle{Tape simulation via pebbles}
+  \begin{itemize}
+    \item Simulate tape of size $m$ by pebbles:
+      \begin{itemize}
+        \item<3-> Separate into memory blocks of size $m_{1}$
+        \item<4-> Represent every block by one of $\left\{p_{0},\dots,p_{\frac{m}{m_{1}-1}}\right\}$ pebbles
+      \end{itemize}
+  \end{itemize}
+  \uncover<2->{\input{tikz/tapesimint}}
 \end{frame}
+
+\begin{frame}
+  \frametitle{Tape simulation via pebbles}
+  \input{tikz/tapesimpebsep}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item Every pebbles needs $2^{m_{1}}$ distinct \enquote{states}
+        \begin{itemize}
+          \item Placement on a walk with at least $2^{m_{1}}$ distinct vertices
+            yields \enquote{states}
+        \end{itemize}
+    \end{itemize}
+    \column{0.5\textwidth}
+    \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Mechanisms of simulation}
+  \begin{itemize}
+    \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
+      distinct vertices
+    \item Identify \emph{distinct} vertices of the walk
+    \item Read from and write to simulated tape
+    \item Preserve tape content through steps of simulated agent
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Simulation of $M_{\text{Walk}}$}
+  \begin{itemize}
+    \item $M_{\text{Walk}}$ can be implemented as
+      $(\mathcal{O}(1), 0, \mathcal{O}(m_{1}))$ pebble machine
+    \item Used variables:
+      \begin{itemize}
+        \item $\Twalk$: stores $M_{\text{Walk}}$'s tape
+        \item $\Tsteps$: stores number of taken steps
+        \item $\Tid$: stores number of visited distinct vertices
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Finding distinct vertices}
+  Problem: Indistinguishable vertices $\leadsto$ next vertex \enquote{new}?
+  \begin{columns}
+    \column{0.5\textwidth}
+    Solution:
+    \begin{enumerate}
+      \item Execute step
+      \item Drop pebble $p_{\text{tmp}}$
+      \item Store $\Twalk$ in $T'_{\text{walk}}$
+      \item Restart $M_{\text{Walk}}$
+      \item Execute steps until $p_{\text{tmp}}$ is observed
+      \item If $\Twalk = T'_{\text{walk}}$ the vertex is new
+      \item Otherwise start over
+    \end{enumerate}
+    \column{0.5\textwidth}
+    \input{tikz/disvert}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \begin{center}
+    \Huge Thank you for your attention.
+  \end{center}
+\end{frame}
+
 \end{document}

### 2016-05-05 presentation/main.tex
graphical simulation of distinct vertices
started on barriers

@@
 
+\section{Graph traversial}
 \begin{frame}
@@
     \begin{center}
-      \resizebox{\textwidth}{!}{\input{tikz/portex}}
+      % \resizebox{\textwidth}{!}{\input{tikz/portex}}
     \end{center}
@@
     \begin{center}
-      \resizebox{\textwidth}{!}{\input{tikz/moveex}}
+      % \resizebox{\textwidth}{!}{\input{tikz/moveex}}
     \end{center}
@@
     \column{0.5\textwidth}
-    \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
+    % \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
   \end{columns}
@@
 
+\section{Simulation}
 \begin{frame}
@@
   \end{itemize}
-  \uncover<2->{\input{tikz/tapesimint}}
+  % \uncover<2->{\input{tikz/tapesimint}}
 \end{frame}
@@
   \frametitle{Tape simulation via pebbles}
-  \input{tikz/tapesimpebsep}
+  % \input{tikz/tapesimpebsep}
   \begin{columns}
@@
     \column{0.5\textwidth}
-    \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
+    % \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
   \end{columns}
@@
       $(\mathcal{O}(1), 0, \mathcal{O}(m_{1}))$ pebble machine
-    \item Used variables:
+    \item Used variables/pebbles:
       \begin{itemize}
@@
         \item $\Tid$: stores number of visited distinct vertices
+        \item $p_{\text{start}}$: marks the beginning
       \end{itemize}
@@
     \column{0.5\textwidth}
-    \input{tikz/disvert}
+    % \input{tikz/disvert}
   \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Memory management}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item $\Thead$ stores head position
+      \item $p_{\lfloor\frac{\Thead}{m_{1}}\rfloor}$: pebble of memory block
+      \item $\mathit{off} = \Thead\mod m_{1}$: offset in memory block
+      \item Reading:
+        \begin{itemize}
+          \item Retrieve encoding pebble
+          \item Return bit with offset
+        \end{itemize}
+      \item Writing:
+        \begin{itemize}
+          \item Read bit
+          \item On bit-flip move encoding pebble $2^{\mathit{off}}$ bits up or down
+        \end{itemize}
+    \end{itemize}
+    \column{0.5\textwidth}
+    % \resizebox{\textwidth}{!}{\input{tikz/tapesimpebsep}}
+    % \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Memory management: Writing}
+  \begin{itemize}
+    \item Read bit
+    \item On bit-flip: move pebble
+  \end{itemize}
+  % \resizebox{\textwidth}{!}{\input{tikz/bitwrite}}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Simulation}
+  \begin{theorem}
+    For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by a
+    $(cs,p+c,m)$ pebble machine that simulates the walk of $M$ on $G$ or
+    explores $G$.
+  \end{theorem}
+  \begin{itemize}
+    \item There is a $(c,0,c\cdot\log n)$ pebble machine which explores
+      a graph $G$ with $n$ vertices
+    \item Applying above simulation $\log \log n$ times yields:
+      \begin{theorem}
+        For every Graph $G$ with $n$ vertices there is a
+        $(c'^{\log\log n}\cdot c, \log\log n\cdot c', c)$ pebble machine
+        which explores $G$.
+      \end{theorem}
+  \end{itemize}
+\end{frame}
+
+\section{Limitations of pebble machines}
+\begin{frame}
+  \frametitle{Limitations of pebbles}
+  \begin{itemize}
+    \item Construct graphs which cannot be traversed by agents with $p$ pebbles
+    \item Such graphs are called $p$-barriers
+      \begin{center}
+        \resizebox{0.3\textwidth}{!}{\input{tikz/barrier}}
+      \end{center}
+    \item In the following: inductive construction of barriers
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Locality gadget}
+  \begin{itemize}
+    \item Replace edge by a $p$-barrier
+    \item Enforce \enquote{locality} of pebbles
+    \item An agent cannot traverse any gadget without all his pebbles
+    \item All pebbles of the agent are either carried or placed within the
+      adjacent gadgets
+  \end{itemize}
+  \begin{center}
+    \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/locgadget}}}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier construction}
 \end{frame}

### 2016-05-05 presentation/main.tex
projection done

@@
   \begin{itemize}
-    \item Replace edge by a $p$-barrier
+    \item Replace edge by a $(p-1)$-barrier
     \item Enforce \enquote{locality} of pebbles
-    \item An agent cannot traverse any gadget without all his pebbles
+    \item An agent cannot traverse any gadget without \emph{all} his pebbles
     \item All pebbles of the agent are either carried or placed within the
@@
 \begin{frame}
-  \frametitle{Barrier construction}
+  \frametitle{Barrier construction: Initial thoughts}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item Consider a subset of pebbles of cardinality $p$
+      \item Use the locality gadget as edges
+      \item Since pebbles are local: enumerate configurations in macro vertex
+        $C_{1},\dots,C_{\alpha}$
+      \item Project $A$ to a agent without pebbles $B$
+      \item $B$ has $\alpha$ states and traverses through macro vertices
+    \end{itemize}
+    \column{0.5\textwidth}
+    \resizebox{\textwidth}{!}{\input{tikz/projection}}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier construction: The real deal}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item $B$ has no pebbles and is therefore prone to a $0$-barrier
+    \end{itemize}
+    \column{0.5\textwidth}
+  \end{columns}
 \end{frame}

### 2016-05-06 presentation/main.tex
barrier construction tikzed
small correction

@@
     \begin{center}
-      % \resizebox{\textwidth}{!}{\input{tikz/portex}}
+      \resizebox{\textwidth}{!}{\input{tikz/portex}}
     \end{center}
@@
     \begin{center}
-      % \resizebox{\textwidth}{!}{\input{tikz/moveex}}
+      \resizebox{\textwidth}{!}{\input{tikz/moveex}}
     \end{center}
@@
     \column{0.5\textwidth}
-    % \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
+    \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
   \end{columns}
@@
         \item<3-> Separate into memory blocks of size $m_{1}$
-        \item<4-> Represent every block by one of $\left\{p_{0},\dots,p_{\frac{m}{m_{1}-1}}\right\}$ pebbles
+        \item<4-> Represent every block by one of $\left\{p_{0},\dots,p_{\frac{m}{m_{1}}-1}\right\}$ pebbles
       \end{itemize}
   \end{itemize}
-  % \uncover<2->{\input{tikz/tapesimint}}
+  \uncover<2->{\input{tikz/tapesimint}}
 \end{frame}
@@
   \frametitle{Tape simulation via pebbles}
-  % \input{tikz/tapesimpebsep}
+  \input{tikz/tapesimpebsep}
   \begin{columns}
@@
     \column{0.5\textwidth}
-    % \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
+    \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
   \end{columns}
@@
     \column{0.5\textwidth}
-    % \input{tikz/disvert}
+    \input{tikz/disvert}
   \end{columns}
@@
     \column{0.5\textwidth}
-    % \resizebox{\textwidth}{!}{\input{tikz/tapesimpebsep}}
-    % \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
+    \resizebox{\textwidth}{!}{\input{tikz/tapesimpebsep}}
+    \resizebox{\textwidth}{!}{\input{tikz/tapesimwalk}}
   \end{columns}
@@
   \end{itemize}
-  % \resizebox{\textwidth}{!}{\input{tikz/bitwrite}}
+  \resizebox{\textwidth}{!}{\input{tikz/bitwrite}}
 \end{frame}
@@
   \frametitle{Barrier construction: The real deal}
-  \begin{columns}
-    \column{0.5\textwidth}
   \begin{itemize}
     \item $B$ has no pebbles and is therefore prone to a $0$-barrier
+    \item Apply locality gadget to all edges
+    \item This yields a $p$-barrier for the chosen subset of pebbles
+    \item Iterate $p$-barriers for all possible subsets
   \end{itemize}
-    \column{0.5\textwidth}
-  \end{columns}
+  \begin{center}
+    \resizebox{0.8\textwidth}{!}{\input{tikz/iterbarrier}}
+  \end{center}
 \end{frame}

### 2016-05-09 presentation/main.tex
separated proof of exploring pebble machine into lemmata

@@
 \usepackage{csquotes}
+\usepackage{xcolor}
 
@@
 
-\title{A Grimm idea}
-\subtitle{Exploring graphs with pebbles}
+\title{Undirected Graph Exploration with $\Theta(\log\log n)$ Pebbles}
+\subtitle{A Grimm idea}
 \author{Christoph Welzel}
@@
 \begin{document}
+% \tikzexternalize
 \maketitle
@@
   \begin{itemize}
-    \item Traversing Brobdingnagian graphs
-    \item[$\rightarrow$] Web crawlers
-    \item Agent moves over vertices along edges
-    \item[$\Rightarrow$] Memory efficient agents
+    \item Exploration of huge finite graphs with bounded degree by agents
+    \item Agents are entities which are located on a vertex and can move along
+      an edge
+    \item Agents can drop markers on vertices
+    \item Agent \emph{explores} a graph by deterministically visiting all of
+      its vertices
   \end{itemize}
@@
 
-\section{Graph traversial}
+\section{Preliminaries}
 \begin{frame}
-  \frametitle{Agents}
-  \begin{quotation}
-    Und als der volle Mond aufgestiegen war, so nahm Hänsel sein
-    Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten
-    wie neu geschlagene Batzen und zeigten ihnen den Weg.
-  \end{quotation}
-  \vspace{-0.5cm}
-  \flushright{Brüder Grimm}
-  \vspace{-0.5cm}
-  \flushright{\emph{Hänsel und Gretel}}
-  \begin{itemize}
-    \item Agent carries set of markers $\rightarrow$ pebbles
-    \item Leave pebbles on vertices
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Brobdignagian graphs}
+  \frametitle{Huge graphs}
   \begin{columns}
@@
     \begin{itemize}
+      \item Finite, but huge
+      \item Undirected
       \item Indistinguishable vertices
       \item Bounded degree ($\Delta$)
-      \item Edges can locally enumerated $\left\{0,\dots,\Delta-1\right\}$
+      \item Edges can locally be enumerated as $0,\dots,\Delta-1$
         (Port)
-      \item Agent is aware of:
-        \begin{enumerate}
-          \item Degree  of vertex
-          \item Pebbles placed on vertex
-          \item Pebbles carried by agent
-          \item Port    agent entered vertex
-        \end{enumerate}
     \end{itemize}
@@
 \begin{frame}
+  \frametitle{Agents}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item Agent carries set of distinguishable pebbles
+      \item Formalisation as pebble-machines
+        \begin{itemize}
+          \item $(Q,F,P,m,\delta,\din,\dout,q_{0})$
+          \item $P$: set of pebbles
+          \item $m$: length of the used memory tape
+          \item $\din$: formalisation of agent entering
+          \item $\dout$ formalisation of agent leaving
+        \end{itemize}
+    \end{itemize}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item As an agent moves on a vertex it observes:
+        \begin{itemize}
+          \item Pebbles it carries
+          \item Pebbles lying on the vertex
+          \item Degree of vertex
+        \end{itemize}
+      \item Agent executes a computation on a vertex to determine:
+        \begin{itemize}
+          \item Port to leave
+          \item Pebbles to leave behind
+          \item Pebbles to carry with it
+        \end{itemize}
+    \end{itemize}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
   \frametitle{Exploration sequence}
@@
     \begin{itemize}
-      \item Describe movement of agent by relative turns
-      \item $e_{1},\dots, e_{n}$
-      \item For a vertex $v$ with degree $d_{v}$ which is entered on port $p$
-        is left through port $p + e_{i}\mod p$
+      \item Describe movement of agent by relative movements:
+        \begin{itemize}
+          \item An exploration sequence has the form $e_{1},\dots, e_{n}$
+          \item For a vertex $v$ with degree $d_{v}$ which is entered on port
+            $p$ is left through port $p + e_{i}\mod d_{v}$
+          \item An exploration sequence is called \emph{universial} for a class
+            of graphs if following it explores any graph of that class
           \item<2->[$\rightarrow$] Example:
@@
             \alt<6-6>{\colorbox{green}{2}}{\colorbox{white!0}{2}}$
+        \end{itemize}
     \end{itemize}
@@
 
+\section{Graph traversal}
+\begin{frame}
+  \frametitle{Exploring pebble machine}
+  \begin{theorem}[Reingold]
+    There is an $\mathcal{O}(n)$-space algorithm producing a universal
+    exploration sequence for any regular graph on $n$ vertices.
+  \end{theorem}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (d1) {};
+      \node[below=2 of d1] (d2) {};
+      \draw[decorate,decoration={snake,amplitude=0.3cm, segment length=1cm},->]
+        (d1) to (d2);
+    \end{tikzpicture}
+  \end{center}
+  \begin{theorem}
+    There exists a $(\mathcal{O}(1), 0, \mathcal{O}(\log n))$-pebble machine
+    that moves along a closed walk and either explores the graph or visits at
+    least $n$ distinct vertices, for any graph with bounded degree.
+  \end{theorem}
+\end{frame}
 \begin{frame}
   \frametitle{Closed walk}
-  \begin{theorem}
-    A exploration sequence $(e_{1},\dots,e_{k})^{\ast}$ produces a closed walk.
-  \end{theorem}
+  \begin{lemma}
+    An agent following an exploration sequence of the form
+    $(e_{1},\dots,e_{k})^{\ast}$ moves along a closed walk.
+  \end{lemma}
   \begin{itemize}
-    \item Introduce triple $(v,l,i)$ with vertex $v$ is entered
-      through port $l$ and $e_{i}$ is the next turn
-    \item Note that there is exactly one $(v,l,i) \leadsto (v',l',i')$
-    \item Furthermore assume $t_{1} = (v',l',i') \leadsto (v,l,i)$ and
-      $t_{2} = (v'',l'',i'') \leadsto (v,l,i)$:
+    \item Examine triples $(v,\ell,i)$:
       \begin{itemize}
-        \item $t_{1}$ and $t_{2}$ both entered $v$ through $l$: $v' = v''$
-        \item $t_{1}$ and $t_{2}$ lead that $i$ is the next turn: $i' = i''$
-        \item $l' + e_{i'} \mod d_{v'} = l'' + e_{i''} \mod d_{v''}$ and
-          $l',l''\leq d_{v'} = d_{v''}$: $l' = l''$
+        \item $v$: current vertex
+        \item $\ell$: port agent entered $v$ through
+        \item $i$: next step of the exploration sequence
       \end{itemize}
-    \item Only finite triples, thus projection to vertices yields closed walk
+    \item Deterministically $(v,\ell,i) \leadsto (v',\ell',i')$
+    \item If $t_{1} = (v',\ell',i') \leadsto (v,\ell,i)$ and
+      $t_{2} = (v'',\ell'',i'') \leadsto (v,\ell,i)$: $t_{1} = t_{2}$
+    \item Only finite triples: projection to vertices yields closed walk
   \end{itemize}
@@
 \begin{frame}
+  \frametitle{Universal exploration of $3$-regular graphs}
+  \begin{lemma}
+    There exists an $\mathcal{O}(\log n)$-space algorithm producing a universal
+    exploration sequence $(e_{1},\dots,e_{k})^{\ast}$ for any $3$-regular graph
+    with at most $n$ vertices.
+  \end{lemma}
+  \begin{itemize}
+    \item Let $\mathcal{M}$ be the Turing machine from Reingold's Theorem
+    \item The exploration sequence computed by $\mathcal{M}$ is universial for
+      3-regular graphs with at most $n$ vertices
+      \alt<1-1>{
+        \begin{itemize}
+          \item Assume $3$-regular $G_{0}$ with $n_{0} < n$ vertices is not
+            explored
+          \item Then there is a vertex that is not traversed
+          \item Repeatedly apply \parbox{3\baselineskip}{\resizebox{!}
+            {3\baselineskip}{\input{tikz/blowup}}}
+          \item Until there are $n$ vertices which contradicts Reingold's
+            Theorem
+        \end{itemize}
+      }{
+      \item Produce a periodic universal exploration sequence
+        $(e_{1},\dots,e_{k})^{\ast}$
+        \begin{itemize}
+          \item Construct $\mathcal{M}'$ which simulates $\mathcal{M}$ for
+            $3n\cdot c$ steps where $c$ is the number of configurations of $M$
+          \item Output $e = (e_{1},\dots,e_{k})^{\ast}$
+          \item Assume $e$ is not universal; then it loops in $V'$ with
+            $|V'|<n$
+          \item $\mathcal{M}$ has to enter a vertex twice with the same
+            configuration
+          \item Contradicts universality of the exploration sequence of
+            $\mathcal{M}$
+        \end{itemize}
+      }
+  \end{itemize}
+  \pause
+\end{frame}
+
+\begin{frame}
   \frametitle{Exploring pebble machine}
-  \alt<+>{
-    \begin{theorem}[Reingold]
-      There is an algorithm $A$ with $\mathcal{O}(n)$ space requirement
-      producing a universal exploration sequence for every regular graph with
-      $n$ vertices.
-    \end{theorem}
-  }{
-    \begin{theorem}
-      Thus, there is $(\mathcal{O}(1), 0, \mathcal{O}(\log n))$ that moves
-      along a closed walk with $n$ distinct vertices (or explores the whole
-      graph).
-    \end{theorem}
-  }
   \begin{columns}
@@
     \begin{itemize}
-      \item<3-> Establish 3-regularity
+      \item<2-> Establish 3-regularity
         \begin{itemize}
           \item Transform $v$ to $3\cdot d_{v}$ distinct vertices
-          \item TODO: ADD BOUNDARY
         \end{itemize}
-      \item<5-> Use $A$ and take first $k = 3n\cdot c$ ($c$ number of
+      \item<4-> Use Reingold's algorithm and take first $k = 3n\cdot c$ ($c$ number of
         configurations $M_{A}$)
@@
     \column{0.5\textwidth}
-    \uncover<4->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
+    \uncover<3->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
   \end{columns}

### 2016-05-09 tikz/settings.tex
separated proof of exploring pebble machine into lemmata

@@
-\usetikzlibrary{patterns, arrows, cd, positioning, backgrounds, fit, decorations.pathmorphing, shapes.misc, calc, matrix, decorations.pathreplacing}
+\usetikzlibrary{patterns, arrows, cd, positioning, backgrounds, fit, decorations.pathmorphing, shapes.misc, calc, matrix, decorations.pathreplacing, external}
 \tikzset{%

### 2016-05-09 presentation/main.tex
finished simulation

@@
 \usepackage{xcolor}
+\usepackage{amssymb}
 
@@
   \frametitle{Closed walk}
-  \begin{lemma}
+  \begin{lemma}[Closed walk]
     An agent following an exploration sequence of the form
@@
   \frametitle{Universal exploration of $3$-regular graphs}
-  \begin{lemma}
+  \begin{lemma}[Periodic exploration sequence (PES-Lemma)]
     There exists an $\mathcal{O}(\log n)$-space algorithm producing a universal
@@
         $(e_{1},\dots,e_{k})^{\ast}$
+        \uncover<2-2>{
           \begin{itemize}
             \item Construct $\mathcal{M}'$ which simulates $\mathcal{M}$ for
-            $3n\cdot c$ steps where $c$ is the number of configurations of $M$
+              $3n\cdot c$ steps where $c$ is the number of configurations of
+              $M$
             \item Output $e = (e_{1},\dots,e_{k})^{\ast}$
@@
         }
+      }
   \end{itemize}
+  \pause
   \pause
@@
 \begin{frame}
-  \frametitle{Exploring pebble machine}
+  \frametitle{3-Regularity}
   \begin{columns}
@@
     \begin{itemize}
-      \item<2-> Establish 3-regularity
+      \item Establish 3-regularity
         \begin{itemize}
-          \item Transform $v$ to $3\cdot d_{v}$ distinct vertices
+          \item Recall: \parbox{3\baselineskip}{\resizebox{!}
+            {3\baselineskip}{\input{tikz/blowup}}}
+          \item<2-> Transform $v$ to $3\cdot d_{v}$ distinct vertices
         \end{itemize}
-      \item<4-> Use Reingold's algorithm and take first $k = 3n\cdot c$ ($c$ number of
-        configurations $M_{A}$)
     \end{itemize}
@@
 
-\section{Simulation}
+\begin{frame}
+  \frametitle{Exploring pebble machine}
+  \begin{itemize}
+    \item Graph $G$
+    \item Transform to 3-regular $G_{\text{reg}}$
+    \item Applying PES-Lemma to $G_{\text{reg}}$ yields:
+  \end{itemize}
+  \begin{theorem}
+    There exists a $(\mathcal{O}(1), 0, \mathcal{O}(\log n))$-pebble machine
+    that moves along a closed walk and either explores the graph or visits at
+    least $n$ distinct vertices, for any graph with bounded degree.
+  \end{theorem}
+\end{frame}
+
+\section{Pebble simulation}
+\begin{frame}
+  \begin{theorem}
+    There is a constant $c\in\mathcal{N}$, such that for any Graph $G$
+    with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
+    exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates the walk
+    of $\mathcal{M}$ or explores $G$.
+  \end{theorem}
+\end{frame}
+
 \begin{frame}
@@
 \begin{frame}
-  \frametitle{Simulation}
+  \frametitle{Transfer tape-content through movements}
+  \begin{itemize}
+    \item Simulated machine moves
+    \item Preserve tape-content:
+      \begin{itemize}
+        \item Drop $p_{\text{next}}$ on next vertex
+        \item Transfer encoding pebbles onto walk $\omega'$ starting from
+          next vertex
+        \item Preserve \enquote{state} by placing at same index
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Recall: Mechanisms of simulation}
+  \begin{itemize}
+    \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
+      distinct vertices \uncover<2->{\checkmark}
+    \item Identify \emph{distinct} vertices of the walk \uncover<3->{\checkmark}
+    \item Read from and write to simulated tape \uncover<4->{\checkmark}
+    \item Preserve tape content through steps of simulated agent \uncover<5->{\checkmark}
+  \end{itemize}
+  \uncover<6->{
     \begin{theorem}
-    For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by a
-    $(cs,p+c,m)$ pebble machine that simulates the walk of $M$ on $G$ or
-    explores $G$.
+      There is a constant $c\in\mathcal{N}$, such that for any Graph $G$
+      with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
+      exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates the walk
+      of $\mathcal{M}$ or explores $G$.
     \end{theorem}
+  }
+\end{frame}
+
+\begin{frame}
+  \frametitle{Exploring graphs with $\log\log n$ pebbles}
   \begin{itemize}
@@
       a graph $G$ with $n$ vertices
-    \item Applying above simulation $\log \log n$ times yields:
+    \item Applying above simulation $\log \log n$ times yields
+      $(c'^{\log\log n}\cdot c, c'\cdot\log\log n, c)$ pebble machine
       \begin{theorem}
-        For every Graph $G$ with $n$ vertices there is a
-        $(c'^{\log\log n}\cdot c, \log\log n\cdot c', c)$ pebble machine
-        which explores $G$.
+        Any bounded-degree graph on at most $n$ vertices can be explored using
+        $\mathcal{O}(\log\log n)$ pebbles and memory.
       \end{theorem}

### 2016-05-10 presentation/main.tex
barriers

@@
   \begin{theorem}
-    There is a constant $c\in\mathcal{N}$, such that for any Graph $G$
+    There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
     with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
@@
         \item<3-> Separate into memory blocks of size $m_{1}$
-        \item<4-> Represent every block by one of $\left\{p_{0},\dots,p_{\frac{m}{m_{1}}-1}\right\}$ pebbles
+        \item<4-> Represent every block by one of
+          $p_{0},\dots,p_{\frac{m}{m_{1}}-1}$ pebbles
       \end{itemize}
@@
           \item Read bit
-          \item On bit-flip move encoding pebble $2^{\mathit{off}}$ bits up or down
+          \item On bit-flip move encoding pebble $2^{\mathit{off}}$ bits up or
+            down
         \end{itemize}
@@
       distinct vertices \uncover<2->{\checkmark}
-    \item Identify \emph{distinct} vertices of the walk \uncover<3->{\checkmark}
+    \item Identify \emph{distinct} vertices of the walk
+      \uncover<3->{\checkmark}
     \item Read from and write to simulated tape \uncover<4->{\checkmark}
-    \item Preserve tape content through steps of simulated agent \uncover<5->{\checkmark}
+    \item Preserve tape content through steps of simulated agent
+      \uncover<5->{\checkmark}
   \end{itemize}
@@
     \begin{theorem}
-      There is a constant $c\in\mathcal{N}$, such that for any Graph $G$
-      with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
-      exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates the walk
-      of $\mathcal{M}$ or explores $G$.
+      There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
+      with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$,
+      there exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates
+      the walk of $\mathcal{M}$ or explores $G$.
     \end{theorem}
@@
   \begin{itemize}
-    \item Construct graphs which cannot be traversed by agents with $p$ pebbles
+    \item Construct 3-regular graphs which cannot be traversed by an agent
+      $\mathcal{A}$ with $p$ pebbles
     \item Such graphs are called $p$-barriers
       \begin{center}
-        \resizebox{0.3\textwidth}{!}{\input{tikz/barrier}}
+        \resizebox{0.7\textwidth}{!}{\input{tikz/barrierint}}
       \end{center}
-    \item In the following: inductive construction of barriers
+    \item If $\mathcal{A}$ starts in any vertex in $G$ it will never traverse
+      the barrier from $v_{1}$ ($v_{2}$) to $v_{2}$ or $v_{3}$ using at most
+      $p$ pebbles
   \end{itemize}

### 2016-05-10 presentation/main.tex
mark for a nearly complete set of slides

@@
     \item Applying above simulation $\log \log n$ times yields
-      $(c'^{\log\log n}\cdot c, c'\cdot\log\log n, c)$ pebble machine
+      $(c'^{\log\log n}\cdot c, c'\cdot\log\log n, c)$ pebble machine exploring
+      $G$
       \begin{theorem}
@@
       \begin{center}
-        \resizebox{0.7\textwidth}{!}{\input{tikz/barrierint}}
+        \resizebox{0.6\textwidth}{!}{\input{tikz/barrierint}}
       \end{center}
-    \item If $\mathcal{A}$ starts in any vertex in $G$ it will never traverse
-      the barrier from $v_{1}$ ($v_{2}$) to $v_{2}$ or $v_{3}$ using at most
-      $p$ pebbles
+    \item $\mathcal{A}$ cannot traverse a barrier from $v_{1}$ or $v_{2}$
+      to $v_{3}$ or $v_{4}$ or vice versa using at most $p$ pebbles
+    \item Inductive construction of barriers
   \end{itemize}
@@
       adjacent gadgets
-  \end{itemize}
       \begin{center}
@@
       \end{center}
+    \item<3-> Original vertices are called \emph{macro} vertices
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \begin{theorem}
+    Given an $(r-1)$-barrier $B$ with $m$ vertices for an agent $\mathcal{A}$
+    with $p\geq r$ pebbles, we can construct an $r$-barrier $B'$ with
+    $\mathcal{O}(\binom{p}{r}\cdot m\cdot\alpha_{B}^{2})$ vertices for
+    $\mathcal{A}$.
+  \end{theorem}
+  \begin{itemize}
+    \item $\alpha_{B}$ is the amount of \enquote{local} configurations for
+      $\mathcal{A}$ with $r$ pebbles
+  \end{itemize}
 \end{frame}
@@
     \begin{itemize}
-      \item Consider a subset of pebbles of cardinality $p$
+      \item Consider a subset of pebbles of cardinality $r$
       \item Use the locality gadget as edges
@@
 \begin{frame}
-  \frametitle{Barrier construction: The real deal}
+  \frametitle{Barrier construction}
   \begin{itemize}
@@
     \item Iterate $p$-barriers for all possible subsets
+      \begin{center}
+        \resizebox{0.7\textwidth}{!}{\input{tikz/iterbarrier}}
+      \end{center}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier base case}
+  \begin{theorem}
+    For any $q$ non cooperative $s$-state agents without pebbles, there
+    exists a 3-regular graph $G$ on $\mathcal{O}(qs)$ vertices with the
+    following property: There are two edges $\left\{v_{1},v_{2}\right\}$
+    and $\left\{v_{3},v_{4}\right\}$ in $G$, the first labeled 0, such
+    that any of the $q$ agents starting in $v_{1}$ or $v_{2}$ does not
+    traverse the edge $\left\{v_{3},v_{4}\right\}$.
+  \end{theorem}
+  \begin{itemize}
+    \item For agent $\mathcal{A}$ consider
+      $S = \left\{\mathcal{A}_{q}\mid q\in Q\right\}$
+    \item Since $|S| = |Q| = q$ there is a 0-barrier with $\mathcal{O}(s^{2})$
+      vertices
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier}
+  \begin{theorem}
+    Given an $(r-1)$-barrier $B$ with $m$ vertices for an agent $\mathcal{A}$
+    with $p\geq r$ pebbles, we can construct an $r$-barrier $B'$ with
+    $\mathcal{O}(\binom{p}{r}\cdot m\cdot\alpha_{B}^{2})$ vertices for
+    $\mathcal{A}$.
+  \end{theorem}
+  \begin{center}
+    \resizebox{0.7\textwidth}{!}{\input{tikz/iterbarrier}}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier size}
+  \begin{itemize}
+    \item Iterative construction
   \end{itemize}
   \begin{center}
-    \resizebox{0.8\textwidth}{!}{\input{tikz/iterbarrier}}
+    \resizebox{0.8\textwidth}{!}{\input{tikz/barriersize}}
   \end{center}
+  \begin{theorem}
+    For $r\leq p$ and $s\geq 2^{p}$, the number of vertices of $r$-barrier
+    $B_{r}$ for the $s$-state agent $\mathcal{A}$ with $p$ pebbles is bounded
+    by $\mathcal{O}(s^{8^{r+1}})$.
+  \end{theorem}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Lower pebble bound}
+  \begin{theorem}
+    For any constant $\epsilon > 0$, an agent with at most
+    $\mathcal{O}((\log n)^{1-\epsilon})$ bits of memory needs at least
+    $\Omega(\log\log n)$ distinguishable pebbles for exploring all
+    graphs on at most $n$ vertices.
+  \end{theorem}
 \end{frame}

### 2016-05-10 tikz/barriersize.tex
mark for a nearly complete set of slides

\begin{tikzpicture}
  \node[node] (b0l0) {};
  \node[node,below=3 of b0l0] (b0l1) {};
  \node[node,right=of b0l0] (b0r0) {};
  \node[node,below=3 of b0r0] (b0r1) {};
  \node[fit=(b0l0) (b0l1) (b0r0) (b0r1),draw=black,label={90:\huge{$H_{1}$}}] (b0) {};
  \draw[dashed, thick] (b0.north) to (b0.south);

  \node[node,right=of b0r0] (b1l0) {};
  \node[node,below=3 of b1l0] (b1l1) {};
  \node[node,right=12 of b1l0] (b1r0) {};
  \node[node,below=3 of b1r0] (b1r1) {};
  \node[fit=(b1l0) (b1l1) (b1r0) (b1r1),draw=black,label={90:\huge{$H_{2}$}}] (b1) {};
  \draw[dashed, thick] (b1.north) to (b1.south);

  \node[below right=0.1 and 1.3 of b1l0]   (i0) {};
  \node[below=1.5 of i0]     (i1) {};
  \node[right=3 of i0] (i2) {};
  \node[below=1.5 of i2]     (i3) {};
  \node[fit=(i0) (i1) (i2) (i3), draw=black, rectangle, label={90:\huge{$B_{r-1}$}}] (Br2) {};

  \node[below right=0.08 and 0.3 of i0] (i4) {\huge{$\ddots$}};
  \node[below =0.1 of i4] (i5) {};
  \node[right =0.3 of i4]     (i6) {};
  \node[below =0.1 of i6] (i7) {};
  \node[fit=(i4) (i5) (i6) (i7), draw=black, rectangle] (Br3) {};

  \node[minimum size=12mm,circle,right=of b1r0] (b2l0) {};
  \node[minimum size=12mm,circle,below=3 of b2l0] (b2l1) {};
  \node[minimum size=12mm,circle,right=of b2l0] (b2r0) {};
  \node[minimum size=12mm,circle,below=3 of b2r0] (b2r1) {};

  \node[node,right=of b2r0] (b3l0) {};
  \node[node,below=3 of b3l0] (b3l1) {};
  \node[node,right=of b3l0] (b3r0) {};
  \node[node,below=3 of b3r0] (b3r1) {};
  \node[fit=(b3l0) (b3l1) (b3r0) (b3r1),draw=black,label={90:\huge{$H_{{p}\choose{r}}$}}] (b2) {};
  \draw[dashed, thick] (b1.north) to (b1.south);

  \draw[edge] (b0r0) to (b1l0);
  \draw[edge] (b0r1) to (b1l1);
  \draw[dashed] (b1r0) to (b2l0);
  \draw[dashed] (b1r1) to (b2l1);
  \draw[dashed] (b2r0) to (b3l0);
  \draw[dashed] (b2r1) to (b3l1);

  \draw[edge] (b0l0) to (b0l1);
  \draw[edge] (b3r0) to (b3r1);

  \draw[dashed] (b1l0) to (Br2.west);

  \node[fit=(b0) (b1) (b2), draw=black, label={90:\huge{$B$}},inner sep=12mm] (b) {};
\end{tikzpicture}

### 2016-05-10 presentation/main.tex
slides alpha

@@
 \usepackage{amssymb}
+\usepackage{mdframed}
 
@@
   \begin{itemize}
-    \item Exploration of huge finite graphs with bounded degree by agents
-    \item Agents are entities which are located on a vertex and can move along
-      an edge
-    \item Agents can drop markers on vertices
+    \item Exploration of huge finite graphs by agents
+    \item Agents are located on a vertex and move along edges
+    \item Agents can drop pebbles on vertices
     \item Agent \emph{explores} a graph by deterministically visiting all of
@@
   \begin{columns}
-    \column{0.5\textwidth}
+    \column{0.55\textwidth}
     \begin{itemize}
@@
       \item Undirected
-      \item Indistinguishable vertices
+      \item Indistinguishable vertices:
+      \parbox{\baselineskip}{
+        \resizebox{!}{\baselineskip}{
+          \begin{tikzpicture}
+            \node[node] {};
+          \end{tikzpicture}
+        }
+      }
       \item Bounded degree ($\Delta$)
-      \item Edges can locally be enumerated as $0,\dots,\Delta-1$
-        (Port)
+      \item Edges can locally be labeled with
+        \textcolor{green}{$0,\dots,\Delta-1$} (Port)
     \end{itemize}
@@
           \item $(Q,F,P,m,\delta,\din,\dout,q_{0})$
-          \item $P$: set of pebbles
-          \item $m$: length of the used memory tape
-          \item $\din$: formalisation of agent entering
-          \item $\dout$ formalisation of agent leaving
+          \item<2-> $\din$: moving onto vertex
+          \item<7-> $\dout$: leaving vertex
         \end{itemize}
@@
     \begin{itemize}
-      \item As an agent moves on a vertex it observes:
+      \item<3-> As an agent moves onto a vertex it observes:
         \begin{itemize}
-          \item Pebbles it carries
-          \item Pebbles lying on the vertex
-          \item Degree of vertex
+          \item<4-> Pebbles it carries
+          \item<5-> Pebbles on the vertex
+          \item<6-> Degree of vertex
         \end{itemize}
-      \item Agent executes a computation on a vertex to determine:
+      \item<8-> Computation on a vertex determines:
         \begin{itemize}
-          \item Port to leave
-          \item Pebbles to leave behind
-          \item Pebbles to carry with it
+          \item<9-> Port to leave
+          \item<10-> Pebbles to drop
+          \item<11-> Pebbles to carry along
         \end{itemize}
@@
     \begin{itemize}
-      \item Describe movement of agent by relative movements:
-        \begin{itemize}
-          \item An exploration sequence has the form $e_{1},\dots, e_{n}$
-          \item For a vertex $v$ with degree $d_{v}$ which is entered on port
-            $p$ is left through port $p + e_{i}\mod d_{v}$
-          \item An exploration sequence is called \emph{universial} for a class
-            of graphs if following it explores any graph of that class
+      \item Exploration sequence $e_{1},\dots, e_{n}$
+      \item Relative movements of agent
+      \item Leaving port: $\ell_{i} + e_{i}\mod d_{v}$
+      \item \emph{Universial} for a class of graphs if it explores any graph of
+        that class
       \item<2->[$\rightarrow$] Example:
@@
         \alt<6-6>{\colorbox{green}{2}}{\colorbox{white!0}{2}}$
-        \end{itemize}
     \end{itemize}
@@
       \node[below=2 of d1] (d2) {};
-      \draw[decorate,decoration={snake,amplitude=0.3cm, segment length=1cm},->]
-        (d1) to (d2);
+      \draw[->, bend right] (d1) to (d2);
+      \uncover<2->{
+        \node[rectangle, draw=green, below right=0.3 and 1 of d1]
+        {3-Regularity};
+      }
+      \uncover<3->{
+        \node[rectangle, draw=blue, below right=1 and 1.2 of d1]
+        {Periodic Universal lemma};
+      }
+      \uncover<4->{
+        \node[rectangle, draw=yellow, below right=1.7 and 1 of d1]
+        {Closed walk lemma};
+      }
     \end{tikzpicture}
@@
 \end{frame}
+
 \begin{frame}
   \frametitle{Closed walk}
+  \begin{mdframed}[linecolor=yellow]
     \begin{lemma}[Closed walk]
@@
     \end{lemma}
-  \begin{itemize}
-    \item Examine triples $(v,\ell,i)$:
-      \begin{itemize}
-        \item $v$: current vertex
-        \item $\ell$: port agent entered $v$ through
-        \item $i$: next step of the exploration sequence
-      \end{itemize}
-    \item Deterministically $(v,\ell,i) \leadsto (v',\ell',i')$
-    \item If $t_{1} = (v',\ell',i') \leadsto (v,\ell,i)$ and
-      $t_{2} = (v'',\ell'',i'') \leadsto (v,\ell,i)$: $t_{1} = t_{2}$
-    \item Only finite triples: projection to vertices yields closed walk
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Universal exploration of $3$-regular graphs}
+  \end{mdframed}
+  \uncover<2->{
+    \begin{mdframed}[linecolor=blue]
       \begin{lemma}[Periodic exploration sequence (PES-Lemma)]
-    There exists an $\mathcal{O}(\log n)$-space algorithm producing a universal
-    exploration sequence $(e_{1},\dots,e_{k})^{\ast}$ for any $3$-regular graph
-    with at most $n$ vertices.
+        There exists an $\mathcal{O}(\log n)$-space algorithm producing a
+        universal exploration sequence $(e_{1},\dots,e_{k})^{\ast}$ for any
+        $3$-regular graph with at most $n$ vertices.
       \end{lemma}
-  \begin{itemize}
-    \item Let $\mathcal{M}$ be the Turing machine from Reingold's Theorem
-    \item The exploration sequence computed by $\mathcal{M}$ is universial for
-      3-regular graphs with at most $n$ vertices
-      \alt<1-1>{
-        \begin{itemize}
-          \item Assume $3$-regular $G_{0}$ with $n_{0} < n$ vertices is not
-            explored
-          \item Then there is a vertex that is not traversed
-          \item Repeatedly apply \parbox{3\baselineskip}{\resizebox{!}
-            {3\baselineskip}{\input{tikz/blowup}}}
-          \item Until there are $n$ vertices which contradicts Reingold's
-            Theorem
-        \end{itemize}
-      }{
-      \item Produce a periodic universal exploration sequence
-        $(e_{1},\dots,e_{k})^{\ast}$
-        \uncover<2-2>{
-          \begin{itemize}
-            \item Construct $\mathcal{M}'$ which simulates $\mathcal{M}$ for
-              $3n\cdot c$ steps where $c$ is the number of configurations of
-              $M$
-            \item Output $e = (e_{1},\dots,e_{k})^{\ast}$
-            \item Assume $e$ is not universal; then it loops in $V'$ with
-              $|V'|<n$
-            \item $\mathcal{M}$ has to enter a vertex twice with the same
-              configuration
-            \item Contradicts universality of the exploration sequence of
-              $\mathcal{M}$
-          \end{itemize}
+    \end{mdframed}
   }
-      }
-  \end{itemize}
-  \pause
-  \pause
 \end{frame}
@@
   \frametitle{3-Regularity}
-  \begin{columns}
-    \column{0.5\textwidth}
-    \begin{itemize}
-      \item Establish 3-regularity
-        \begin{itemize}
-          \item Recall: \parbox{3\baselineskip}{\resizebox{!}
-            {3\baselineskip}{\input{tikz/blowup}}}
-          \item<2-> Transform $v$ to $3\cdot d_{v}$ distinct vertices
-        \end{itemize}
-    \end{itemize}
-    \column{0.5\textwidth}
-    \uncover<3->{\resizebox{\textwidth}{!}{\input{tikz/regsim}}}
-  \end{columns}
+  \begin{mdframed}[linecolor=green]
+    Establish 3-regularity
+  \end{mdframed}
+  \begin{center}
+    \uncover<2->{\resizebox{0.7\textwidth}{!}{\input{tikz/regsim}}}
+  \end{center}
 \end{frame}
@@
   \frametitle{Exploring pebble machine}
-  \begin{itemize}
-    \item Graph $G$
-    \item Transform to 3-regular $G_{\text{reg}}$
-    \item Applying PES-Lemma to $G_{\text{reg}}$ yields:
-  \end{itemize}
+  \begin{theorem}[Reingold]
+    There is an $\mathcal{O}(n)$-space algorithm producing a universal
+    exploration sequence for any regular graph on $n$ vertices.
+  \end{theorem}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (d1) {};
+      \node[below=2 of d1] (d2) {};
+      \draw[->, bend right] (d1) to (d2);
+      \node[rectangle, draw=green, below right=0.3 and 1 of d1]
+        {3-Regularity};
+      \node[rectangle, draw=blue, below right=1 and 1.2 of d1]
+        {Periodic Universal lemma};
+      \node[rectangle, draw=yellow, below right=1.7 and 1 of d1]
+        {Closed walk lemma};
+    \end{tikzpicture}
+  \end{center}
   \begin{theorem}
@@
   \begin{itemize}
-    \item Simulate tape of size $m$ by pebbles:
+    \item Simulate $m$ bits by pebbles:
       \begin{itemize}
-        \item<3-> Separate into memory blocks of size $m_{1}$
-        \item<4-> Represent every block by one of
-          $p_{0},\dots,p_{\frac{m}{m_{1}}-1}$ pebbles
+        \item<3-> Separate into $m_{1}$ sized blocks
+        \item<4-> Represent blocks by pebbles
+          $p_{0},\dots,p_{\frac{m}{m_{1}}-1}$
       \end{itemize}
@@
     \begin{itemize}
-      \item Every pebbles needs $2^{m_{1}}$ distinct \enquote{states}
-        \begin{itemize}
-          \item Placement on a walk with at least $2^{m_{1}}$ distinct vertices
-            yields \enquote{states}
-        \end{itemize}
+      \item Pebble needs $2^{m_{1}}$ distinct \enquote{states}
+      \item State as index of closed walk
     \end{itemize}
@@
   \frametitle{Mechanisms of simulation}
-  \begin{itemize}
-    \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
+  \begin{enumerate}
+    \item Simulation of $M_{\text{walk}}$ providing walk with $2^{m_{1}}$
       distinct vertices
-    \item Identify \emph{distinct} vertices of the walk
+    \item Identify \emph{distinct} vertices of walk
     \item Read from and write to simulated tape
     \item Preserve tape content through steps of simulated agent
-  \end{itemize}
+  \end{enumerate}
 \end{frame}
@@
 \begin{frame}
-  \frametitle{Simulation of $M_{\text{Walk}}$}
+  \frametitle{1. Simulation of $M_{\text{walk}}$}
   \begin{itemize}
-    \item $M_{\text{Walk}}$ can be implemented as
+    \item $M_{\text{Walk}}$ implemented as
       $(\mathcal{O}(1), 0, \mathcal{O}(m_{1}))$ pebble machine
@@
       \begin{itemize}
-        \item $\Twalk$: stores $M_{\text{Walk}}$'s tape
+        \item $\Twalk$: stores $M_{\text{walk}}$'s tape
         \item $\Tsteps$: stores number of taken steps
         \item $\Tid$: stores number of visited distinct vertices
-        \item $p_{\text{start}}$: marks the beginning
+        \item $p_{\text{start}}$: marks beginning of walk
       \end{itemize}
@@
 \begin{frame}
-  \frametitle{Finding distinct vertices}
+  \frametitle{2. Finding distinct vertices}
   Problem: Indistinguishable vertices $\leadsto$ next vertex \enquote{new}?
@@
     \begin{enumerate}
-      \item Execute step
-      \item Drop pebble $p_{\text{tmp}}$
-      \item Store $\Twalk$ in $T'_{\text{walk}}$
-      \item Restart $M_{\text{Walk}}$
-      \item Execute steps until $p_{\text{tmp}}$ is observed
-      \item If $\Twalk = T'_{\text{walk}}$ the vertex is new
-      \item Otherwise start over
+      \item \textcolor<3,8>{green}{Execute step}
+      \item \textcolor<4,9>{green}{Drop pebble $p_{\text{tmp}}$}
+      \item \textcolor<4,9>{green}{Store $\Twalk$ in $T'_{\text{walk}}$}
+      \item \textcolor<5,10>{green}{Restart $M_{\text{walk}}$}
+      \item \textcolor<6,11-18>{green}{Execute steps until $p_{\text{tmp}}$ is
+        observed}
+      \item \textcolor<19-20>{green}{If $\Twalk = T'_{\text{walk}}$ the vertex
+        is new (increase $\Tid$)}
+      \item \textcolor<7>{green}{Otherwise start over}
     \end{enumerate}
@@
 \begin{frame}
-  \frametitle{Memory management}
+  \frametitle{3. Memory management}
   \begin{columns}
@@
     \begin{itemize}
-      \item $\Thead$ stores head position
+      \item $\Thead$: head position
       \item $p_{\lfloor\frac{\Thead}{m_{1}}\rfloor}$: pebble of memory block
@@
 \begin{frame}
-  \frametitle{Memory management: Writing}
+  \frametitle{3. Memory management: Writing}
   \begin{itemize}
@@
 \begin{frame}
-  \frametitle{Transfer tape-content through movements}
+  \frametitle{4. Transfer tape-content through movements}
   \begin{itemize}
-    \item Simulated machine moves
+    \item Simulated agent moves
     \item Preserve tape-content:
       \begin{itemize}
-        \item Drop $p_{\text{next}}$ on next vertex
-        \item Transfer encoding pebbles onto walk $\omega'$ starting from
-          next vertex
-        \item Preserve \enquote{state} by placing at same index
+        \item Drop $p_{\text{next}}$ on next vertex $v$
+        \item $\omega'$ walk of $M_{\text{walk}}$ starting from $v$
+        \item Transfer encoding pebbles onto $\omega'$
+        \item Placing pebbles at same index
       \end{itemize}
@@
     \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
-      distinct vertices \uncover<2->{\checkmark}
+      distinct vertices \uncover<2->{\textcolor{green}{{\checkmark}}}
     \item Identify \emph{distinct} vertices of the walk
-      \uncover<3->{\checkmark}
-    \item Read from and write to simulated tape \uncover<4->{\checkmark}
+      \uncover<3->{\textcolor{green}{{\checkmark}}}
+    \item Read from and write to simulated tape \uncover<4->{\textcolor{green}{{\checkmark}}}
     \item Preserve tape content through steps of simulated agent
-      \uncover<5->{\checkmark}
+      \uncover<5->{\textcolor{green}{{\checkmark}}}
   \end{itemize}
@@
   \frametitle{Exploring graphs with $\log\log n$ pebbles}
-  \begin{itemize}
-    \item There is a $(c,0,c\cdot\log n)$ pebble machine which explores
-      a graph $G$ with $n$ vertices
-    \item Applying above simulation $\log \log n$ times yields
-      $(c'^{\log\log n}\cdot c, c'\cdot\log\log n, c)$ pebble machine exploring
-      $G$
+  \begin{theorem}
+    There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
+    with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$,
+    there exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates
+    the walk of $\mathcal{M}$ or explores $G$.
+  \end{theorem}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (d1) {};
+      \node[below=2 of d1] (d2) {};
+      \draw[->, bend right] (d1) to (d2);
+      \node[below right=0.8 and 1 of d1, rectangle,draw=black] {Apply simulation $\log\log n$ times};
+    \end{tikzpicture}
+  \end{center}
   \begin{theorem}
@@
   \end{theorem}
-  \end{itemize}
 \end{frame}
@@
   \begin{itemize}
-    \item Construct 3-regular graphs which cannot be traversed by an agent
-      $\mathcal{A}$ with $p$ pebbles
-    \item Such graphs are called $p$-barriers
+    \item Construct 3-regular graphs agent $\mathcal{A}$ with $p$ pebbles
+      cannot traverse
+    \item Called $p$-barriers
       \begin{center}
@@
       \end{center}
-    \item $\mathcal{A}$ cannot traverse a barrier from $v_{1}$ or $v_{2}$
+    \item $\mathcal{A}$ cannot traverse a $p$-barrier from $v_{1}$ or $v_{2}$
       to $v_{3}$ or $v_{4}$ or vice versa using at most $p$ pebbles
@@
   \begin{itemize}
-    \item Replace edge by a $(p-1)$-barrier
+    \item Replace edge by $(p-1)$-barrier
     \item Enforce \enquote{locality} of pebbles
-    \item An agent cannot traverse any gadget without \emph{all} his pebbles
-    \item All pebbles of the agent are either carried or placed within the
-      adjacent gadgets
       \begin{center}
@@
       \end{center}
-    \item<3-> Original vertices are called \emph{macro} vertices
   \end{itemize}
@@
     \begin{itemize}
-      \item Consider a subset of pebbles of cardinality $r$
-      \item Use the locality gadget as edges
-      \item Since pebbles are local: enumerate configurations in macro vertex
+      \item Subset of pebbles of cardinality $r$
+      \item Locality gadget as edges
+      \item Pebbles are local: configurations in macro vertex
         $C_{1},\dots,C_{\alpha}$
-      \item Project $A$ to a agent without pebbles $B$
-      \item $B$ has $\alpha$ states and traverses through macro vertices
+      \item Project $A$ to agent without pebbles $B$
+      \item $B$ has $\alpha$ states and traverses macro vertices
     \end{itemize}
@@
   \begin{itemize}
-    \item $B$ has no pebbles and is therefore prone to a $0$-barrier
-    \item Apply locality gadget to all edges
-    \item This yields a $p$-barrier for the chosen subset of pebbles
-    \item Iterate $p$-barriers for all possible subsets
+    \item $B$ has no pebbles and cannot traverse $0$-barrier
+    \item[$\rightarrow$] $p$-barrier for the chosen subset of pebbles:
+  \end{itemize}
   \begin{center}
-        \resizebox{0.7\textwidth}{!}{\input{tikz/iterbarrier}}
+    \resizebox{0.8\textwidth}{!}{\input{tikz/iterbarrier}}
   \end{center}
-  \end{itemize}
 \end{frame}
@@
   \frametitle{Barrier base case}
-  \begin{theorem}
+  \begin{theorem}[Fraigniaud et al.]
     For any $q$ non cooperative $s$-state agents without pebbles, there
@@
   \frametitle{Barrier size}
-  \begin{itemize}
-    \item Iterative construction
-  \end{itemize}
   \begin{center}
-    \resizebox{0.8\textwidth}{!}{\input{tikz/barriersize}}
+    \resizebox{\textwidth}{!}{\input{tikz/barriersize}}
   \end{center}
@@
 
+\section{Conclusion}
+\begin{frame}
+  \frametitle{Conclusion}
+  \begin{itemize}
+    \item Exploring graphs with $\mathcal{O}(\log\log n)$ pebbles and memory
+    \item Simulation via pebbles
+    \item Limitations of pebbles: Barrier construction
+  \end{itemize}
+\end{frame}
+
 \begin{frame}

### 2016-05-10 tikz/barriersize.tex
slides alpha

@@
   \node[node,below=3 of b0r0] (b0r1) {};
-  \node[fit=(b0l0) (b0l1) (b0r0) (b0r1),draw=black,label={90:\huge{$H_{1}$}}] (b0) {};
+  \node[fit=(b0l0) (b0l1) (b0r0) (b0r1),draw=black,label={90:\Huge{$H_{1}$}}, inner sep=15mm] (b0) {};
   \draw[dashed, thick] (b0.north) to (b0.south);
 
-  \node[node,right=of b0r0] (b1l0) {};
+  \node[node,right=4 of b0r0] (b1l0) {};
   \node[node,below=3 of b1l0] (b1l1) {};
@@
   \node[node,below=3 of b1r0] (b1r1) {};
-  \node[fit=(b1l0) (b1l1) (b1r0) (b1r1),draw=black,label={90:\huge{$H_{2}$}}] (b1) {};
+  \node[fit=(b1l0) (b1l1) (b1r0) (b1r1),draw=black,label={90:\Huge{$H_{2}$}}, inner sep=15mm] (b1) {};
   \draw[dashed, thick] (b1.north) to (b1.south);
 
-  \node[below right=0.1 and 1.3 of b1l0]   (i0) {};
-  \node[below=1.5 of i0]     (i1) {};
+  \node[above right=1 and 1.2 of b1l0]   (i0) {};
+  \node[below=1 of i0]     (i1) {};
   \node[right=3 of i0] (i2) {};
-  \node[below=1.5 of i2]     (i3) {};
-  \node[fit=(i0) (i1) (i2) (i3), draw=black, rectangle, label={90:\huge{$B_{r-1}$}}] (Br2) {};
+  \node[below=1 of i2]     (i3) {};
+  \node[fit=(i0) (i1) (i2) (i3), draw=black, rectangle] (Br2) {\Huge{$B_{r-1}$}};
 
-  \node[below right=0.08 and 0.3 of i0] (i4) {\huge{$\ddots$}};
-  \node[below =0.1 of i4] (i5) {};
-  \node[right =0.3 of i4]     (i6) {};
-  \node[below =0.1 of i6] (i7) {};
-  \node[fit=(i4) (i5) (i6) (i7), draw=black, rectangle] (Br3) {};
+  \node[below right=0.6 and 1.2 of b1l0]   (i4) {};
+  \node[below=1 of i4]     (i5) {};
+  \node[right=3 of i4] (i6) {};
+  \node[below=1 of i6]     (i7) {};
+  \node[fit=(i4) (i5) (i6) (i7), draw=black, rectangle] (Br3) {\Huge{$B_{r-1}$}};
 
-  \node[minimum size=12mm,circle,right=of b1r0] (b2l0) {};
+  % \node[below right=0.08 and 0.3 of i0] (i4) {\Huge{$\ddots$}};
+  % \node[below =0.1 of i4] (i5) {};
+  % \node[right =0.3 of i4]     (i6) {};
+  % \node[below =0.1 of i6] (i7) {};
+  % \node[fit=(i4) (i5) (i6) (i7), draw=black, rectangle] (Br3) {};
+
+  \node[minimum size=12mm,circle,right=2 of b1r0] (b2l0) {};
   \node[minimum size=12mm,circle,below=3 of b2l0] (b2l1) {};
-  \node[minimum size=12mm,circle,right=of b2l0] (b2r0) {};
+  \node[minimum size=12mm,circle,right=2 of b2l0] (b2r0) {};
   \node[minimum size=12mm,circle,below=3 of b2r0] (b2r1) {};
 
-  \node[node,right=of b2r0] (b3l0) {};
+  \node[node,right=3 of b2r0] (b3l0) {};
   \node[node,below=3 of b3l0] (b3l1) {};
-  \node[node,right=of b3l0] (b3r0) {};
+  \node[node,right=3 of b3l0] (b3r0) {};
   \node[node,below=3 of b3r0] (b3r1) {};
-  \node[fit=(b3l0) (b3l1) (b3r0) (b3r1),draw=black,label={90:\huge{$H_{{p}\choose{r}}$}}] (b2) {};
+  \node[fit=(b3l0) (b3l1) (b3r0) (b3r1),draw=black,label={90:\Huge{$H_{{p}\choose{r}}$}},inner sep=15mm] (b2) {};
   \draw[dashed, thick] (b1.north) to (b1.south);
@@
   \draw[dashed] (b1l0) to (Br2.west);
+  \draw[dashed] (b1l0) to (Br3.west);
 
-  \node[fit=(b0) (b1) (b2), draw=black, label={90:\huge{$B$}},inner sep=12mm] (b) {};
+  \node[fit=(b0) (b1) (b2), draw=black, label={90:\Huge{$B_{r}$}},inner sep=15mm] (b) {};
 \end{tikzpicture}

### 2016-05-10 tikz/portex.tex
slides alpha

@@
 \begin{tikzpicture}
-  \node[node] (m1) {$v_{1}$};
-  \node[node,right=2cm of m1] (m2) {$v_{2}$};
+  \node[node] (m1) {};
+  \node[node,right=2cm of m1] (m2) {};
 
@@
 
-  \draw[edge] (m1) to node[very near start, above] {0} (e1);
-  \draw[edge] (m1) to node[near start, left] {2} (e2);
+  \draw[edge] (m1) to node[very near start, above] {\textcolor{green}{0}} (e1);
+  \draw[edge] (m1) to node[near start, left] {\textcolor{green}{2}} (e2);
 
-  \draw[edge] (m2) to node[very near start, above] {1} (e3);
-  \draw[edge] (m2) to node[near start, right] {2} (e4);
+  \draw[edge] (m2) to node[very near start, above] {\textcolor{green}{1}} (e3);
+  \draw[edge] (m2) to node[near start, right] {\textcolor{green}{2}} (e4);
 
-  \draw[edge] (m1) to node[very near start, below] {1} node[very near end, above] {0} (m2);
+  \draw[edge] (m1) to node[very near start, below] {\textcolor{green}{1}} node[very near end, above] {\textcolor{green}{0}} (m2);
 \end{tikzpicture}

### 2016-05-10 tikz/regsim.tex
slides alpha

@@
 \begin{tikzpicture}
-  \node[node] (m1) {$v_{1}$};
-  \node[node] (m2) [right = 4cm of m1] {$v_{2}$};
-  \node[node] (m3) [right = 4cm of m2] {$v_{3}$};
+  \node[node] (m1) {};
+  \node[node] (m2) [right = 4cm of m1] {};
+  \node[node] (m3) [right = 4cm of m2] {};
 
@@
 
-  \node[node] (r11) [below = 6cm of m1] {$(v_{1},0)$};
-  \node[node] (r12) [above = 2cm of r11] {$(v_{1},1)$};
-  \node[node] (r13) [below = 2cm of r11] {$(v_{1},2)$};
+  \begin{scope}[on background layer]
+    \node[fit=(m1),fill=green!50] (cl1) {};
+    \node[fit=(m2),fill=yellow!50] (cl2) {};
+    \node[fit=(m3),fill=red!50] (cl3) {};
+  \end{scope}
 
-  \node[node] (l11) [below = 6cm of m3] {$(v_{3},0)$};
-  \node[node] (l12) [above = 2cm of l11] {$(v_{3},1)$};
-  \node[node] (l13) [below = 2cm of l11] {$(v_{3},2)$};
+  \uncover<3->{
+    \node[node] (r11) [below = 6cm of m1] {$0$};
+    \node[node] (r12) [above = 2cm of r11] {$1$};
+    \node[node] (r13) [below = 2cm of r11] {$2$};
+
+    \node[node] (l11) [below = 6cm of m3] {$0$};
+    \node[node] (l12) [above = 2cm of l11] {$1$};
+    \node[node] (l13) [below = 2cm of l11] {$2$};
 
     \node       (anker) [below = 6.5cm of m2] {};
-  \node[node] (mid0) [above right = 1cm and 1cm of anker] {$(v_{2},0)$};
-  \node[node] (mid1) [below right = 1cm and 1cm of anker] {$(v_{2},1)$};
-  \node[node] (mid2) [below = 3cm of anker] {$(v_{2},2)$};
-  \node[node] (mid3) [below left = 1cm and 1cm of anker] {$(v_{2},3)$};
-  \node[node] (mid4) [above left = 1cm and 1cm of anker] {$(v_{2},4)$};
-  \node[node] (mid5) [above = 3cm of anker] {$(v_{2},5)$};
+    \node[node] (mid0) [above right = 1cm and 1cm of anker] {$0$};
+    \node[node] (mid1) [below right = 1cm and 1cm of anker] {$1$};
+    \node[node] (mid2) [below = 3cm of anker] {$2$};
+    \node[node] (mid3) [below left = 1cm and 1cm of anker] {$3$};
+    \node[node] (mid4) [above left = 1cm and 1cm of anker] {$4$};
+    \node[node] (mid5) [above = 3cm of anker] {$5$};
 
@@
 
+    \only<3>{
+      \begin{scope}[on background layer]
+        \node[fit=(r11) (r12) (r13),fill=green!50] (cl1b) {};
+        \node[fit=(mid0) (mid1) (mid2) (mid3) (mid4) (mid5),fill=yellow!50] (cl2b) {};
+        \node[fit=(l11) (l12) (l13),fill=red!50] (cl3b) {};
+        \draw[draw=green!50] (cl1.south west) to (cl1b.north west);
+        \draw[draw=green!50] (cl1.south east) to (cl1b.north east);
+        \draw[draw=yellow!50] (cl2.south west) to (cl2b.north west);
+        \draw[draw=yellow!50] (cl2.south east) to (cl2b.north east);
+        \draw[draw=red!50] (cl3.south west) to (cl3b.north west);
+        \draw[draw=red!50] (cl3.south east) to (cl3b.north east);
+      \end{scope}
+    }
+  }
+
 \end{tikzpicture}

### 2016-05-11 paper/main.tex
began rewriting text shizzle

@@
 \newtheorem{thm}{Theorem}
+\newtheorem{definition}{Definition}
 \newtheorem{lem}{Lemma}
-\newtheorem{ex}{Exercise}
+\newtheorem{prop}{Proposition}
 
@@
 
+\input{tikz/settings}
+
 \begin{document}
-
-\input{tikz/settings}
 
@@
 
-\title{A \emph{Grimm} idea}
-\subtitle{Exploring graphs with pebbles}
+\title{Exploring graphs with pebbles}
+\subtitle{A \emph{Grimm} idea}
 \author{Christoph Welzel}
 \maketitle
-
-\begin{abstract}
-  In this paper we re-present and explain an approach on exploring large
-  undirected graphs with the help of markers, so called pebbles, for vertices.
-  We focus on the central ideas of this approach and explain why it is possible
-  to traverse any graph with $n$ vertices with $\Theta(\log \log n)$ pebbles
-  and the same amount of memory.
-\end{abstract}
 
@@
 \section{Introduction}
-Traversing large graphs is an interesting challenge. In times of the internet
-web crawlers have to traverse immense graphs but also regarding complexity
-theory this is an interesting problem. First we will informally introduce two
-complexity classes to illustrate the importance of graph traversal from a
-complexity point of view: $L$ as the class of problems that can be solved by
-a deterministic Turing machine with additional memory of logarithmic amount
-of the input. And $SL$ as the class of problems that can be solved with the
-same space requirements but by a non-deterministic symmetrical Turing machine,
-where symmetrical means that for every computation step of the Turing machine
-there is a computation step to undo the previous one. As it turns out checking
-if two vertices $s$ and $t$ are connected in an undirected graph is a problem
-that is complete for $SL$. This problem is often refered to as
-$\mathrm{USTCON}$ and \citeauthor{logspacealg} showed in \cite{logspacealg}
-that $\mathrm{USTCON}\in L$ which collapsed $SL$ into $L$, hence $SL = L$.
-In the following we will present the results from \cite{pebbles} where another
-mechanism of graph exploration is used: with the use of pebbles which are small
-pieces of memory that can be dropped on and collected from the vertex as an
-agent traverses the graph. As we will show it is possible to traverse a graph
-with $n$ vertices with $\mathcal{O}(\log\log n)$ memory and the same amount of
-pebbles. Furthermore we will explain why there is no smaller amount of memory
-or pebbles to generally obtain the same guarantee to traverse all $n$ vertices.
 
 \section{Preliminaries}
-For the course of this paper we assume the following: Firstly, the vertices can
-not be distinguished by the traversing agent. But as the agent moves on a
-vertex it can compute its degree. Secondly, the edges attached to the vertex
-can be locally distinguished and are enumerated with the indices
-$\left\{0,\dots,d_{v}-1\right\}$ where $d_{v}$ denotes the degree of the vertex
-$v$. We refer to the \enquote{index} of the edge as its \emph{port}. Note that
-every edge thus has two different ports and furthermore that there is no
-relation between the ports is assumed. Additionally the degree of the
-considered graphs are assumed to be limited by a constant $\Delta$ and that
-there are only a finite amount of vertices.
+For the further course we assume the following: Firstly, the considered
+graphs are finite but huge. The considered agents have limited memory and can
+therefore not compute the identifier of vertices. This makes all vertices
+indistinguishable for the agents. Also, the degree of the vertices is bounded
+by a constant $\Delta$. For every vertex $v$ we assume that the connected edges
+can be locally enumerated with labels $0,\dots,d_{v} - 1$ where $d_{v}$ is the
+degree of $v$. These edge-labels are called ports and every edge has one port
+for both vertices it connects. Note that there is no relation between these
+ports is presumed.
 
-\section{Pebble machines}
-We are now ready to introduce the model of pebble machines. It closely
-follows the notion of Turing machines but adds mechanisms to model the
-movements of the agent. The presented model of pebble machines thus have
+\section{Graph exploration}
+We begin this section by formally defining our agents in the form of
+\emph{pebble machines}. This definition closely follows the notion of Turing
+machines but adds mechanisms to model the movements of the agent.
+\begin{definition}[Pebble machine]
+  A $(s,p,m)$-\emph{pebble machine} $\mathcal{M}$ is defined as a tuple
+  $(Q,F,P,m,\delta,\din,\dout,q_{0})$. Here we have
   \begin{enumerate}
-  \item a finite set of states $Q$
+    \item a finite set of states $Q$ with cadinality $s$
     \item a finite set of final states $F\subseteq Q$
-  \item a finite set of distinguishable pebbles $P$
-  \item a length of the used memory tape $m$
+    \item a finite set of distinguishable pebbles $P$ with cardinality $p$
+    \item the length of the available memory tape $m$
     \item a computation function $\delta$
@@
   where formally the computation function models the behaviour of the pebble
-machine as follows:
+  machine as
   \begin{equation*}
@@
   with the typical understanding of the computation of a Turing machine.
-As an agent traverses a vertex it is aware of the pebbles it carries
-around, it observes the set of pebbles on the vertex and the degree of the
-vertex and it furthermore aware of the port that it entered through.
-Thus we use
+  Furthermore
   \begin{equation*}
@@
   \end{equation*}
-to model this behaviour. And finally as the agent leaves a vertex it leaves
-a set of pebbles behind, picks up another set and chooses the port it leaves
-through. We choose to model this behaviour as
+  models how a pebble machine moves upon a vertex $v$ with
+  $\din(q,P_{1},P_{2},d,\ell) = q'$ where $q$ is the current state of
+  $\mathcal{M}$, $P_{1}$ the set of pebbles it carries, $P_{2}$ the set
+  of pebbles located on $v$, $d$ is the degree of $v$ and $\ell$ the port
+  through which $\mathcal{M}$ enters $v$. Then $\mathcal{M}$ starts its
+  computation according to $\delta$ in state $q'$.
+
+  $\dout$ is defined as
   \begin{equation*}
@@
   \end{equation*}
-Of course we also demand consistency of the pebbles, i.e. that if the agent
-carried $P_{1}\subseteq P$ and found $P_{2}\subseteq P$ it is necessary that
-$P_{1}$ and $P_{2}$ are disjoint and furthermore that if the agent leaves
-carrying $P'_{1}$ and leaving $P'_{2}$ behind those sets are disjoint and
-$P_{1}\cup P_{2} = P'_{1}\cup P'_{2}$.
+  where $\dout(q) = (P_{1}, P_{2}, \ell)$ defines that $\mathcal{M}$ leaves
+  a vertex $v$ through port $\ell$ dropping the pebbles in $P_{1}$ onto $v$
+  and carrying the pebble in $P_{2}$.
 
-\section{Graph exploration}
+  We additionally demand consistency of pebbles, i.e. that if the agent
+  carried the pebbles in $P_{1}\subseteq P$ and found the pebbles in
+  $P_{2}\subseteq P$ it is necessary that $P_{1}$ and $P_{2}$ are disjoint and
+  furthermore that if the agent leaves carrying $P'_{1}$ and leaving $P'_{2}$
+  behind those sets are disjoint and $P_{1}\cup P_{2} = P'_{1}\cup P'_{2}$.
+\end{definition}
+
 In order to describe the movement of an agent we introduce the notion of an
-exploration sequence as $e_{0}, e_{1},\dots$ which models relative movements
-as follows. We use a sequence of variables $l_{0},l_{1},\dots$ which denotes
-the port a vertex was entered through. And the next vertex is determined as the
-one connected to the port $(l_{i} + e_{i}) \mod d_{v_{i}}$. We define
-$l_{0} = 0$ and the notion $(e_{0},\dots,e_{k})^{\ast}$ for periodic sequences.
-It can be shown that a periodic sequence produces a closed walk through a
-graph.
-\begin{proof}
-  We argue that there is only a finite amount of triples of the
-  form $(v,l,i)$ where currently the agent is on vertex $v$, entered
-  this vertex through port $l$ and is currently at index $i$ of the exploration
-  sequence. For two triples $(v',l',i')$ and $(v'',l'',i'')$ that both lead to
-  $(v,l,i)$ it is easy to see, that $(v',l',i') = (v'',l'',i'')$. Thus, for
-  every triple there is a unique predecessor and successor which implies due to
-  the finiteness of the triples $(v,l,i)$ and because the agent moves
-  infinitely that the first triple has to be valid infinitly often.
-  This means a periodic exploration sequence yields a closed walk.
-\end{proof}
+exploration sequence as $e_{0}, e_{1},\dots$ which define relative movements:
+Let $\ell = \ell_{0},\ell_{1},\dots$ be a sequence of variables where
+$\ell_{i}$ denotes the port which a vertex $v$ was entered through. Then an
+agent following $\ell$ leaves through port
+$(\ell_{i} + e_{i}) \mod d_{v}$. We define $\ell_{0} = 0$ and the notion
+$(e_{0},\dots,e_{k})^{\ast}$ for periodic exploration sequence.
 
-From the following result of \cite{logspacealg} we present how we can obtain
-an $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine that finds a closed
-walk of at least $n$ distinct vertices in any graph with bounded degree.
-\begin{thm}
+Beginning from the following result of \cite{logspacealg} we present how we can
+obtain an $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine that walks
+along a closed walk of at least $n$ distinct vertices in any graph with bounded
+degree.
+\begin{thm}[Reingold]
   \label{thm:logalg}
-There is an algorithm $M\in L$ which produces a universal exploration sequence
-for every regular graph with $n$ vertices.
+  There is an $\mathcal{O}(\log n)$-space algorithm producing a universal
+  exploration sequence for any regular graph on $n$ vertices.
 \end{thm}
-First we argue that we can use this algorithm to find a universal exploration
-sequence of the form $e=(e_{0},\dots,e_{k})^{\ast}$ that traverses $n$ distinct
-vertices for any 3-regular graph and requires only $\mathcal{O}(\log n)$
-memory. Therefore we rely on the traversal sequence of $M$ from Theorem
-\ref{thm:logalg} and take from that the first $k:=3n\cdot c$ indices where
-$c$ denotes the number of configurations of $M$. We can now be assured that
-$e$ actually is a universal traversal sequence for any 3-regular graph because
-otherwise $M$ would have already looped in a strict subset of vertices of some
-3-regular graph. This contradicts that $M$ produces a universal exploration
-sequence for any graph with $n$ vertices.
 
@@
   \label{fig:3reg}
-  \resizebox{0.5\textwidth}{!}{\input{tikz/regsim}}
+  \resizebox{0.5\textwidth}{!}{\input{tikz/regtrans}}
 \end{wrapfigure}
@@
 then enjoy the following exercise:
-\begin{ex}
+\begin{prop}
   Given a $p$-barrier with $m$ vertices for a agent $A$ with $p$ pebbles.
   Construct a trap for $A$ (with $2m+4$ vertices). 
-\end{ex}
+\end{prop}
 

### 2016-05-11 presentation/main.tex
began rewriting text shizzle

@@
       \item Leaving port: $\ell_{i} + e_{i}\mod d_{v}$
-      \item \emph{Universial} for a class of graphs if it explores any graph of
+      \item \emph{Universal} for a class of graphs if it explores any graph of
         that class
@@
   \begin{theorem}[Reingold]
-    There is an $\mathcal{O}(n)$-space algorithm producing a universal
+    There is an $\mathcal{O}(\log n)$-space algorithm producing a universal
     exploration sequence for any regular graph on $n$ vertices.
@@
         \node[rectangle, draw=blue, below right=1 and 1.2 of d1]
-        {Periodic Universal lemma};
+        {Periodic Universal Lemma};
       }
@@
         \node[rectangle, draw=yellow, below right=1.7 and 1 of d1]
-        {Closed walk lemma};
+        {Closed walk Lemma};
       }
@@
     \begin{mdframed}[linecolor=blue]
-      \begin{lemma}[Periodic exploration sequence (PES-Lemma)]
+      \begin{lemma}[Periodic Universal Lemma]
         There exists an $\mathcal{O}(\log n)$-space algorithm producing a
@@
   \begin{theorem}
-    There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
+    There is a constant $c\in\mathbb{N}$, such that for any graph $G$
     with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
@@
         \item Transfer encoding pebbles onto $\omega'$
-        \item Placing pebbles at same index
+        \item Place pebbles at same index
       \end{itemize}
@@
     \begin{theorem}
-      There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
+      There is a constant $c\in\mathbb{N}$, such that for any graph $G$
       with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$,
@@
   \begin{theorem}
-    There is a constant $c\in\mathbb{N}$, such that for any Graph $G$
+    There is a constant $c\in\mathbb{N}$, such that for any graph $G$
     with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$,
@@
       \draw[->, bend right] (d1) to (d2);
-      \node[below right=0.8 and 1 of d1, rectangle,draw=black] {Apply simulation $\log\log n$ times};
+      \node[below right=0.8 and 1 of d1, rectangle,draw=black] {Apply simulation Theorem $\log\log n$ times};
     \end{tikzpicture}
@@
   \begin{itemize}
-    \item Construct 3-regular graphs agent $\mathcal{A}$ with $p$ pebbles
+    \item Construct 3-regular graphs which agent $\mathcal{A}$ with $p$ pebbles
       cannot traverse
@@
 \begin{frame}
-  \frametitle{Barrier construction: Initial thoughts}
+  \frametitle{Barrier construction: Idea}
   \begin{columns}

### 2016-05-11 paper/main.tex
adj

@@
 \end{thm}
+At first we show that an agent which follows a periodic exploration sequence
+moves along a closed walk.
+\begin{lem}[Closed Walk Lemma]
+  An agent following an exploration sequence of the form
+  $(e_{0},\dots,e_{k-1})^{\ast}$ in an undirected graph moves along a closed
+  walk.
+\end{lem}
+\begin{proof}
+  We therefore consider a graph with vertices of the form $(v,\ell,i)$ which
+  denote that the agent entered in the original graph vertex $v$ through port
+  $\ell$ and that the next element of the exploration sequence is $i$. For the
+  edges we consider movements of the agent from the configuration given by the
+  current vertex $(v,\ell,i)$. It is easy to see that for a vertex $(v,\ell,i)$
+  the next vertex is deterministically chosen and is therefore unique. We
+  furthermore argue that there is at most one predecessor for every vertex.
+  ...
+\end{proof}
 

### 2016-05-11 paper/main.tex
write up completed, have to shorten here and there

@@
-\documentclass[draft,oneside]{scrartcl}
+\documentclass[oneside]{scrartcl}
 
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{amsthm}
@@
 \section{Introduction}
+In the following we present the main results from \cite{pebbles}. These are
+how to systematically traverse graphs of a very large size by agents. Such
+agents are located on vertices of the graph and move along the edges. Because
+the memory of the agents is very limited we allow agents to use a set of
+distinguishable devices, called pebbles, which can be left on vertices and
+regained by another visit on the same vertex. As we will see this is a very
+rewarding extension since it is possible to obtain very low memory consumption
+for the agents.
 
@@
   furthermore argue that there is at most one predecessor for every vertex.
-  ...
+  Examine therefore two vertices $(v',\ell',i')$ and $(v'',\ell'',i'')$ which
+  lead to $(v,\ell,i)$. Both enter $v$ by $\ell$ thus $v' = v''$. Furthermore
+  it is clear that $i' + 1 \mod k = i = i'' + 1 \mod k$ which implies
+  $i' = i''$. Concludingly,
+  $\ell' + e_{i'} \mod d_{v'} = \ell'' + e_{i''} \mod d_{v''}$ and since
+  $v' = v''$ and $e_{i'} = e_{i''}$ and $\ell',\ell'' < d_{v'} = d_{v''}$
+  it follows that $\ell' = \ell''$.
+  Because now every vertex has one outgoing and at most one incoming edge 
+  a walk starting in $(v_{0},0,0)$ must loop
+  because there are only finitly many triples $(v,\ell,i)$ but the agent moves
+  infinitly. Projecting this walk to the first component yields a closed walk
+  on the original graph.
 \end{proof}
+In the following we can show that the algorithm from Theorem \ref{thm:logalg}
+can be adapted to output a periodic universal exploration sequence for every
+graph with up to $n$ vertices.
+\begin{lem}[Periodic Universal Lemma]
+  \label{lem:pul}
+  There exists an $\mathcal{O}(\log n)$-space algorithm producing a universal
+  exploration sequence $(e_{0},\dots,e_{k-1})^{\ast}$ for any 3-regular graph
+  with at most $n$ vertices.
+\end{lem}
+\begin{proof}
+  Let $\mathcal{M}$ be the TM of Theorem \ref{thm:logalg}.
+  At first we show that the exploration sequence produced by $\mathcal{M}$ is
+  universal for every graph with at most $n$ vertices. Assume therefore there
+  is a 3-regular graph with $n_{0} < n$ vertices for which $\mathcal{M}$
+  produces a non universal exploration sequence. Note that $n_{0}$ is even
+  because every 3-regular graph has an even amount of nodes by the Handshaking
+  lemma. Then there is a vertex $v$ which is not explored. We can now
+  repeatedly apply the following construction:
+  \begin{center}
+    \parbox{3\baselineskip}{\resizebox{!}{3\baselineskip}{\input{tikz/blowup}}}
+  \end{center}
+  Thus, we added 2 vertices which are also not explored. This can be iterated
+  until there are $n$ vertices for which all added vertices are not explored
+  contradicting Theorem \ref{thm:logalg}.
 
-We can now find the $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine we
-are looking for.
-\begin{thm}
-  \label{thm:pebblewalk}
-  There is a $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine which
-  explores every given graph $G$ with bounded degree $\Delta$ either completly
-  or at least loops on $n$ distinct vertices.
-\end{thm}
+  Secondly, we show that we can construct a TM $\mathcal{M}'$ which simulates
+  $\mathcal{M}$ until it produced a exploration sequence of length $3n\cdot c$
+  where $c$ is the number of configurations of $\mathcal{M}$. $\mathcal{M}'$
+  outputs now $(e_{0},\dots,e_{k-1})^{\ast}$ which is universal for any
+  3-regular graph with $n$ vertices. If we assume that it is not we can
+  conclude that we loop in a set of vertices $V'$ for which $|V'|<n$. By a
+  simple combinatorial argument we see that the produced exploration sequence
+  of $\mathcal{M}$ therefore always loops in $V'$ because an agent following
+  the produced exploration sequence would have entered a vertex twice by the
+  same port whilst $\mathcal{M}$ was in the same configuration.
+\end{proof}
 \begin{wrapfigure}{r}{0.5\textwidth}
@@
   \label{fig:3reg}
-  \resizebox{0.5\textwidth}{!}{\input{tikz/regtrans}}
+  \flushright{\resizebox{0.4\textwidth}{!}{\input{tikz/regtrans}}}
 \end{wrapfigure}
-\begin{proof}
-  The main idea is to use the adapted algorithm $A$ to find for an
-  universal exploration sequence for a 3-regular graph from above. Therefore
-  we take $G$ and transform it to a 3-regular graph on which $A$ finds the
-  corresponding universal exploration sequence. The transformation replaces
-  any node $v$ with degree $d$ by $3d$ nodes which then form a circle where
-  every nodes has degree $3$. The edges of $v$ are moved to nodes in the
-  circle. Specifically the edge with port $i$ is replaced by 3 edges which are
-  attached to $(v,i), (v,i+d), (v,i+2d)$. (Note that the other
-  vertex attached to the edge is replaced by the same construction and therfore
-  offers enough ports for the newly introduced edges.) Figure \ref{fig:3reg}
-  illustrates this construction.  This simulation yields at most
-  $3\Delta n^{2}$ many nodes and can be emulated with $\mathcal{O}(1)$ many
-  memory space since it is only needed to store the second component of the
-  inserted nodes which is bounded by $3\Delta$. Furthermore $A$ can be run on
-  this constructed Graph and only needs $\mathcal{0}(\log n)$ space since
-  $\mathcal{O}(\log(3\Delta n^{2})) = \mathcal{O}(\log(3) + \log(\Delta) +
-  2\log(n)) = \mathcal{O}(\log n)$. Which yields the desired
-  $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine.
+These lemmata are used in \cite{pebbles} to give the following theorem.
+\begin{thm}
+  \label{thm:pebblewalk}
+  There exists a $(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine
+  that moves along a closed walk and either explores the graph or visits
+  at least $n$ distinct vertices, for any graph with bounded degree.
+\end{thm}
+\begin{proof}[Sketch]
+  The TM constructed in Lemma \ref{lem:pul} is used as the desired pebble
+  machine. But first the graph has to be transformed to be 3-regular.
+  We refer therefore to Figure \ref{fig:3reg} which shows how every vertex $v$
+  can be replaced by $3\cdot d_{v}$ vertices which only have 3 edges. It is
+  furthermore noteworthy that this transformation can be emulated with
+  $\mathcal{O}(\log n)$ memory because of the regular structure of the
+  transformation (moving along port 0 or 1 stays in the gadget and only
+  moving along port 2 changes the actual vertex). For details we refer to
+  \cite{pebbles}.
 \end{proof}
 
-In order to obtain the desired boundary of $\log\log n$ space and $\log\log n$
-pebbles we show that a pebble machine can be simulated by storing its tape
-content by pebbles that are placed on a closed walk.
+\section{Simulation}
+In the following we present possibly the most interesting result from
+\cite{pebbles}. A simulation of a pebble machine which allows to store
+the tape content of the simulated pebble machine as pebbles placed on a
+defined walk within a graph.
 \begin{thm}
   \label{thm:simulation}
-  For every graph $G$ a $(s,p,2m)$ pebble machine $M$ can be simulated by
-  a $(cs,p + c,m)$ pebble machine that simulates the walk of $M$ or explores
-  $G$.
+  There is a constant $c\in\mathbb{N}$, such that for any graph $G$ with
+  bounded degree and any $(s,p,2m)$-pebble machine $\mathcal{M}$, there
+  exists a $(cs,p+c,m)$-pebble machine $\mathcal{M}'$ that simulates the
+  walk of $\mathcal{M}$ or explores $G$.
 \end{thm}
@@
   the bits $im_{1},\dots,(i+1)m_{1}-1$. It is therefore necessary that every
-  pebble can encode $2^{m_1}$ different states. Therefore we use a closed walk
+  pebble can encode $2^{m_1}$ different states. For this we use a closed walk
   $\omega$ which visits at least $2^{m_1}$ distinct vertices yielding $2^{m_1}$
@@
 \end{proof}
+
 As Theorem \ref{thm:pebblewalk} yields a $(c,0,c\cdot\log n)$ pebble machine
 that explores a given graph we can now repeatedly apply the simulation
-from Theorem \ref{thm:simulation} (precisely $\log\log n$ times) and end up
-with a $(c'^{\log\log n}\cdot c, \log\log n\cdot c',
-\frac{c}{2^{\log\log n}}\log n) =
-(c'^{\log\log n}\cdot c, \log\log n\cdot c', c)$ pebble machine exploring the
-graph.
+from Theorem \ref{thm:simulation} (precisely $\log\log n$ times) and obtain
+a $(c'^{\log\log n}\cdot c, \log\log n\cdot c', c)$-pebble machine exploring
+the graph as the following theorem from \cite{pebbles} states.
+\begin{thm}
+  Any bounded-degree graph of at most $n$ vertices can be explored using
+  $\mathcal{O}(\log \log n)$ pebbles and memory.
+\end{thm}
 
 \section{Barriers}
-In the following we will discuss the limits of the exploration approach with
-pebbles. Specifically, we will argue that we can construct 3-regular graphs
-that any agent with $p$ pebbles cannot traverse. Such graphs are called
-$p$-barriers.
-Note that connecting a 3-regular graph might violate its 3-regularity.
-Therefore we rely on having a distinguishable edge $e$ in the 3-regular graph
-which we can delete to connect the vertices $e$ connected to the
-\enquote{outside}. This preserves the 3-regularity. The interested reader might
-then enjoy the following exercise:
-\begin{prop}
-  Given a $p$-barrier with $m$ vertices for a agent $A$ with $p$ pebbles.
-  Construct a trap for $A$ (with $2m+4$ vertices). 
-\end{prop}
+In the following we lead through the discussion in \cite{pebbles} of the limits
+of the exploration approach with pebbles. Specifically, we will argue that
+there are 3-regular graphs that any agent with $p$ pebbles cannot traverse.
+Such graphs are called $p$-barriers.
 
-\begin{wrapfigure}{r}{0.4\textwidth}
-  \caption{Gadget construction that ensures locality of pebbles.}
-  \label{fig:gadget}
-  \resizebox{0.4\textwidth}{!}{\input{tikz/gadget}}
-\end{wrapfigure}
-The construction of barriers is inductively and therefore requires that the
-base case can be constructed directly. Fortunately Theorem 4 in \cite{0barrier}
-yields a graph which can be adapted to a 0-barrier. With this in mind we
-introduce a gadget construction for a given $r$-barrier $B$ as it can be seen
-in Figure \ref{fig:gadget}. Replacing edges of a graph with
-such gadgets enforces, in a sense, \enquote{locality} of pebbles. We call
-the verices that are connected by the gadget macro-vertices and if a $r+1$
-pebble machine stands on a macro vertex we can safely be assured that all
-pebbles are either carried by the agent or are placed within the adjacent
-\enquote{edges} because otherwise the agent has left a pebble across of an
-$r$-barrier and crossed the barrier with $r$ pebbles contradicting that it is
-in fact an $r$-barrier. This observation can be used to construct an
-$r$-barrier given a $(r-1)$-barrier is known.
+This construction of barriers is iteratively and relies on a result from
+\cite{0barrier}.
 \begin{thm}
-  With a given $(r-1)$-barrier for an agent $A$ a $r$-barrier can be
-  constructed.
+  For any $q$ non-cooperative $s$-state agents without pebbles, there exists
+  a 3-regular graph $G$ on $\mathcal{O}(qs)$ vertices with the following
+  property: There are two edges $\left\{v_1,v_2\right\}$ and
+  $\left\{v_3,v_4\right\}$ in $G$, the first labeled 0, such that any of the
+  $q$ agents starting in $v_1$ or $v_2$ does not traverse the edge
+  $\left\{v_3,v_4\right\}$.
+\end{thm}
+From this we obtain a $0$-barrier for an agent $\mathcal{A}$ by applying
+above theorem to the set of agents
+$\left\{\mathcal{A}_{q}\mid q\in Q_{\mathcal{A}}\right\}$ where
+$\mathcal{A}_{q}$ has the same behaviour as $\mathcal{A}$ but starts in
+state $q$. More formally,
+\begin{lem}
+  \label{lem:0bar}
+  For every $s$-state agent with $p$ pebbles $\mathcal{A}$ there exists a
+  $0$-barrier with $\mathcal{O}(s^{2})$ vertices, which is independent of
+  the starting state of $\mathcal{A}$.
+\end{lem}
+
+In the following we introduce a gadget construction which enforces
+\enquote{locality} of pebbles. For an agent with $p$ pebbles we can exchange
+every edge in a graph $G$ with a copy of a $(p-1)$-barrier $B$. We refer to the
+original vertices as \emph{macro} vertices and to the constructed graph as
+$G(B)$.  Since every edge is replaced by a $(p-1)$-barrier an agent has to use
+at least $p$ pebbles to cross this barrier which means that the agent keeps its
+pebbles nearby because the agent cannot move along \enquote{edges} without
+them.  This leads to the following lemma.
+\begin{lem}
+  \label{lem:loc}
+  Let $B$ be a $(p-1)$-barrier for an agent $\mathcal{A}$ with $p$ pebbles.
+  Then, the following holds for any graph of the form $G(B)$.
+  \begin{enumerate}
+    \item $\mathcal{A}$ cannot get from a macro vertex $v$ to a distinct
+      macro vertex $v'$ while using less than $p$ pebbles.
+    \item At any time, there is some macro vertex $v$ such that $\mathcal{A}$
+      and each pebble are at $v$ or in one of the surrounding gadgets $B(0),
+      B(1), B(2)$
+  \end{enumerate}
+\end{lem}
+
+With the help of this gadget construction we can now present how it is possible
+to construct barriers iteratively.
+\begin{thm}
+  Given an $(r-1)$-barrier $B$ with $m$ vertices for an agent $\mathcal{A}$
+  with $p\geq r$ pebbles, we can construct an $r$-barrier $B'$ with
+  $\mathcal{O}({{p}\choose{r}}\cdot m\cdot \alpha_{B}^{2})$ vertices for
+  $\mathcal{A}$.
 \end{thm}
 \begin{proof}
-  We will present only the key ideas of this proof since it involves a
-  few technicalities which do not add much to the general understanding
-  and are therefore omitted. Given a subset of pebbles of cardinality $r$
-  we can construct an $r$-barrier for this subset by using the given
-  $(r-1)$-barrier. By the above described gadget construction we can enforce
-  the locality of the used $r$ pebbles. We can then project
-  $A$'s behaviour to an agent $B$ which is a pebble machine without pebbles
-  and has a state for every configuration (which includes the placing of the
-  pebbles as well as state and tape content) of $A$. $B$ now moves over the
-  macro-vertices as $A$ moves through the gadgets. But $B$ has no pebbles and
-  thus, it is applicable to the 0-barrier. Projecting this construct back to
-  the gadget construction yields an $r$-barrier for $A$ and the chosen subset
-  of pebbles. Connecting now such $r$-barriers for all possible subsets of
-  pebbles gives the desired $r$-barrier because $A$ always fails to traverse
-  the $r$-barrier particularly constructed for the pebble set used by $A$.
+  For any subset of pebbles of cardinality $p$ we can use $B$ to apply the
+  locality construction and obtaining a graph $G(B)$. For $G(B)$ we can argue
+  with the use of Lemma \ref{lem:loc} that $\mathcal{A}$ has only a limited
+  amount of configurations within a macro vertex. Let $\alpha_{B}$ be the
+  amount of these configurations. We can now project $\mathcal{A}$ to a pebble
+  machine without pebbles $\mathcal{B}$ with $\alpha_{B}$ states which only
+  traverses macro vertices. Since $\mathcal{B}$ cannot use any pebbles we can
+  obtain by Lemma \ref{lem:0bar} a barrier $C$ for it. Then we can argue that
+  $C(B)$ is the desired barrier for $\mathcal{A}$ which uses only the chosen
+  subset of pebbles. For all ${p}\choose{r}$ possible subsets of pebbles a
+  barrier can be obtained as described above. Connecting these barriers gives
+  the desired barrier $B'$.
 \end{proof}
-By constructing such barriers it is possible to find for every agent
-with $s$ states and $p$ pebbles (note that here the tape of the agent is
-encoded in the states) it is possible to give a trap where the amount of
-vertices can be bound by $\mathcal{O}(s^{8^{p+1}})$. Which can be used to
-show that every agent with sub-logarithmic bits of memory needs at least
-$\Omega(\log\log n)$ many pebbles to explore at least $n$ vertices.
+For the given bound of the vertices we refer to \cite{pebbles}. The
+analysis there contains a thorough combinatorial analysis of the amount of
+vertices for barriers which we do not present here but which leads to the
+following theorem.
+\begin{thm}
+  For $r\leq p$ and $s \geq 2^{p}$, the number of vertices of the $r$-barrier
+  $B_{r}$ for the $s$-state agent $\mathcal{A}$ with $p$ pebbles is bounded by
+  $\mathcal{O}(s^{8^{r+1}})$.
+\end{thm}
+
+Using this theorem it is possible to show that any agent with sublogarithmic
+memory needs to use at least $\log\log n$ pebbles to explore a graph with $n$
+vertices. For this result it is essential that from a $p$-barrier with $m$
+vertices for an agent with $p$ pebbles we can construct a trap for this agent
+with $2m+4$ vertices. Due to its technical nature we omit the proof to the
+following theorem.
+\begin{thm}
+  For any constant $\epsilon < 0$, an agent with at most
+  $\mathcal{O}((\log n)^{1-\epsilon})$ bits of memory needs at least
+  $\Omega(\log\log n)$ distinguishable pebbles for exploring all graphs on at
+  most $n$ vertices.
+\end{thm}
 
@@
 In this paper re-presented the idea of pebble machines for graph exploration
-as discussed in \cite{pebbles}. For this we focused on conwaying the essential
-ideas and constructions rather than explore the technical details. The main
-result clearly is the simulation of memory of pebble machines by encoding
-memory blocks by pebbles and that these pebbles keep a state by their placement
-along a closed walk.
+as discussed in \cite{pebbles}. We lay the main focus on the simulation of
+memory of pebble machines The idea to give pebbles a state by their placement
+on a closed walk strikes as a very interesting approach. Furthermore it is also
+possible to find limitations of this approach in the form of barriers.
 

### 2016-05-11 paper/main.tex
shorten shorten shorten

@@
 This construction of barriers is iteratively and relies on a result from
-\cite{0barrier}.
-\begin{thm}
-  For any $q$ non-cooperative $s$-state agents without pebbles, there exists
-  a 3-regular graph $G$ on $\mathcal{O}(qs)$ vertices with the following
-  property: There are two edges $\left\{v_1,v_2\right\}$ and
-  $\left\{v_3,v_4\right\}$ in $G$, the first labeled 0, such that any of the
-  $q$ agents starting in $v_1$ or $v_2$ does not traverse the edge
-  $\left\{v_3,v_4\right\}$.
-\end{thm}
-From this we obtain a $0$-barrier for an agent $\mathcal{A}$ by applying
-above theorem to the set of agents
-$\left\{\mathcal{A}_{q}\mid q\in Q_{\mathcal{A}}\right\}$ where
-$\mathcal{A}_{q}$ has the same behaviour as $\mathcal{A}$ but starts in
-state $q$. More formally,
+\cite{0barrier} which is used to obtain an initial $0$-barrier.
 \begin{lem}

### 2016-05-12 paper/main.tex
paper "done"

@@
 \section{Introduction}
-In the following we present the main results from \cite{pebbles}. These are
-how to systematically traverse graphs of a very large size by agents. Such
-agents are located on vertices of the graph and move along the edges. Because
+In this work we present the main results from \cite{pebbles}. These are
+how to systematically traverse graphs of a very large size by agents.
+Agents are located on vertices of the graph and move along the edges. Because
 the memory of the agents is very limited we allow agents to use a set of
-distinguishable devices, called pebbles, which can be left on vertices and
-regained by another visit on the same vertex. As we will see this is a very
-rewarding extension since it is possible to obtain very low memory consumption
-for the agents.
+distinguishable tokens, called pebbles, which can be left on a vertex and
+recollected by another visit of the same vertex. As we will see this is a very
+beneficial extension since it is possible to obtain a very low memory footprint
+for the agents while preserving the exploration range.
 
@@
 For the further course we assume the following: Firstly, the considered
-graphs are finite but huge. The considered agents have limited memory and can
-therefore not compute the identifier of vertices. This makes all vertices
+graphs are finite but huge and agents have limited memory and can
+therefore not compute the identifier of vertices which renders all vertices
 indistinguishable for the agents. Also, the degree of the vertices is bounded
@@
 degree of $v$. These edge-labels are called ports and every edge has one port
-for both vertices it connects. Note that there is no relation between these
-ports is presumed.
+for both vertices it connects. Note that no relation between these ports is
+presumed.
 
-\section{Graph exploration}
+\section{Graph Exploration}
 We begin this section by formally defining our agents in the form of
@@
   A $(s,p,m)$-\emph{pebble machine} $\mathcal{M}$ is defined as a tuple
-  $(Q,F,P,m,\delta,\din,\dout,q_{0})$. Here we have
+  $(Q,F,P,m,\delta,\din,\dout,q_{0})$ with
   \begin{enumerate}
-    \item a finite set of states $Q$ with cadinality $s$
+    \item a finite set of states $Q$ with cardinality $s$
     \item a finite set of final states $F\subseteq Q$
     \item a finite set of distinguishable pebbles $P$ with cardinality $p$
-    \item the length of the available memory tape $m$
+    \item the length $m$ of the available memory tape
     \item a computation function $\delta$
-    \item a function that describes the movement onto a vertex
-      $\din$
-    \item a function that describes the leaving of a vertex $\dout$
+    \item a function $\din$ that describes the movement onto a vertex
+    \item a function $\dout$ that describes the leaving of a vertex
     \item an inital state $q_{0}$
@@
   $\din(q,P_{1},P_{2},d,\ell) = q'$ where $q$ is the current state of
-  $\mathcal{M}$, $P_{1}$ the set of pebbles it carries, $P_{2}$ the set
+  $\mathcal{M}$, $P_{1}$ is the set of pebbles it carries, $P_{2}$ the set
   of pebbles located on $v$, $d$ is the degree of $v$ and $\ell$ the port
-  through which $\mathcal{M}$ enters $v$. Then $\mathcal{M}$ starts its
-  computation according to $\delta$ in state $q'$.
-
-  $\dout$ is defined as
+  through which $\mathcal{M}$ enters $v$. Then, $\mathcal{M}$ starts its
+  computation according to $\delta$ in state $q'$.  On the other hand $\dout$
+  is defined as
   \begin{equation*}
@@
   where $\dout(q) = (P_{1}, P_{2}, \ell)$ defines that $\mathcal{M}$ leaves
-  a vertex $v$ through port $\ell$ dropping the pebbles in $P_{1}$ onto $v$
-  and carrying the pebble in $P_{2}$.
+  a vertex $v$ through port $\ell$, drops the pebbles in $P_{1}$ onto $v$
+  and carries the pebbles in $P_{2}$.
 
-  We additionally demand consistency of pebbles, i.e. that if the agent
+  We additionally demand consistency of pebbles, i.e. if the agent
   carried the pebbles in $P_{1}\subseteq P$ and found the pebbles in
-  $P_{2}\subseteq P$ it is necessary that $P_{1}$ and $P_{2}$ are disjoint and
-  furthermore that if the agent leaves carrying $P'_{1}$ and leaving $P'_{2}$
-  behind those sets are disjoint and $P_{1}\cup P_{2} = P'_{1}\cup P'_{2}$.
+  $P_{2}\subseteq P$ it is necessary that $P_{1}$ and $P_{2}$ are disjoint.
+  Furthermore, if the agent leaves carrying $P'_{1}$ and dropping $P'_{2}$
+  those sets are disjoint and $P_{1}\cup P_{2} = P'_{1}\cup P'_{2}$.
 \end{definition}
 
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \begin{center}
+    \resizebox{0.3\textwidth}{!}{\input{tikz/blowup}}
+  \end{center}
+  \caption{Replace vertex by a 3-clique preserving 3-regularity.}
+  \label{fig:blowup}
+\end{wrapfigure}
 In order to describe the movement of an agent we introduce the notion of an
-exploration sequence as $e_{0}, e_{1},\dots$ which define relative movements:
-Let $\ell = \ell_{0},\ell_{1},\dots$ be a sequence of variables where
-$\ell_{i}$ denotes the port which a vertex $v$ was entered through. Then an
-agent following $\ell$ leaves through port
+exploration sequence $e = e_{0}, e_{1},\dots$ for agents which defines relative
+movements.
+Let $\ell = \ell_{0},\ell_{1},\dots$ be a sequence of variables.
+$\ell_{i}$ denotes that the $i$-th visited vertex is entered through port
+$\ell_{i}$. Then, an agent following $e$ leaves through port
 $(\ell_{i} + e_{i}) \mod d_{v}$. We define $\ell_{0} = 0$ and the notion
-$(e_{0},\dots,e_{k})^{\ast}$ for periodic exploration sequence.
+$(e_{0},\dots,e_{k})^{\ast}$ for periodic exploration sequences. We call an
+exploration sequence universal for a class of graphs if an agent following
+it explores any graph of that class.
 
 Beginning from the following result of \cite{logspacealg} we present how we can
-obtain an $(\mathcal{O}(1),0,\mathcal{O}(\log n))$ pebble machine that walks
-along a closed walk of at least $n$ distinct vertices in any graph with bounded
+obtain an $(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine that performs
+a closed walk of at least $n$ distinct vertices in any graph with bounded
 degree.
@@
 \begin{proof}
-  We therefore consider a graph with vertices of the form $(v,\ell,i)$ which
-  denote that the agent entered in the original graph vertex $v$ through port
-  $\ell$ and that the next element of the exploration sequence is $i$. For the
-  edges we consider movements of the agent from the configuration given by the
-  current vertex $(v,\ell,i)$. It is easy to see that for a vertex $(v,\ell,i)$
-  the next vertex is deterministically chosen and is therefore unique. We
-  furthermore argue that there is at most one predecessor for every vertex.
-  Examine therefore two vertices $(v',\ell',i')$ and $(v'',\ell'',i'')$ which
-  lead to $(v,\ell,i)$. Both enter $v$ by $\ell$ thus $v' = v''$. Furthermore
-  it is clear that $i' + 1 \mod k = i = i'' + 1 \mod k$ which implies
-  $i' = i''$. Concludingly,
+  Consider a graph with vertices of the form $(v,\ell,i)$
+  denoting that the agent entered in the original graph vertex $v$ through port
+  $\ell$ and that the next element of the exploration sequence is $i$.
+  Edges are given by the next movement of the agent following the exploration
+  sequence from the configuration of the current vertex $(v,\ell,i)$. It is
+  easy to see that for a vertex $(v,\ell,i)$
+  the next vertex is deterministically chosen and therefore is unique.
+  Furthermore we argue that there is at most one predecessor for every vertex.
+  Examine two predecessor $(v',\ell',i')$ and $(v'',\ell'',i'')$ for
+  $(v,\ell,i)$. Both enter $v$ by $\ell$ thus $v' = v''$.  It is clear that
+  $i' + 1 \mod k = i = i'' + 1 \mod k$ which implies $i' = i''$. Concludingly,
   $\ell' + e_{i'} \mod d_{v'} = \ell'' + e_{i''} \mod d_{v''}$ and since
-  $v' = v''$ and $e_{i'} = e_{i''}$ and $\ell',\ell'' < d_{v'} = d_{v''}$
-  it follows that $\ell' = \ell''$.
+  $v' = v''$, $e_{i'} = e_{i''}$ and $\ell',\ell'' < d_{v'} = d_{v''}$,
+  $\ell' = \ell''$ follows.
   Because now every vertex has one outgoing and at most one incoming edge 
@@
 \end{lem}
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \flushright{\resizebox{0.4\textwidth}{!}{\input{tikz/regtrans}}}
+  \caption{Illustration how to transform any graph to a 3-regular graph.}
+  \label{fig:3reg}
+\end{wrapfigure}
 \begin{proof}
-  Let $\mathcal{M}$ be the TM of Theorem \ref{thm:logalg}.
+  Let $\mathcal{M}$ be the Turing machine(TM) of Theorem \ref{thm:logalg}.
   At first we show that the exploration sequence produced by $\mathcal{M}$ is
-  universal for every graph with at most $n$ vertices. Assume therefore there
+  universal for every graph with at most $n$ vertices. Assume there
   is a 3-regular graph with $n_{0} < n$ vertices for which $\mathcal{M}$
-  produces a non universal exploration sequence. Note that $n_{0}$ is even
-  because every 3-regular graph has an even amount of nodes by the Handshaking
-  lemma. Then there is a vertex $v$ which is not explored. We can now
-  repeatedly apply the following construction:
-  \begin{center}
-    \parbox{3\baselineskip}{\resizebox{!}{3\baselineskip}{\input{tikz/blowup}}}
-  \end{center}
-  Thus, we added 2 vertices which are also not explored. This can be iterated
-  until there are $n$ vertices for which all added vertices are not explored
-  contradicting Theorem \ref{thm:logalg}.
+  produces a non-universal exploration sequence. Note that $n_{0}$ is even
+  because every 3-regular graph has an even number of nodes by the Handshaking
+  Lemma. Then, there is a vertex $v$ which is not explored. We can now
+  repeatedly transform $v$ into a clique of three vertices with degree three
+  (see Figure \ref{fig:blowup}).
+  Thus, we added two vertices which are also not explored. This can be iterated
+  until there are $n$ vertices. All the added vertices are not explored in a
+  graph with $n$ vertices contradicting Theorem \ref{thm:logalg}.
 
   Secondly, we show that we can construct a TM $\mathcal{M}'$ which simulates
-  $\mathcal{M}$ until it produced a exploration sequence of length $3n\cdot c$
-  where $c$ is the number of configurations of $\mathcal{M}$. $\mathcal{M}'$
-  outputs now $(e_{0},\dots,e_{k-1})^{\ast}$ which is universal for any
-  3-regular graph with $n$ vertices. If we assume that it is not we can
-  conclude that we loop in a set of vertices $V'$ for which $|V'|<n$. By a
-  simple combinatorial argument we see that the produced exploration sequence
-  of $\mathcal{M}$ therefore always loops in $V'$ because an agent following
-  the produced exploration sequence would have entered a vertex twice by the
-  same port whilst $\mathcal{M}$ was in the same configuration.
+  $\mathcal{M}$ until it produced a exploration sequence of length
+  $k = 3n\cdot c$ where $c$ is the number of configurations of $\mathcal{M}$.
+  $\mathcal{M}'$ outputs now $(e_{0},\dots,e_{k-1})^{\ast}$ which is universal
+  for any 3-regular graph with $n$ vertices. If we assume that it is not, we
+  can conclude that we loop in a set of vertices $V'$ for which $|V'|<n$. By a
+  combinatorial argument we see that the produced exploration sequence $e$
+  of $\mathcal{M}$ always loops in $V'$ because an agent following
+  $e$ would have entered a vertex twice by the same port whilst $\mathcal{M}$
+  is in the same configuration both times.
 \end{proof}
-\begin{wrapfigure}{r}{0.5\textwidth}
-  \caption{Illustration how to transform any graph to a 3-regular graph.}
-  \label{fig:3reg}
-  \flushright{\resizebox{0.4\textwidth}{!}{\input{tikz/regtrans}}}
-\end{wrapfigure}
 These lemmata are used in \cite{pebbles} to give the following theorem.
@@
 \end{thm}
-\begin{proof}[Sketch]
+\begin{proof}[Proof-Sketch]
   The TM constructed in Lemma \ref{lem:pul} is used as the desired pebble
-  machine. But first the graph has to be transformed to be 3-regular.
+  machine but first the graph has to be transformed to be 3-regular.
   We refer therefore to Figure \ref{fig:3reg} which shows how every vertex $v$
-  can be replaced by $3\cdot d_{v}$ vertices which only have 3 edges. It is
-  furthermore noteworthy that this transformation can be emulated with
-  $\mathcal{O}(\log n)$ memory because of the regular structure of the
+  can be replaced by a gadget with $3\cdot d_{v}$ vertices of degree three. It
+  is also noteworthy that this transformation can be done with
+  $\mathcal{O}(\log n)$ memory: Because of the regular structure of the
   transformation (moving along port 0 or 1 stays in the gadget and only
@@
 \section{Simulation}
-In the following we present possibly the most interesting result from
-\cite{pebbles}. A simulation of a pebble machine which allows to store
+In the following we present the most interesting result from
+\cite{pebbles}: A simulation of a pebble machine which allows to store
 the tape content of the simulated pebble machine as pebbles placed on a
-defined walk within a graph.
+walk within a graph.
 \begin{thm}
@@
 \end{thm}
-\begin{proof}
-  In this proof we will focus on the simulation and we leave out a thorough
-  analysis of the space requirements of the simulation since it is rather
-  technical but does not add a lot to the idea. Nevertheless we encourage
-  interested readers to see \cite{pebbles} for the details.
+\begin{proof}[Proof-Sketch]
+  For a detailed description of mechanisms of the simulation we refer to
+  \cite{pebbles}. At this point we present the conceptional ideas but encourage
+  interested readers to look up the details.
 
-  The main idea of this simulation is to store the tape of $M$ by pebbles
-  placed on a closed walk in the graph. We show that every node on this closed
-  walk can be given an index and a pebble placed on a node represents the
-  binary representation of the index as the content of $M$'s tape. Therefore we
-  first off introduce a variable $m_{1}$ which is dependent on the simulated
-  pebble machine $M$ (further requirements on $m_{1}$ and how to obtain it
-  can be seen in \cite{pebbles}). We will now take the tape of $M$ and separate
-  it into $2m/m_{1}$ blocks of the size $m_{1}$. And each of these blocks is
-  encoded by the placement of a pebble on a closed walk $\omega$. So we use
-  pebble $p_{0}$ to encode the first $m_{1}$ bits, the pebble $p_{1}$ used to
-  encode the next $m_{1}$ bits and so forth. Thus, the pebble $p_{i}$ encodes
-  the bits $im_{1},\dots,(i+1)m_{1}-1$. It is therefore necessary that every
-  pebble can encode $2^{m_1}$ different states. For this we use a closed walk
-  $\omega$ which visits at least $2^{m_1}$ distinct vertices yielding $2^{m_1}$
-  many \enquote{states} for each pebble (by its placement on this closed walk).
-  Therefore we can use the binary representation of the indices of the nodes
-  on which the pebbles are placed as the content of the encoded memory block.
-  Figure \ref{fig:tapesim} illustrates this.
-  \begin{figure}[h!]
+  We separate the tape of the simulated machine into memory blocks of size
+  $m_1$. With Theorem \ref{thm:pebblewalk} there is a
+  $(\mathcal{O}(1),0,\mathcal{O}(m_{1}))$-pebble machine
+  $\mathcal{M}_{\text{walk}}$ to perform a closed walk $\omega$ with
+  $2^{m_{1}}$ distinct vertices. We use a pebble to mark the beginning vertex
+  of this walk. Every memory block can now be represented by
+  a pebble which encodes the block by its placement on $\omega$ (see
+  Figure \ref{fig:tapesim}).
+
+  Because the vertices are indistinguishable it is necessary to find a
+  mechanism to enumerate distinct vertices in $\omega$ otherwise the state of
+  pebbles might be ambiguous. This can be achieved by always marking the next
+  vertex $v$ of $\omega$ with a pebble and check if $v$ is
+  traversed by a new run of $\mathcal{M}_{\text{walk}}$ in fewer steps. If so
+  $v$ is not a new distinct vertex.
+
+  The head position of the simulated machine is stored in a variable $\Thead$.
+  In order to access this memory cell the state of the pebble with index
+  $\left\lfloor \frac{\Thead}{m_{1}}\right\rfloor$ is extracted. Then the
+  corresponding $(\Thead\mod m_{1})$-th bit is the desired bit. If this bit is
+  altered the corresponding pebble can be moved according to the new state of
+  the memory block by $2^{(\Thead\mod m_{1})}$ indices on $\omega$.
+
+  Finally, if the simulated machine executes a movement, it is necessary to
+  carry the tape content along. Therefore the vertex $v'$ the machine moves
+  onto is marked with a pebble and $\mathcal{M}_{\text{walk}}$ is used to find
+  a new closed walk $\omega'$ starting in $v'$. Then all encoding pebbles are
+  moved to the corresponding distinct vertex in $\omega'$ to preserve their
+  states. (Note that $\mathcal{M}_{\text{walk}}$ gives a walk with at least
+  $2^{m_{1}}$ distinct vertices for every starting vertex).
+  \begin{figure}
+    \begin{center}
+      \resizebox{0.6\textwidth}{!}{\input{tikz/tapesim}}
+    \end{center}
     \caption{Illustration how to simulate the tape of a pebble machine by
@@
     \label{fig:tapesim}
-    \begin{center}
-      \resizebox{0.6\textwidth}{!}{\input{tikz/tapesim}}
-    \end{center}
   \end{figure}
-
-  In the following we show how this simulation can be managed.
-  Let $M_{\text{Walk}}$ be pebble machine that yields $\omega$ on $G$.
-  $M_{\text{Walk}}$ can be implemented as $(\mathcal{O}(1),0,\mathcal{O}(m_{1}))$
-  pebble machine by Theorem \ref{thm:pebblewalk}.
-  In order to manage the simulation we use some
-  variables: $\Tid, \Tsteps, \Twalk, \Thead$ where $\Tid$ is used to identify
-  the index of a vertex on the walk of $M_{\text{Walk}}$, $\Twalk$ is the tape
-  content of $M_{\text{Walk}}$ which can therefore be restarted by setting
-  $\Twalk$ to 0, $\Tsteps$ counts the number of steps taken by
-  $M_{\text{Walk}}$, and $\Thead$ stores where $M$'s head is positioned.
-  Furthermore we need some pebbles to mark certain vertices of the closed walk:
-  $p_{\text{start}}, p_{\text{tmp}}, p_{\text{next}}$ and additionally the
-  pebbles that are placed on the walk to store $M$'s tape content
-  $P_{M} = \left\{p_{0},p_{1},\dots,p_{2m/m_{1}-1}\right\}$.
-  Now the different procedures used for the simulation can be presented:
-  \begin{description}
-    \item[Step():] Simulates on step according to $M_{\text{Walk}}$ and
-      increases $\Tsteps$.
-    \item[FindPebble($p_{i}$):] Executes \emph{Step()} until the pebble $p_{i}$
-      is observed.
-    \item[Restart():] Goes to the beginning of the closed walk by
-      \emph{FindPebble($p_{\text{start}}$)} and sets $\Tsteps,\Tid,\Twalk$ to 0
-    \item[NextDistinctVertex()] Finds the next distinct vertex of the walk. If
-      there are no more vertices on the walk (which means that already
-      $2^{m_1}$ distinct vertices have been traversed; the number of distinct
-      vertices on the walk is given by $\Tid$) it simply executes
-      \emph{Restart()}. Otherwise it does one step and drops $p_{\text{tmp}}$
-      to mark this vertex. It then stores the current amount of steps as well
-      as the current state of $M_{\text{Walk}}$ (introducing two auxiliary
-      variables $\Tsteps',\Twalk'$). It then restarts $M_{\text{Walk}}$ and
-      moves to $p_{\text{tmp}}$ by \emph{FindPebble($p_{\text{tmp}}$)}. If
-      it used the same amount of steps as stored in $\Tsteps'$ then this is the
-      first occurence of the vertex in the closed walk and therefore it is a
-      new distinct vertex and $\Tid$ can be increased. Otherwise the context of
-      $M_{\text{Walk}}$ is restored and the next vertex is checked.
-    \item[GetPebbleId($p_{i}$):] Finds the index of the vertex $p_{i}$ is
-      placed on. Beginning from the start of the closed walk
-      (found by executing \emph{Restart()} it moves along distinct vertices
-      (by using \emph{NextDistinctVertex()}) and returns $\Tid$ as soon as
-      $p_{i}$ is observed.
-    \item[PutPebbleAtId($p_{i},\mathit{id}$):] Puts pebble $p_i$ at a certain
-      index. First it picks up $p_{i}$ and restarts the walk. Then it executes
-      $\mathit{id}$ times \emph{NextDistinctVertex()} and drops $p_{i}$.
-    \item[ReadBit():] Reads the $\Thead$'s bit of $M$'s tape. $\Thead$ gives
-      the position of the bit that should be read. Therefore the pebble
-      $p_{\lfloor \Thead/m_{1}\rfloor}$ encodes this bit. The \enquote{state}
-      of this pebble can be obtained with
-      \emph{GetPebbleId($p_{\lfloor \Thead/m_{1}\rfloor}$)} and from the
-      encoded value the $(\Thead\mod m_{1})$-th bit is the one under $M$'s
-      head.
-    \item[WriteBit($b$):] Writes $b$ to $\Thead$'s bit of $M$'s tape. First
-      $\Thead$'s bit is obtained (by \emph{ReadBit()}). Additionally we
-      identify the encoding pebble $p_{i}$ as already seen for
-      \emph{ReadBit()} and let be $j = \Thead\mod m_{1}$ the offset of the bit
-      within the memory block. If the bit actually flips the value of the
-      memory block changes by $2^j$ (for the flip from 1 to 0 the value
-      decreases and for the flip from 0 to 1 it increases). Therefore $p_{i}$
-      is put either $2^j$ indices up or down which can be easily done by using
-      \emph{PutPebbleAtId(\dots)}.
-  \end{description}
-  These are the procedures used to simulate $M$'s tape. Furthermore we keep
-  $M$'s states in the state space of the simulation. To conclude the simulation
-  we have to consider what happens if $M$ moves from the current vertex to
-  another vertex $v'$. Then the pebble $p_{tmp}$ is dropped on $v'$ and the
-  pebbles are moved to the same index they have in $\omega$ for a new closed
-  walk $\omega'$ (obtained by $M_{\text{Walk}}$ simulated starting in $v'$;
-  this walk is also ensured to have at least $2^{m_1}$ distinct vertices).
+  This concludes the intuition on how the tape of a pebble machine can be
+  simulated by a set of pebbles.
 \end{proof}
@@
 
-This construction of barriers is iteratively and relies on a result from
+The construction of a barrier is done iteratively and relies on a result from
 \cite{0barrier} which is used to obtain an initial $0$-barrier.
@@
 original vertices as \emph{macro} vertices and to the constructed graph as
-$G(B)$.  Since every edge is replaced by a $(p-1)$-barrier an agent has to use
+$G(B)$.  Since every edge is replaced by a $(p-1)$-barrier, an agent has to use
 at least $p$ pebbles to cross this barrier which means that the agent keeps its
@@
 \begin{proof}
-  For any subset of pebbles of cardinality $p$ we can use $B$ to apply the
+  For any subset of pebbles of cardinality $r$ we can use $B$ to apply the
   locality construction and obtaining a graph $G(B)$. For $G(B)$ we can argue
-  with the use of Lemma \ref{lem:loc} that $\mathcal{A}$ has only a limited
+  using Lemma \ref{lem:loc} that $\mathcal{A}$ has only a limited
   amount of configurations within a macro vertex. Let $\alpha_{B}$ be the
@@
   traverses macro vertices. Since $\mathcal{B}$ cannot use any pebbles we can
-  obtain by Lemma \ref{lem:0bar} a barrier $C$ for it. Then we can argue that
+  obtain a barrier $C$ for it by Lemma \ref{lem:0bar}. Then, we can argue that
   $C(B)$ is the desired barrier for $\mathcal{A}$ which uses only the chosen
@@
 
-Using this theorem it is possible to show that any agent with sublogarithmic
+Using this theorem it is possible to show that any agent with sub-logarithmic
 memory needs to use at least $\log\log n$ pebbles to explore a graph with $n$
-vertices. For this result it is essential that from a $p$-barrier with $m$
-vertices for an agent with $p$ pebbles we can construct a trap for this agent
-with $2m+4$ vertices. Due to its technical nature we omit the proof to the
-following theorem.
+vertices.
 \begin{thm}
@@
 
+For this result it is essential that from a $p$-barrier with $m$
+vertices for an agent with $p$ pebbles we can construct a trap for this agent
+with $2m+4$ vertices. Due to its technical nature we omit the proof.
+
 \section{Conclusion}
-In this paper re-presented the idea of pebble machines for graph exploration
-as discussed in \cite{pebbles}. We lay the main focus on the simulation of
-memory of pebble machines The idea to give pebbles a state by their placement
-on a closed walk strikes as a very interesting approach. Furthermore it is also
-possible to find limitations of this approach in the form of barriers.
+In this work we presented the idea of pebble machines for graph exploration
+as discussed in \cite{pebbles}. We focus mainly on the simulation of
+memory of pebble machines. The idea to give pebbles a state by their placement
+on a closed walk strikes as a very interesting approach. Furthermore, it is
+also possible to find limitations of this approach in the form of barriers.
 

### 2016-05-12 presentation/main.tex
slides "done"

@@
 \usepackage{mdframed}
+\usepackage{graphicx}
+\usepackage{appendixnumberbeamer}
 
@@
 \metroset{numbering=fraction}
+\setbeamercolor{math text}{fg=blue}
 
@@
 \begin{document}
-% \tikzexternalize
 \maketitle
 \begin{frame}
-  \frametitle{Motivation}
+  \begin{center}
+    \includegraphics{hanselgretel.jpg}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Outlook}
   \begin{itemize}
@@
     \item Agents can drop pebbles on vertices
-    \item Agent \emph{explores} a graph by deterministically visiting all of
+    \item Agent \emph{explores} a graph by systematically visiting all of
       its vertices
@@
       \item Edges can locally be labeled with
-        \textcolor{green}{$0,\dots,\Delta-1$} (Port)
+        \textcolor{blue}{$0,\dots,\Delta-1$} (Port)
     \end{itemize}
@@
       \item Agent carries set of distinguishable pebbles
-      \item Formalisation as pebble-machines
+      \item Formalisation as pebble machines
         \begin{itemize}
+          \item $(s,p,m)$-pebble machine
           \item $(Q,F,P,m,\delta,\din,\dout,q_{0})$
           \item<2-> $\din$: moving onto vertex
-          \item<7-> $\dout$: leaving vertex
+          \item<8-> $\dout$: leaving vertex
         \end{itemize}
@@
         \begin{itemize}
-          \item<4-> Pebbles it carries
-          \item<5-> Pebbles on the vertex
-          \item<6-> Degree of vertex
+          \item<4-> Port it entered through
+          \item<5-> Pebbles it carries
+          \item<6-> Pebbles on the vertex
+          \item<7-> Degree of vertex
         \end{itemize}
-      \item<8-> Computation on a vertex determines:
+      \item<9-> Computation on a vertex determines:
         \begin{itemize}
-          \item<9-> Port to leave
-          \item<10-> Pebbles to drop
-          \item<11-> Pebbles to carry along
+          \item<10-> Port to leave
+          \item<11-> Pebbles to drop
+          \item<12-> Pebbles to carry along
         \end{itemize}
@@
   \begin{columns}
-    \column{0.5\textwidth}
+    \column{0.6\textwidth}
     \begin{itemize}
@@
       \item<2->[$\rightarrow$] Example:
-        $\alt<3-3>{\colorbox{green}{1}}{\colorbox{white!0}{1}},
+        $\alt<3-3>{\colorbox{green}{0}}{\colorbox{white!0}{0}},
         \alt<4-4>{\colorbox{green}{3}}{\colorbox{white!0}{3}},
-        \alt<5-5>{\colorbox{green}{2}}{\colorbox{white!0}{2}},
+        \alt<5-5>{\colorbox{green}{1}}{\colorbox{white!0}{1}},
         \alt<6-6>{\colorbox{green}{2}}{\colorbox{white!0}{2}}$
     \end{itemize}
-    \column{0.5\textwidth}
+    \column{0.4\textwidth}
     \begin{center}
@@
   \frametitle{Exploring pebble machine}
+  \begin{mdframed}
     \begin{theorem}[Reingold]
@@
     \end{theorem}
+  \end{mdframed}
   \begin{center}
@@
       \uncover<2->{
-        \node[rectangle, draw=green, below right=0.3 and 1 of d1]
+        \node[rectangle, draw=purple, below right=0.3 and 1 of d1]
         {3-Regularity};
@@
       \uncover<4->{
-        \node[rectangle, draw=yellow, below right=1.7 and 1 of d1]
-        {Closed walk Lemma};
+        \node[rectangle, draw=magenta, below right=1.7 and 1 of d1]
+        {Closed Walk Lemma};
       }
@@
   \end{center}
+  \begin{mdframed}
     \begin{theorem}
@@
     \end{theorem}
+  \end{mdframed}
 \end{frame}
@@
   \frametitle{Closed walk}
-  \begin{mdframed}[linecolor=yellow]
-    \begin{lemma}[Closed walk]
+  \begin{mdframed}[linecolor=magenta]
+    \begin{lemma}[Closed Walk Lemma]
       An agent following an exploration sequence of the form
@@
 \begin{frame}
-  \frametitle{3-Regularity}
-  \begin{mdframed}[linecolor=green]
-    Establish 3-regularity
+  \frametitle{$3$-regularity}
+  \begin{mdframed}[linecolor=purple]
+    Establish $3$-regularity
   \end{mdframed}
@@
   \frametitle{Exploring pebble machine}
+  \begin{mdframed}
     \begin{theorem}[Reingold]
-    There is an $\mathcal{O}(n)$-space algorithm producing a universal
+      There is an $\mathcal{O}(\log n)$-space algorithm producing a universal
       exploration sequence for any regular graph on $n$ vertices.
     \end{theorem}
+  \end{mdframed}
   \begin{center}
@@
       \node[rectangle, draw=blue, below right=1 and 1.2 of d1]
-        {Periodic Universal lemma};
+        {Periodic Universal Lemma};
       \node[rectangle, draw=yellow, below right=1.7 and 1 of d1]
-        {Closed walk lemma};
+        {Closed Walk Lemma};
     \end{tikzpicture}
   \end{center}
+  \begin{mdframed}
     \begin{theorem}
@@
 \begin{frame}
+  \begin{mdframed}
     \begin{theorem}
       There is a constant $c\in\mathbb{N}$, such that for any graph $G$
-    with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$, there
-    exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates the walk
-    of $\mathcal{M}$ or explores $G$.
+      with bounded degree and any $(s,p,2m)$-pebble machine $\mathcal{M}$,
+      there exists a $(cs,p+c,m)$-pebble machine $\mathcal{M}'$ that simulates
+      the walk of $\mathcal{M}$ or explores $G$.
     \end{theorem}
+  \end{mdframed}
 \end{frame}
@@
   \begin{enumerate}
-    \item Simulation of $M_{\text{walk}}$ providing walk with $2^{m_{1}}$
-      distinct vertices
-    \item Identify \emph{distinct} vertices of walk
+    \item Simulation of $M_{\text{walk}}$ providing
+        walk with $2^{m_{1}}$ distinct vertices
+    \item \textcolor<2->{blue}{Identify \emph{distinct} vertices of walk}
     \item Read from and write to simulated tape
@@
 \begin{frame}
+  \frametitle{2. Finding distinct vertices}
+  Problem: Indistinguishable vertices $\leadsto$ next vertex \enquote{new}?
+  \begin{columns}
+    \column{0.5\textwidth}
+    Solution:
+    \begin{enumerate}
+      \item \textcolor<3,8>{magenta}{Execute step of $M_{\text{walk}}$}
+      \item \textcolor<4,9>{magenta}{Drop pebble $p_{\text{tmp}}$}
+      \item \textcolor<4,9>{magenta}{Store $\Twalk$ in $T'_{\text{walk}}$}
+      \item \textcolor<5,10>{magenta}{Restart $M_{\text{walk}}$}
+      \item \textcolor<6,11-18>{magenta}{Execute steps of $M_{\text{walk}}$
+          until $p_{\text{tmp}}$ is observed}
+      \item \textcolor<19-20>{magenta}{If $\Twalk = T'_{\text{walk}}$ the
+          vertex is new (increase $\Tid$)}
+      \item \textcolor<7>{magenta}{Otherwise start over}
+    \end{enumerate}
+    \column{0.5\textwidth}
+    \input{tikz/disvert}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Simulation of a pebble machine}
+  \begin{itemize}
+    \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
+      distinct vertices \uncover<2->{\textcolor{green}{{\checkmark}}}
+    \item Identify \emph{distinct} vertices of the walk
+      \uncover<3->{\textcolor{green}{{\checkmark}}}
+    \item Read from and write to simulated tape \uncover<4->{\textcolor{green}{{\checkmark}}}
+    \item Preserve tape content through steps of simulated agent
+      \uncover<5->{\textcolor{green}{{\checkmark}}}
+  \end{itemize}
+  \uncover<6->{
+    \begin{mdframed}
+      \begin{theorem}
+        There is a constant $c\in\mathbb{N}$, such that for any graph $G$
+        with bounded degree and any $(s,p,2m)$-pebble machine $\mathcal{M}$,
+        there exists a $(cs,p+c,m)$-pebble machine $\mathcal{M}'$ that simulates
+        the walk of $\mathcal{M}$ or explores $G$.
+      \end{theorem}
+    \end{mdframed}
+  }
+\end{frame}
+
+\begin{frame}
+  \frametitle{Exploring graphs with $\log\log n$ pebbles}
+  \begin{mdframed}
+    \begin{theorem}
+      There exists a $(\mathcal{O}(1), 0, \mathcal{O}(\log n))$-pebble machine
+      that moves along a closed walk and either explores the graph or visits at
+      least $n$ distinct vertices, for any graph with bounded degree.
+    \end{theorem}
+  \end{mdframed}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (d1) {};
+      \node[below=1.5 of d1] (d2) {};
+      \draw[->, bend right] (d1) to (d2);
+      \node[below right=0.6 and 1 of d1, rectangle,draw=black] {Apply simulation Theorem $\log\log n$ times};
+    \end{tikzpicture}
+  \end{center}
+  \begin{mdframed}
+    \begin{theorem}
+      Any bounded-degree graph on at most $n$ vertices can be explored using
+      $\mathcal{O}(\log\log n)$ pebbles and memory.
+    \end{theorem}
+  \end{mdframed}
+\end{frame}
+
+\section{Limitations of pebble machines}
+\begin{frame}
+  \frametitle{Limitations of pebbles}
+  \begin{itemize}
+    \item Construct $3$-regular graphs which an agent $\mathcal{A}$ with $p$
+      pebbles cannot traverse
+    \item Called $p$-barriers
+      \begin{center}
+        \resizebox{0.6\textwidth}{!}{\input{tikz/barrierint}}
+      \end{center}
+    \item For every pair $(a,b)$ in
+      $\left\{v_{1},v_{2}\right\}\times\left\{v_{3},v_{4}\right\}$
+      $\mathcal{A}$ cannot traverse a $p$-barrier from $a$ to $b$
+      or vice versa using at most $p$ pebbles
+    \item Inductive construction of barriers
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Locality gadget}
+  \begin{itemize}
+    \item Replace edge by $(r-1)$-barrier
+    \item Enforce \enquote{locality} of pebbles
+      \begin{center}
+        \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/locgadget}}}
+      \end{center}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \begin{mdframed}
+    \begin{theorem}
+      Given an $(r-1)$-barrier $B$ with $m$ vertices for an agent $\mathcal{A}$
+      with $p\geq r$ pebbles, we can construct an $r$-barrier $B'$ with
+      $\mathcal{O}(\binom{p}{r}\cdot m\cdot\alpha_{B}^{2})$ vertices for
+      $\mathcal{A}$.
+    \end{theorem}
+  \end{mdframed}
+  where $\alpha_{B}$ is the amount of \enquote{local} configurations for
+  $\mathcal{A}$ with $r$ pebbles
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier construction: Idea}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{itemize}
+      \item Subset of pebbles of cardinality $r$
+      \item Locality gadget as edges
+      \item Pebbles are local: configurations in macro vertex
+        $C_{1},\dots,C_{\alpha}$
+      \item Project $A$ to agent without pebbles $B$
+      \item $B$ has $\alpha$ states and traverses macro vertices
+    \end{itemize}
+    \column{0.5\textwidth}
+    \resizebox{\textwidth}{!}{\input{tikz/projection}}
+  \end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier construction}
+  \begin{itemize}
+    \item $B$ has no pebbles and cannot traverse $0$-barrier
+    \item $r$-barrier for chosen subset of pebbles
+    \item Connect barriers for all possible subsets of pebbles with cardinality
+      $r$:
+  \end{itemize}
+  \begin{center}
+    \resizebox{0.8\textwidth}{!}{\input{tikz/iterbarrier}}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier base case}
+  \begin{mdframed}
+    \begin{theorem}[Fraigniaud et al.]
+      For any $q$ non cooperative $s$-state agents without pebbles, there
+      exists a $3$-regular graph $G$ on $\mathcal{O}(qs)$ vertices with the
+      following property: There are two edges $\left\{v_{1},v_{2}\right\}$
+      and $\left\{v_{3},v_{4}\right\}$ in $G$, the first labeled 0, such
+      that any of the $q$ agents starting in $v_{1}$ or $v_{2}$ does not
+      traverse the edge $\left\{v_{3},v_{4}\right\}$.
+    \end{theorem}
+  \end{mdframed}
+  \begin{itemize}
+    \item For agent $\mathcal{A}$ consider
+      $S = \left\{\mathcal{A}_{q}\mid q\in Q\right\}$
+    \item Since $|S| = |Q| = q$ there is a 0-barrier with $\mathcal{O}(s^{2})$
+      vertices
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Barrier}
+  \begin{mdframed}
+    \begin{theorem}
+      Given an $(r-1)$-barrier $B$ with $m$ vertices for an agent $\mathcal{A}$
+      with $p\geq r$ pebbles, we can construct an $r$-barrier $B'$ with
+      $\mathcal{O}(\binom{p}{r}\cdot m\cdot\alpha_{B}^{2})$ vertices for
+      $\mathcal{A}$.
+    \end{theorem}
+  \end{mdframed}
+  \begin{center}
+    \resizebox{0.7\textwidth}{!}{\input{tikz/iterbarrier}}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Lower pebble bound}
+  \begin{mdframed}
+    \begin{theorem}
+      For any constant $\epsilon > 0$, an agent with at most
+      $\mathcal{O}((\log n)^{1-\epsilon})$ bits of memory needs at least
+      $\Omega(\log\log n)$ distinguishable pebbles for exploring all
+      graphs on at most $n$ vertices.
+    \end{theorem}
+  \end{mdframed}
+\end{frame}
+
+\section{Conclusion}
+\begin{frame}
+  \frametitle{Conclusion}
+  \begin{itemize}
+    \item Exploring graphs with $\mathcal{O}(\log\log n)$ pebbles and memory
+    \item Simulation via pebbles
+    \item Limitations of pebbles: Barrier construction
+    \item Every agent with sub-logarithmic memory needs $\Omega(\log\log n)$
+      pebbles to explore $n$ vertices
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \begin{center}
+    \Huge Thank you for your attention.
+  \end{center}
+\end{frame}
+
+\appendix
+\begin{frame}
   \frametitle{1. Simulation of $M_{\text{walk}}$}
@@
     \item $M_{\text{Walk}}$ implemented as
-      $(\mathcal{O}(1), 0, \mathcal{O}(m_{1}))$ pebble machine
+      $(\mathcal{O}(1), 0, \mathcal{O}(m_{1}))$-pebble machine
     \item Used variables/pebbles:
@@
 \begin{frame}
-  \frametitle{2. Finding distinct vertices}
-  Problem: Indistinguishable vertices $\leadsto$ next vertex \enquote{new}?
-  \begin{columns}
-    \column{0.5\textwidth}
-    Solution:
-    \begin{enumerate}
-      \item \textcolor<3,8>{green}{Execute step}
-      \item \textcolor<4,9>{green}{Drop pebble $p_{\text{tmp}}$}
-      \item \textcolor<4,9>{green}{Store $\Twalk$ in $T'_{\text{walk}}$}
-      \item \textcolor<5,10>{green}{Restart $M_{\text{walk}}$}
-      \item \textcolor<6,11-18>{green}{Execute steps until $p_{\text{tmp}}$ is
-        observed}
-      \item \textcolor<19-20>{green}{If $\Twalk = T'_{\text{walk}}$ the vertex
-        is new (increase $\Tid$)}
-      \item \textcolor<7>{green}{Otherwise start over}
-    \end{enumerate}
-    \column{0.5\textwidth}
-    \input{tikz/disvert}
-  \end{columns}
-\end{frame}
-
-\begin{frame}
   \frametitle{3. Memory management}
@@
       \item $\Thead$: head position
-      \item $p_{\lfloor\frac{\Thead}{m_{1}}\rfloor}$: pebble of memory block
+      \item $p_{\left\lfloor\frac{\Thead}{m_{1}}\right\rfloor}$: pebble of
+        memory block
       \item $\mathit{off} = \Thead\mod m_{1}$: offset in memory block
@@
           \item Retrieve encoding pebble
-          \item Return bit with offset
+          \item Return $\mathit{off}$-th bit
         \end{itemize}
@@
 \begin{frame}
-  \frametitle{Recall: Mechanisms of simulation}
-  \begin{itemize}
-    \item Simulation of $M_{\text{Walk}}$ which explores at least $2^{m_{1}}$
-      distinct vertices \uncover<2->{\textcolor{green}{{\checkmark}}}
-    \item Identify \emph{distinct} vertices of the walk
-      \uncover<3->{\textcolor{green}{{\checkmark}}}
-    \item Read from and write to simulated tape \uncover<4->{\textcolor{green}{{\checkmark}}}
-    \item Preserve tape content through steps of simulated agent
-      \uncover<5->{\textcolor{green}{{\checkmark}}}
-  \end{itemize}
-  \uncover<6->{
+  \frametitle{Barrier size}
+  \begin{mdframed}
     \begin{theorem}
-      There is a constant $c\in\mathbb{N}$, such that for any graph $G$
-      with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$,
-      there exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates
-      the walk of $\mathcal{M}$ or explores $G$.
-    \end{theorem}
-  }
-\end{frame}
-
-\begin{frame}
-  \frametitle{Exploring graphs with $\log\log n$ pebbles}
-  \begin{theorem}
-    There is a constant $c\in\mathbb{N}$, such that for any graph $G$
-    with bounded degree and any $(s,p,2m)$ pebble machine $\mathcal{M}$,
-    there exists a $(cs,p+c,m)$ pebble machine $\mathcal{M}'$ that simulates
-    the walk of $\mathcal{M}$ or explores $G$.
-  \end{theorem}
-  \begin{center}
-    \begin{tikzpicture}
-      \node (d1) {};
-      \node[below=2 of d1] (d2) {};
-      \draw[->, bend right] (d1) to (d2);
-      \node[below right=0.8 and 1 of d1, rectangle,draw=black] {Apply simulation Theorem $\log\log n$ times};
-    \end{tikzpicture}
-  \end{center}
-  \begin{theorem}
-    Any bounded-degree graph on at most $n$ vertices can be explored using
-    $\mathcal{O}(\log\log n)$ pebbles and memory.
-  \end{theorem}
-\end{frame}
-
-\section{Limitations of pebble machines}
-\begin{frame}
-  \frametitle{Limitations of pebbles}
-  \begin{itemize}
-    \item Construct 3-regular graphs which agent $\mathcal{A}$ with $p$ pebbles
-      cannot traverse
-    \item Called $p$-barriers
-      \begin{center}
-        \resizebox{0.6\textwidth}{!}{\input{tikz/barrierint}}
-      \end{center}
-    \item $\mathcal{A}$ cannot traverse a $p$-barrier from $v_{1}$ or $v_{2}$
-      to $v_{3}$ or $v_{4}$ or vice versa using at most $p$ pebbles
-    \item Inductive construction of barriers
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Locality gadget}
-  \begin{itemize}
-    \item Replace edge by $(p-1)$-barrier
-    \item Enforce \enquote{locality} of pebbles
-      \begin{center}
-        \uncover<2->{\resizebox{0.8\textwidth}{!}{\input{tikz/locgadget}}}
-      \end{center}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \begin{theorem}
-    Given an $(r-1)$-barrier $B$ with $m$ vertices for an agent $\mathcal{A}$
-    with $p\geq r$ pebbles, we can construct an $r$-barrier $B'$ with
-    $\mathcal{O}(\binom{p}{r}\cdot m\cdot\alpha_{B}^{2})$ vertices for
-    $\mathcal{A}$.
-  \end{theorem}
-  \begin{itemize}
-    \item $\alpha_{B}$ is the amount of \enquote{local} configurations for
-      $\mathcal{A}$ with $r$ pebbles
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Barrier construction: Idea}
-  \begin{columns}
-    \column{0.5\textwidth}
-    \begin{itemize}
-      \item Subset of pebbles of cardinality $r$
-      \item Locality gadget as edges
-      \item Pebbles are local: configurations in macro vertex
-        $C_{1},\dots,C_{\alpha}$
-      \item Project $A$ to agent without pebbles $B$
-      \item $B$ has $\alpha$ states and traverses macro vertices
-    \end{itemize}
-    \column{0.5\textwidth}
-    \resizebox{\textwidth}{!}{\input{tikz/projection}}
-  \end{columns}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Barrier construction}
-  \begin{itemize}
-    \item $B$ has no pebbles and cannot traverse $0$-barrier
-    \item[$\rightarrow$] $p$-barrier for the chosen subset of pebbles:
-  \end{itemize}
-  \begin{center}
-    \resizebox{0.8\textwidth}{!}{\input{tikz/iterbarrier}}
-  \end{center}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Barrier base case}
-  \begin{theorem}[Fraigniaud et al.]
-    For any $q$ non cooperative $s$-state agents without pebbles, there
-    exists a 3-regular graph $G$ on $\mathcal{O}(qs)$ vertices with the
-    following property: There are two edges $\left\{v_{1},v_{2}\right\}$
-    and $\left\{v_{3},v_{4}\right\}$ in $G$, the first labeled 0, such
-    that any of the $q$ agents starting in $v_{1}$ or $v_{2}$ does not
-    traverse the edge $\left\{v_{3},v_{4}\right\}$.
-  \end{theorem}
-  \begin{itemize}
-    \item For agent $\mathcal{A}$ consider
-      $S = \left\{\mathcal{A}_{q}\mid q\in Q\right\}$
-    \item Since $|S| = |Q| = q$ there is a 0-barrier with $\mathcal{O}(s^{2})$
-      vertices
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Barrier}
-  \begin{theorem}
-    Given an $(r-1)$-barrier $B$ with $m$ vertices for an agent $\mathcal{A}$
-    with $p\geq r$ pebbles, we can construct an $r$-barrier $B'$ with
-    $\mathcal{O}(\binom{p}{r}\cdot m\cdot\alpha_{B}^{2})$ vertices for
-    $\mathcal{A}$.
-  \end{theorem}
-  \begin{center}
-    \resizebox{0.7\textwidth}{!}{\input{tikz/iterbarrier}}
-  \end{center}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Barrier size}
-  \begin{center}
-    \resizebox{\textwidth}{!}{\input{tikz/barriersize}}
-  \end{center}
-  \begin{theorem}
-    For $r\leq p$ and $s\geq 2^{p}$, the number of vertices of $r$-barrier
+      For $r\leq p$ and $s\geq 2^{p}$, the number of vertices of an $r$-barrier
       $B_{r}$ for the $s$-state agent $\mathcal{A}$ with $p$ pebbles is bounded
@@
     \end{theorem}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Lower pebble bound}
-  \begin{theorem}
-    For any constant $\epsilon > 0$, an agent with at most
-    $\mathcal{O}((\log n)^{1-\epsilon})$ bits of memory needs at least
-    $\Omega(\log\log n)$ distinguishable pebbles for exploring all
-    graphs on at most $n$ vertices.
-  \end{theorem}
-\end{frame}
-
-\section{Conclusion}
-\begin{frame}
-  \frametitle{Conclusion}
-  \begin{itemize}
-    \item Exploring graphs with $\mathcal{O}(\log\log n)$ pebbles and memory
-    \item Simulation via pebbles
-    \item Limitations of pebbles: Barrier construction
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
+  \end{mdframed}
   \begin{center}
-    \Huge Thank you for your attention.
+    \resizebox{\textwidth}{!}{\input{tikz/barriersize}}
   \end{center}

### 2016-05-12 tikz/moveex.tex
slides "done"

@@
 
-  \draw[edge] (0) to node[very near start, above] {0} node[very near end, above] {1} (1);
-  \draw[edge] (1) to node[very near start, below] {0} node[very near end, above] {1} (2);
-  \draw[edge,bend right] (2.north west) to node[very near start, right] {0} node[very near end, above] {2} (0);
-  \draw[edge] (0) to node[very near start, right] {1} node[very near end, left ] {0} (3);
+  \draw[edge] (0) to node[very near start, above] (l0) {0} node[very near end, above] (e0) {1} (1);
+  \draw[edge] (1) to node[very near start, below] (l1) {0} node[very near end, above] (e1) {1} (2);
+  \draw[edge,bend right] (2.north west) to node[very near start, right] (l2) {0} node[very near end, above] (e2) {2} (0);
+  \draw[edge] (0) to node[very near start, right] (l3) {1} node[very near end, left ] (e3) {0} (3);
   \draw[edge] (3) to node[very near start, above] {1} node[very near end, below] {1} (4);
@@
       \node [fit=(0), fill=green!50] (layer) {};%
+      \node [fit=(l0), fill=blue!50, inner sep=0pt] {};
   \end{scope}}
   \only<4-4>{\begin{scope}[on background layer]%
-      \node [fit=(3), fill=green!50] (layer) {};%
+      \node [fit=(1), fill=green!50] (layer) {};%
+      \node [fit=(l1), fill=blue!50, inner sep=0pt] {};
+      \node [fit=(e0), fill=red!50, inner sep=0pt] {};
   \end{scope}}
   \only<5-5>{\begin{scope}[on background layer]%
-      \node [fit=(4), fill=green!50] (layer) {};%
+      \node [fit=(2), fill=green!50] (layer) {};%
+      \node [fit=(l2), fill=blue!50, inner sep=0pt] {};
+      \node [fit=(e1), fill=red!50, inner sep=0pt] {};
   \end{scope}}
   \only<6-6>{\begin{scope}[on background layer]%
-      \node [fit=(3), fill=green!50] (layer) {};%
+      \node [fit=(0), fill=green!50] (layer) {};%
+      \node [fit=(l3), fill=blue!50, inner sep=0pt] {};
+      \node [fit=(e2), fill=red!50, inner sep=0pt] {};
   \end{scope}}
   \only<7-7>{\begin{scope}[on background layer]%
-      \node [fit=(4), fill=green!50] (layer) {};%
+      \node [fit=(3), fill=green!50] (layer) {};%
+      \node [fit=(e3), fill=red!50, inner sep=0pt] {};
   \end{scope}}

### 2016-05-12 tikz/portex.tex
slides "done"

@@
 
-  \draw[edge] (m1) to node[very near start, above] {\textcolor{green}{0}} (e1);
-  \draw[edge] (m1) to node[near start, left] {\textcolor{green}{2}} (e2);
+  \draw[edge] (m1) to node[very near start, above] {\textcolor{blue}{0}} (e1);
+  \draw[edge] (m1) to node[near start, left] {\textcolor{blue}{2}} (e2);
 
-  \draw[edge] (m2) to node[very near start, above] {\textcolor{green}{1}} (e3);
-  \draw[edge] (m2) to node[near start, right] {\textcolor{green}{2}} (e4);
+  \draw[edge] (m2) to node[very near start, above] {\textcolor{blue}{1}} (e3);
+  \draw[edge] (m2) to node[near start, right] {\textcolor{blue}{2}} (e4);
 
-  \draw[edge] (m1) to node[very near start, below] {\textcolor{green}{1}} node[very near end, above] {\textcolor{green}{0}} (m2);
+  \draw[edge] (m1) to node[very near start, below] {\textcolor{blue}{1}} node[very near end, above] {\textcolor{blue}{0}} (m2);
 \end{tikzpicture}

### 2016-05-12 tikz/regsim.tex
slides "done"

@@
   \uncover<3->{
-    \node[node] (r11) [below = 6cm of m1] {$0$};
-    \node[node] (r12) [above = 2cm of r11] {$1$};
-    \node[node] (r13) [below = 2cm of r11] {$2$};
+    \node[node] (r11) [below = 6cm of m1] {0};
+    \node[node] (r12) [above = 2cm of r11] {1};
+    \node[node] (r13) [below = 2cm of r11] {2};
 
-    \node[node] (l11) [below = 6cm of m3] {$0$};
-    \node[node] (l12) [above = 2cm of l11] {$1$};
-    \node[node] (l13) [below = 2cm of l11] {$2$};
+    \node[node] (l11) [below = 6cm of m3] {0};
+    \node[node] (l12) [above = 2cm of l11] {1};
+    \node[node] (l13) [below = 2cm of l11] {2};
 
     \node       (anker) [below = 6.5cm of m2] {};
-    \node[node] (mid0) [above right = 1cm and 1cm of anker] {$0$};
-    \node[node] (mid1) [below right = 1cm and 1cm of anker] {$1$};
-    \node[node] (mid2) [below = 3cm of anker] {$2$};
-    \node[node] (mid3) [below left = 1cm and 1cm of anker] {$3$};
-    \node[node] (mid4) [above left = 1cm and 1cm of anker] {$4$};
-    \node[node] (mid5) [above = 3cm of anker] {$5$};
+    \node[node] (mid0) [above right = 1cm and 1cm of anker] {0};
+    \node[node] (mid1) [below right = 1cm and 1cm of anker] {1};
+    \node[node] (mid2) [below = 3cm of anker] {2};
+    \node[node] (mid3) [below left = 1cm and 1cm of anker] {3};
+    \node[node] (mid4) [above left = 1cm and 1cm of anker] {4};
+    \node[node] (mid5) [above = 3cm of anker] {5};
 

### 2016-05-12 presentation/main.tex
slides!

@@
 \usepackage{appendixnumberbeamer}
+\usepackage{url}
 
@@
         \begin{itemize}
+          \item $(Q,F,P,m,\delta,\din,\dout,q_{0})$
           \item $(s,p,m)$-pebble machine
-          \item $(Q,F,P,m,\delta,\din,\dout,q_{0})$
           \item<2-> $\din$: moving onto vertex
@@
 \begin{frame}
-  \frametitle{$3$-regularity}
+  \frametitle{$3$-Regularity}
   \begin{mdframed}[linecolor=purple]
-    Establish $3$-regularity
+    Establish $3$-Regularity
   \end{mdframed}
@@
       \draw[->, bend right] (d1) to (d2);
-      \node[rectangle, draw=green, below right=0.3 and 1 of d1]
+      \node[rectangle, draw=purple, below right=0.3 and 1 of d1]
         {3-Regularity};
@@
       \item \textcolor<4,9>{magenta}{Drop pebble $p_{\text{tmp}}$}
-      \item \textcolor<4,9>{magenta}{Store $\Twalk$ in $T'_{\text{walk}}$}
+      \item \textcolor<4,9>{magenta}{Store number of steps $M_{\text{walk}}$
+        executed}
       \item \textcolor<5,10>{magenta}{Restart $M_{\text{walk}}$}
@@
           until $p_{\text{tmp}}$ is observed}
-      \item \textcolor<19-20>{magenta}{If $\Twalk = T'_{\text{walk}}$ the
-          vertex is new (increase $\Tid$)}
+      \item \textcolor<19-20>{magenta}{Same amount of steps for
+        $M_{\text{walk}}$ to find $p_{\text{tmp}}$ $\rightarrow$ new vertex}
       \item \textcolor<7>{magenta}{Otherwise start over}
@@
     \begin{theorem}
+      For $r\leq p$ and $s\geq 2^{p}$, the number of vertices of an $r$-barrier
+      $B_{r}$ for the $s$-state agent $\mathcal{A}$ with $p$ pebbles is bounded
+      by $\mathcal{O}(s^{8^{r+1}})$.
+    \end{theorem}
+  \end{mdframed}
+  \begin{center}
+    \begin{tikzpicture}
+      \node (d1) {};
+      \node[below=1.5 of d1] (d2) {};
+      \draw[->, bend right] (d1) to (d2);
+    \end{tikzpicture}
+  \end{center}
+  \begin{mdframed}
+    \begin{theorem}
       For any constant $\epsilon > 0$, an agent with at most
@@
 \begin{frame}
+  \vspace{0.3\textheight}
   \begin{center}
-    \Huge Thank you for your attention.
+    {\Huge Thank you for your attention.}
   \end{center}
+  \vspace{0.35\textheight}
+  Slides and text on \url{https://github.com/weltoph/sem-pebbles}.
 \end{frame}

### 2016-05-12 paper/main.tex
references

@@
 \section{Introduction}
-In this work we present the main results from \cite{pebbles}. These are
+In this work we present the main results from \cite{pebbles}, i.e.
 how to systematically traverse graphs of a very large size by agents.
-Agents are located on vertices of the graph and move along the edges. Because
-the memory of the agents is very limited we allow agents to use a set of
-distinguishable tokens, called pebbles, which can be left on a vertex and
+Agents are initially located on a vertex of the graph and move along edges.
+Because the memory of the agents is very limited we allow agents to use a set
+of distinguishable tokens, called pebbles, which can be left on a vertex and
 recollected by another visit of the same vertex. As we will see this is a very
@@
 For the further course we assume the following: Firstly, the considered
-graphs are finite but huge and agents have limited memory and can
-therefore not compute the identifier of vertices which renders all vertices
-indistinguishable for the agents. Also, the degree of the vertices is bounded
-by a constant $\Delta$. For every vertex $v$ we assume that the connected edges
-can be locally enumerated with labels $0,\dots,d_{v} - 1$ where $d_{v}$ is the
-degree of $v$. These edge-labels are called ports and every edge has one port
-for both vertices it connects. Note that no relation between these ports is
-presumed.
+graphs are finite but very large and agents have limited memory. Therefore,
+agents can not compute the identifier of vertices which renders all vertices
+indistinguishable for these. Additionally, the degree of the vertices is
+bounded by a constant $\Delta$. For every vertex $v$ we assume that the
+connected edges can be locally enumerated with labels $0,\dots,d_{v} - 1$
+where $d_{v}$ is the degree of $v$. These edge-labels are called \emph{ports}
+and every edge has one port for each incident vertex. Note that no
+relation between these ports is presumed.
 
 \section{Graph Exploration}
-We begin this section by formally defining our agents in the form of
+We begin this section by formally defining the agents as
 \emph{pebble machines}. This definition closely follows the notion of Turing
-machines but adds mechanisms to model the movements of the agent.
+machines but adds mechanisms to model the movements of the agent as well as
+the management of pebbles.
 \begin{definition}[Pebble machine]
-  A $(s,p,m)$-\emph{pebble machine} $\mathcal{M}$ is defined as a tuple
+  An $(s,p,m)$-\emph{pebble machine} $\mathcal{M}$ is defined as a tuple
   $(Q,F,P,m,\delta,\din,\dout,q_{0})$ with
@@
     \item a function $\dout$ that describes the leaving of a vertex
-    \item an inital state $q_{0}$
+    \item an initial state $q_{0}$
   \end{enumerate}
-  where formally the computation function models the behaviour of the pebble
+  where the computation function $\delta$ models the behaviour of the pebble
   machine as
@@
   \end{equation*}
-  models how a pebble machine moves upon a vertex $v$ with
-  $\din(q,P_{1},P_{2},d,\ell) = q'$ where $q$ is the current state of
-  $\mathcal{M}$, $P_{1}$ is the set of pebbles it carries, $P_{2}$ the set
-  of pebbles located on $v$, $d$ is the degree of $v$ and $\ell$ the port
+  models how an agent moves upon a vertex $v$ where
+  $\din(q,P_{1},P_{2},d,\ell) = q'$ means that $q$ is the current state of
+  $\mathcal{M}, P_{1}$ is the set of pebbles it carries, $P_{2}$ the set
+  of pebbles located on $v, d$ is the degree of $v$ and $\ell$ the port
   through which $\mathcal{M}$ enters $v$. Then, $\mathcal{M}$ starts its
@@
   where $\dout(q) = (P_{1}, P_{2}, \ell)$ defines that $\mathcal{M}$ leaves
-  a vertex $v$ through port $\ell$, drops the pebbles in $P_{1}$ onto $v$
-  and carries the pebbles in $P_{2}$.
+  a vertex $v$ through port $\ell$, drops the pebbles in $P_{1}\subseteq P$
+  onto $v$ and carries the pebbles in $P_{2}\subseteq P$.
 
   We additionally demand consistency of pebbles, i.e. if the agent
-  carried the pebbles in $P_{1}\subseteq P$ and found the pebbles in
-  $P_{2}\subseteq P$ it is necessary that $P_{1}$ and $P_{2}$ are disjoint.
+  carried the pebbles in $P_{1}$ and found the pebbles in
+  $P_{2}$, then $P_{1}$ and $P_{2}$ are disjoint.
   Furthermore, if the agent leaves carrying $P'_{1}$ and dropping $P'_{2}$
@@
   \label{fig:blowup}
+  \vspace{-0.5cm}
 \end{wrapfigure}
@@
 $\ell_{i}$. Then, an agent following $e$ leaves through port
-$(\ell_{i} + e_{i}) \mod d_{v}$. We define $\ell_{0} = 0$ and the notion
-$(e_{0},\dots,e_{k})^{\ast}$ for periodic exploration sequences. We call an
+$(\ell_{i} + e_{i}) \mod d_{v}$. We define $\ell_{0} = 0$ and use
+$(e_{0},\dots,e_{k})^{\ast}$ for periodic exploration sequences, i.e. that
+the $(k+1)$-th step is again $e_{0}$. We call an
 exploration sequence universal for a class of graphs if an agent following
@@
 
-Beginning from the following result of \cite{logspacealg} we present how we can
-obtain an $(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine that performs
-a closed walk of at least $n$ distinct vertices in any graph with bounded
-degree.
-\begin{thm}[Reingold]
+Beginning from the following result of \citeauthor{logspacealg}
+\cite{logspacealg} we present how we can obtain an
+$(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine that defines an agent
+which performs a closed walk of at least $n$ distinct vertices in any graph
+with bounded degree.
+\begin{thm}[Reingold \cite{logspacealg}]
   \label{thm:logalg}
@@
 \end{thm}
-At first we show that an agent which follows a periodic exploration sequence
+First we show that an agent which follows a periodic exploration sequence
 moves along a closed walk.
@@
 \begin{proof}
-  Consider a graph with vertices of the form $(v,\ell,i)$
-  denoting that the agent entered in the original graph vertex $v$ through port
-  $\ell$ and that the next element of the exploration sequence is $i$.
-  Edges are given by the next movement of the agent following the exploration
-  sequence from the configuration of the current vertex $(v,\ell,i)$. It is
-  easy to see that for a vertex $(v,\ell,i)$
-  the next vertex is deterministically chosen and therefore is unique.
+  Consider a graph with vertices of the form $(v,\ell,i)$ and
+  edges, given by the next movement of an agent following the exploration
+  sequence if it entered $v$ through port $\ell$ and performs the $i$-th step
+  of the exploration sequence. It is easy to see that for a vertex $(v,\ell,i)$
+  the next vertex is unique.
   Furthermore we argue that there is at most one predecessor for every vertex.
   Examine two predecessor $(v',\ell',i')$ and $(v'',\ell'',i'')$ for
-  $(v,\ell,i)$. Both enter $v$ by $\ell$ thus $v' = v''$.  It is clear that
-  $i' + 1 \mod k = i = i'' + 1 \mod k$ which implies $i' = i''$. Concludingly,
-  $\ell' + e_{i'} \mod d_{v'} = \ell'' + e_{i''} \mod d_{v''}$ and since
+  $(v,\ell,i)$. Both enter $v$ by $\ell$, thus $v' = v''$. It is clear that
+  $i'$ and $i''$ are equal because for both the next index considered index of
+  the exploration sequence is $i$. Finally, $\ell' + e_{i'} \mod d_{v'} =
+  \ell'' + e_{i''} \mod d_{v''}$ and since
   $v' = v''$, $e_{i'} = e_{i''}$ and $\ell',\ell'' < d_{v'} = d_{v''}$,
@@
   Because now every vertex has one outgoing and at most one incoming edge 
-  a walk starting in $(v_{0},0,0)$ must loop
-  because there are only finitly many triples $(v,\ell,i)$ but the agent moves
-  infinitly. Projecting this walk to the first component yields a closed walk
+  a walk starting in $(v_{0},0,0)$ must eventually lead to $(v_{0},0,0)$ again,
+  because there are only finitely many triples $(v,\ell,i)$ but the agent moves
+  infinitely. Projecting this walk to the first component yields a closed walk
   on the original graph.
 \end{proof}
-In the following we can show that the algorithm from Theorem \ref{thm:logalg}
+In the following we show that the algorithm from Theorem \ref{thm:logalg}
 can be adapted to output a periodic universal exploration sequence for every
-graph with up to $n$ vertices.
-\begin{lem}[Periodic Universal Lemma]
+graph with at most $n$ vertices.
+\begin{lem}
   \label{lem:pul}
@@
   \label{fig:3reg}
+  \vspace{-0.5cm}
 \end{wrapfigure}
@@
   Let $\mathcal{M}$ be the Turing machine(TM) of Theorem \ref{thm:logalg}.
-  At first we show that the exploration sequence produced by $\mathcal{M}$ is
+  First we show that the exploration sequence produced by $\mathcal{M}$ is
   universal for every graph with at most $n$ vertices. Assume there
-  is a 3-regular graph with $n_{0} < n$ vertices for which $\mathcal{M}$
-  produces a non-universal exploration sequence. Note that $n_{0}$ is even
-  because every 3-regular graph has an even number of nodes by the Handshaking
-  Lemma. Then, there is a vertex $v$ which is not explored. We can now
-  repeatedly transform $v$ into a clique of three vertices with degree three
-  (see Figure \ref{fig:blowup}).
+  is a 3-regular graph with $n_{0} < n$ vertices which the exploration
+  sequence produced by $\mathcal{M}$ does not explore. Note that $n_{0}$ is
+  even because every 3-regular graph has an even number of vertices by the
+  Handshaking Lemma. Then, there is a vertex $v$ which is not explored. We can
+  now repeatedly transform $v$ into a clique of three vertices with degree
+  three (see Figure \ref{fig:blowup}).
   Thus, we added two vertices which are also not explored. This can be iterated
@@
   Secondly, we show that we can construct a TM $\mathcal{M}'$ which simulates
-  $\mathcal{M}$ until it produced a exploration sequence of length
+  $\mathcal{M}$ until it produces an exploration sequence of length
   $k = 3n\cdot c$ where $c$ is the number of configurations of $\mathcal{M}$.
@@
   for any 3-regular graph with $n$ vertices. If we assume that it is not, we
-  can conclude that we loop in a set of vertices $V'$ for which $|V'|<n$. By a
+  can conclude that we loop in a set of vertices $V'$ with $|V'|<n$. By a
   combinatorial argument we see that the produced exploration sequence $e$
   of $\mathcal{M}$ always loops in $V'$ because an agent following
-  $e$ would have entered a vertex twice by the same port whilst $\mathcal{M}$
+  $e$ would enter a vertex twice by the same port whilst $\mathcal{M}$
   is in the same configuration both times.
@@
   \label{thm:pebblewalk}
-  There exists a $(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine
+  There exists a\\ $(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine
   that moves along a closed walk and either explores the graph or visits
@@
 \begin{proof}[Proof-Sketch]
-  The TM constructed in Lemma \ref{lem:pul} is used as the desired pebble
-  machine but first the graph has to be transformed to be 3-regular.
-  We refer therefore to Figure \ref{fig:3reg} which shows how every vertex $v$
+  The TM constructed in Lemma \ref{lem:pul} is used as pebble
+  machine after the graph is transformed to be 3-regular.
+  We refer to Figure \ref{fig:3reg} which shows how every vertex $v$
   can be replaced by a gadget with $3\cdot d_{v}$ vertices of degree three. It
@@
 \section{Simulation}
-In the following we present the most interesting result from
-\cite{pebbles}: A simulation of a pebble machine which allows to store
+In the following we present a crucial result from
+\cite{pebbles} which is a simulation of a pebble machine which allows to store
 the tape content of the simulated pebble machine as pebbles placed on a
-walk within a graph.
+walk within a given graph.
 \begin{thm}
@@
   vertex $v$ of $\omega$ with a pebble and check if $v$ is
-  traversed by a new run of $\mathcal{M}_{\text{walk}}$ in fewer steps. If so
+  traversed by a new run of $\mathcal{M}_{\text{walk}}$ in fewer steps. If so,
   $v$ is not a new distinct vertex.
@@
   $\left\lfloor \frac{\Thead}{m_{1}}\right\rfloor$ is extracted. Then the
-  corresponding $(\Thead\mod m_{1})$-th bit is the desired bit. If this bit is
+  corresponding $(\Thead\mod m_{1})$-th bit is the bit under the current
+  head-position of the simulated machine. If this bit is
   altered the corresponding pebble can be moved according to the new state of
@@
       $2^{m_{1}}=2^{3}=8$ distinct vertices are used for the simulation but the
-    walk can be longer (as indicated by the dotted connection from $7$ to $0$).}
+    walk can be longer (as indicated by the dotted connection from $7$ to $0$).
+  }
     \label{fig:tapesim}
@@
   This concludes the intuition on how the tape of a pebble machine can be
-  simulated by a set of pebbles.
+  simulated by a set of pebbles. Each of these pebbles store a state by their
+  placement in $\omega$ and can be managed to read and write from the tape.
+  Furthermore the tape content can be preserved through movements of the
+  simulated machine.
 \end{proof}
@@
 there are 3-regular graphs that any agent with $p$ pebbles cannot traverse.
-Such graphs are called $p$-barriers.
+Such graphs are called $p$-\emph{barriers}.
 
 The construction of a barrier is done iteratively and relies on a result from
-\cite{0barrier} which is used to obtain an initial $0$-barrier.
+\citeauthor{0barrier} \cite{0barrier} which is used to obtain an initial
+$0$-barrier.
 \begin{lem}
@@
   For any subset of pebbles of cardinality $r$ we can use $B$ to apply the
-  locality construction and obtaining a graph $G(B)$. For $G(B)$ we can argue
+  locality construction and obtain a graph $G(B)$. For $G(B)$ we can argue
   using Lemma \ref{lem:loc} that $\mathcal{A}$ has only a limited
-  amount of configurations within a macro vertex. Let $\alpha_{B}$ be the
-  amount of these configurations. We can now project $\mathcal{A}$ to a pebble
-  machine without pebbles $\mathcal{B}$ with $\alpha_{B}$ states which only
-  traverses macro vertices. Since $\mathcal{B}$ cannot use any pebbles we can
-  obtain a barrier $C$ for it by Lemma \ref{lem:0bar}. Then, we can argue that
-  $C(B)$ is the desired barrier for $\mathcal{A}$ which uses only the chosen
-  subset of pebbles. For all ${p}\choose{r}$ possible subsets of pebbles a
-  barrier can be obtained as described above. Connecting these barriers gives
-  the desired barrier $B'$.
+  number of configurations within a macro vertex. Let $\alpha_{B}$ be the
+  number of such configurations. Since the next macro vertex $\mathcal{A}$
+  traverses is entirely dependent on the current configuration of $\mathcal{A}$
+  we can project $\mathcal{A}$ to a pebble machine without pebbles
+  $\mathcal{B}$ with $\alpha_{B}$ states which traverses macro vertices as
+  $\mathcal{A}$ traverses macro vertices.
+  Since $\mathcal{B}$ cannot use any pebbles we can
+  obtain a $0$-barrier $C$ for it by Lemma \ref{lem:0bar}. Then, we can argue
+  that $C(B)$ is the desired barrier for $\mathcal{A}$ which uses only the
+  chosen subset of pebbles. In this manner a barrier for every ${p}\choose{r}$
+  possible subsets of pebbles be obtained. Connecting these barriers gives
+  the desired barrier $B'$. For the given bound of the vertices we refer to
+  \cite{pebbles}.
 \end{proof}
-For the given bound of the vertices we refer to \cite{pebbles}. The
-analysis there contains a thorough combinatorial analysis of the amount of
-vertices for barriers which we do not present here but which leads to the
-following theorem.
+With a thorough combinatorial analysis of the amount of vertices for barriers
+as it is performed in \cite{pebbles} the following theorem can be shown.
 \begin{thm}
@@
 \end{thm}
-
 Using this theorem it is possible to show that any agent with sub-logarithmic
@@
 \end{thm}
-
 For this result it is essential that from a $p$-barrier with $m$
-vertices for an agent with $p$ pebbles we can construct a trap for this agent
-with $2m+4$ vertices. Due to its technical nature we omit the proof.
+vertices for an agent $\mathcal{A}$ with $p$ pebbles we can construct a
+\emph{trap} for $\mathcal{A}$, i.e. a graph which $\mathcal{A}$ cannot
+traverse entirely, with $2m+4$ vertices.
 
 \section{Conclusion}
-In this work we presented the idea of pebble machines for graph exploration
+We presented the idea of pebble machines for graph exploration
 as discussed in \cite{pebbles}. We focus mainly on the simulation of
@@
 on a closed walk strikes as a very interesting approach. Furthermore, it is
-also possible to find limitations of this approach in the form of barriers.
+also possible to find limitations of this approach in the form of barriers,
+specifically that every agent with sub-logarithmic memory needs
+$\Omega(\log\log n)$ pebbles to explore a graph with $n$ vertices. For agents
+with $\mathcal{O}(\log\log n)$ memory $\Theta(\log\log n)$ pebbles are
+necessary to explore graphs with $n$ vertices.
 

### 2016-05-13 paper/main.tex
slides done

@@
-\documentclass[oneside]{scrartcl}
-
-\usepackage[utf8]{inputenc}
-
-\usepackage{epigraph}
-\usepackage[autostyle,german=guillemets]{csquotes}
-\usepackage[ngerman, english]{babel}
-\usepackage[style=numeric,backend=biber]{biblatex}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{todonotes}
-\usepackage{mdframed}
-\usepackage{wrapfig}
-
-\newtheorem{thm}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{lem}{Lemma}
-\newtheorem{prop}{Proposition}
-
-\addbibresource{bibliography.bib}
-
-\DeclareMathOperator{\din}{\delta_{\mathit{in}}}
-\DeclareMathOperator{\dout}{\delta_{\mathit{out}}}
-\DeclareMathOperator{\Tid}{T_{\text{id}}}
-\DeclareMathOperator{\Tsteps}{T_{\text{steps}}}
-\DeclareMathOperator{\Twalk}{T_{\text{walk}}}
-\DeclareMathOperator{\Thead}{T_{\text{head}}}
-
-\input{tikz/settings}
-
-\begin{document}
-
-\setlength{\epigraphwidth}{0.7\textwidth}
-\setquotestyle{german}
-
-\title{Exploring graphs with pebbles}
-\subtitle{A \emph{Grimm} idea}
-\author{Christoph Welzel}
-\maketitle
-
-\epigraph{Und als der volle Mond aufgestiegen war, so nahm Hänsel sein %
-Schwesterchen an der Hand und ging den Kieselsteinen nach, die schimmerten %
-wie neu geschlagene Batzen und zeigten ihnen den Weg.}%
-{\emph{Hänsel und Gretel}\\Brüder Grimm}
-
-\setquotestyle{english}
-\section{Introduction}
-In this work we present the main results from \cite{pebbles}, i.e.
-how to systematically traverse graphs of a very large size by agents.
-Agents are initially located on a vertex of the graph and move along edges.
-Because the memory of the agents is very limited we allow agents to use a set
-of distinguishable tokens, called pebbles, which can be left on a vertex and
-recollected by another visit of the same vertex. As we will see this is a very
-beneficial extension since it is possible to obtain a very low memory footprint
-for the agents while preserving the exploration range.
-
-\section{Preliminaries}
-For the further course we assume the following: Firstly, the considered
-graphs are finite but very large and agents have limited memory. Therefore,
-agents can not compute the identifier of vertices which renders all vertices
-indistinguishable for these. Additionally, the degree of the vertices is
-bounded by a constant $\Delta$. For every vertex $v$ we assume that the
-connected edges can be locally enumerated with labels $0,\dots,d_{v} - 1$
-where $d_{v}$ is the degree of $v$. These edge-labels are called \emph{ports}
-and every edge has one port for each incident vertex. Note that no
-relation between these ports is presumed.
-
-\section{Graph Exploration}
-We begin this section by formally defining the agents as
-\emph{pebble machines}. This definition closely follows the notion of Turing
-machines but adds mechanisms to model the movements of the agent as well as
-the management of pebbles.
-\begin{definition}[Pebble machine]
-  An $(s,p,m)$-\emph{pebble machine} $\mathcal{M}$ is defined as a tuple
-  $(Q,F,P,m,\delta,\din,\dout,q_{0})$ with
-  \begin{enumerate}
-    \item a finite set of states $Q$ with cardinality $s$
-    \item a finite set of final states $F\subseteq Q$
-    \item a finite set of distinguishable pebbles $P$ with cardinality $p$
-    \item the length $m$ of the available memory tape
-    \item a computation function $\delta$
-    \item a function $\din$ that describes the movement onto a vertex
-    \item a function $\dout$ that describes the leaving of a vertex
-    \item an initial state $q_{0}$
-  \end{enumerate}
-  where the computation function $\delta$ models the behaviour of the pebble
-  machine as
-  \begin{equation*}
-    \delta\colon (Q\setminus F)\times\left\{0,1\right\}\rightarrow
-    Q\times\left\{0,1\right\}\times\left\{L,R\right\}
-  \end{equation*}
-  with the typical understanding of the computation of a Turing machine.
-  Furthermore
-  \begin{equation*}
-    \din\colon Q\times 2^{P}\times 2^{P}\times
-    \left\{0,\dots,\Delta - 1\right\}\times\left\{0,\dots,\Delta - 1\right\}
-    \rightarrow Q
-  \end{equation*}
-  models how an agent moves upon a vertex $v$ where
-  $\din(q,P_{1},P_{2},d,\ell) = q'$ means that $q$ is the current state of
-  $\mathcal{M}, P_{1}$ is the set of pebbles it carries, $P_{2}$ the set
-  of pebbles located on $v, d$ is the degree of $v$ and $\ell$ the port
-  through which $\mathcal{M}$ enters $v$. Then, $\mathcal{M}$ starts its
-  computation according to $\delta$ in state $q'$.  On the other hand $\dout$
-  is defined as
-  \begin{equation*}
-    \dout\colon Q
-    \rightarrow 2^{P}\times 2^{P}\times \left\{0,\dots,\Delta - 1\right\}
-  \end{equation*}
-  where $\dout(q) = (P_{1}, P_{2}, \ell)$ defines that $\mathcal{M}$ leaves
-  a vertex $v$ through port $\ell$, drops the pebbles in $P_{1}\subseteq P$
-  onto $v$ and carries the pebbles in $P_{2}\subseteq P$.
-
-  We additionally demand consistency of pebbles, i.e. if the agent
-  carried the pebbles in $P_{1}$ and found the pebbles in
-  $P_{2}$, then $P_{1}$ and $P_{2}$ are disjoint.
-  Furthermore, if the agent leaves carrying $P'_{1}$ and dropping $P'_{2}$
-  those sets are disjoint and $P_{1}\cup P_{2} = P'_{1}\cup P'_{2}$.
-\end{definition}
-
-\begin{wrapfigure}{r}{0.4\textwidth}
-  \begin{center}
-    \resizebox{0.3\textwidth}{!}{\input{tikz/blowup}}
-  \end{center}
-  \caption{Replace vertex by a 3-clique preserving 3-regularity.}
-  \label{fig:blowup}
-  \vspace{-0.5cm}
-\end{wrapfigure}
-In order to describe the movement of an agent we introduce the notion of an
-exploration sequence $e = e_{0}, e_{1},\dots$ for agents which defines relative
-movements.
-Let $\ell = \ell_{0},\ell_{1},\dots$ be a sequence of variables.
-$\ell_{i}$ denotes that the $i$-th visited vertex is entered through port
-$\ell_{i}$. Then, an agent following $e$ leaves through port
-$(\ell_{i} + e_{i}) \mod d_{v}$. We define $\ell_{0} = 0$ and use
-$(e_{0},\dots,e_{k})^{\ast}$ for periodic exploration sequences, i.e. that
-the $(k+1)$-th step is again $e_{0}$. We call an
-exploration sequence universal for a class of graphs if an agent following
-it explores any graph of that class.
-
-Beginning from the following result of \citeauthor{logspacealg}
-\cite{logspacealg} we present how we can obtain an
-$(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine that defines an agent
-which performs a closed walk of at least $n$ distinct vertices in any graph
-with bounded degree.
-\begin{thm}[Reingold \cite{logspacealg}]
-  \label{thm:logalg}
-  There is an $\mathcal{O}(\log n)$-space algorithm producing a universal
-  exploration sequence for any regular graph on $n$ vertices.
-\end{thm}
-First we show that an agent which follows a periodic exploration sequence
-moves along a closed walk.
-\begin{lem}[Closed Walk Lemma]
-  An agent following an exploration sequence of the form
-  $(e_{0},\dots,e_{k-1})^{\ast}$ in an undirected graph moves along a closed
-  walk.
-\end{lem}
-\begin{proof}
-  Consider a graph with vertices of the form $(v,\ell,i)$ and
-  edges, given by the next movement of an agent following the exploration
-  sequence if it entered $v$ through port $\ell$ and performs the $i$-th step
-  of the exploration sequence. It is easy to see that for a vertex $(v,\ell,i)$
-  the next vertex is unique.
-  Furthermore we argue that there is at most one predecessor for every vertex.
-  Examine two predecessor $(v',\ell',i')$ and $(v'',\ell'',i'')$ for
-  $(v,\ell,i)$. Both enter $v$ by $\ell$, thus $v' = v''$. It is clear that
-  $i'$ and $i''$ are equal because for both the next index considered index of
-  the exploration sequence is $i$. Finally, $\ell' + e_{i'} \mod d_{v'} =
-  \ell'' + e_{i''} \mod d_{v''}$ and since
-  $v' = v''$, $e_{i'} = e_{i''}$ and $\ell',\ell'' < d_{v'} = d_{v''}$,
-  $\ell' = \ell''$ follows.
-  Because now every vertex has one outgoing and at most one incoming edge 
-  a walk starting in $(v_{0},0,0)$ must eventually lead to $(v_{0},0,0)$ again,
-  because there are only finitely many triples $(v,\ell,i)$ but the agent moves
-  infinitely. Projecting this walk to the first component yields a closed walk
-  on the original graph.
-\end{proof}
-In the following we show that the algorithm from Theorem \ref{thm:logalg}
-can be adapted to output a periodic universal exploration sequence for every
-graph with at most $n$ vertices.
-\begin{lem}
-  \label{lem:pul}
-  There exists an $\mathcal{O}(\log n)$-space algorithm producing a universal
-  exploration sequence $(e_{0},\dots,e_{k-1})^{\ast}$ for any 3-regular graph
-  with at most $n$ vertices.
-\end{lem}
-\begin{wrapfigure}{r}{0.5\textwidth}
-  \flushright{\resizebox{0.4\textwidth}{!}{\input{tikz/regtrans}}}
-  \caption{Illustration how to transform any graph to a 3-regular graph.}
-  \label{fig:3reg}
-  \vspace{-0.5cm}
-\end{wrapfigure}
-\begin{proof}
-  Let $\mathcal{M}$ be the Turing machine(TM) of Theorem \ref{thm:logalg}.
-  First we show that the exploration sequence produced by $\mathcal{M}$ is
-  universal for every graph with at most $n$ vertices. Assume there
-  is a 3-regular graph with $n_{0} < n$ vertices which the exploration
-  sequence produced by $\mathcal{M}$ does not explore. Note that $n_{0}$ is
-  even because every 3-regular graph has an even number of vertices by the
-  Handshaking Lemma. Then, there is a vertex $v$ which is not explored. We can
-  now repeatedly transform $v$ into a clique of three vertices with degree
-  three (see Figure \ref{fig:blowup}).
-  Thus, we added two vertices which are also not explored. This can be iterated
-  until there are $n$ vertices. All the added vertices are not explored in a
-  graph with $n$ vertices contradicting Theorem \ref{thm:logalg}.
-
-  Secondly, we show that we can construct a TM $\mathcal{M}'$ which simulates
-  $\mathcal{M}$ until it produces an exploration sequence of length
-  $k = 3n\cdot c$ where $c$ is the number of configurations of $\mathcal{M}$.
-  $\mathcal{M}'$ outputs now $(e_{0},\dots,e_{k-1})^{\ast}$ which is universal
-  for any 3-regular graph with $n$ vertices. If we assume that it is not, we
-  can conclude that we loop in a set of vertices $V'$ with $|V'|<n$. By a
-  combinatorial argument we see that the produced exploration sequence $e$
-  of $\mathcal{M}$ always loops in $V'$ because an agent following
-  $e$ would enter a vertex twice by the same port whilst $\mathcal{M}$
-  is in the same configuration both times.
-\end{proof}
-These lemmata are used in \cite{pebbles} to give the following theorem.
-\begin{thm}
-  \label{thm:pebblewalk}
-  There exists a\\ $(\mathcal{O}(1),0,\mathcal{O}(\log n))$-pebble machine
-  that moves along a closed walk and either explores the graph or visits
-  at least $n$ distinct vertices, for any graph with bounded degree.
-\end{thm}
-\begin{proof}[Proof-Sketch]
-  The TM constructed in Lemma \ref{lem:pul} is used as pebble
-  machine after the graph is transformed to be 3-regular.
-  We refer to Figure \ref{fig:3reg} which shows how every vertex $v$
-  can be replaced by a gadget with $3\cdot d_{v}$ vertices of degree three. It
-  is also noteworthy that this transformation can be done with
-  $\mathcal{O}(\log n)$ memory: Because of the regular structure of the
-  transformation (moving along port 0 or 1 stays in the gadget and only
-  moving along port 2 changes the actual vertex). For details we refer to
-  \cite{pebbles}.
-\end{proof}
-
-\section{Simulation}
-In the following we present a crucial result from
-\cite{pebbles} which is a simulation of a pebble machine which allows to store
-the tape content of the simulated pebble machine as pebbles placed on a
-walk within a given graph.
-\begin{thm}
-  \label{thm:simulation}
-  There is a constant $c\in\mathbb{N}$, such that for any graph $G$ with
-  bounded degree and any $(s,p,2m)$-pebble machine $\mathcal{M}$, there
-  exists a $(cs,p+c,m)$-pebble machine $\mathcal{M}'$ that simulates the
-  walk of $\mathcal{M}$ or explores $G$.
-\end{thm}
-\begin{proof}[Proof-Sketch]
-  For a detailed description of mechanisms of the simulation we refer to
-  \cite{pebbles}. At this point we present the conceptional ideas but encourage
-  interested readers to look up the details.
-
-  We separate the tape of the simulated machine into memory blocks of size
-  $m_1$. With Theorem \ref{thm:pebblewalk} there is a
-  $(\mathcal{O}(1),0,\mathcal{O}(m_{1}))$-pebble machine
-  $\mathcal{M}_{\text{walk}}$ to perform a closed walk $\omega$ with
-  $2^{m_{1}}$ distinct vertices. We use a pebble to mark the beginning vertex
-  of this walk. Every memory block can now be represented by
-  a pebble which encodes the block by its placement on $\omega$ (see
-  Figure \ref{fig:tapesim}).
-
-  Because the vertices are indistinguishable it is necessary to find a
-  mechanism to enumerate distinct vertices in $\omega$ otherwise the state of
-  pebbles might be ambiguous. This can be achieved by always marking the next
-  vertex $v$ of $\omega$ with a pebble and check if $v$ is
-  traversed by a new run of $\mathcal{M}_{\text{walk}}$ in fewer steps. If so,
-  $v$ is not a new distinct vertex.
-
-  The head position of the simulated machine is stored in a variable $\Thead$.
-  In order to access this memory cell the state of the pebble with index
-  $\left\lfloor \frac{\Thead}{m_{1}}\right\rfloor$ is extracted. Then the
-  corresponding $(\Thead\mod m_{1})$-th bit is the bit under the current
-  head-position of the simulated machine. If this bit is
-  altered the corresponding pebble can be moved according to the new state of
-  the memory block by $2^{(\Thead\mod m_{1})}$ indices on $\omega$.
-
-  Finally, if the simulated machine executes a movement, it is necessary to
-  carry the tape content along. Therefore the vertex $v'$ the machine moves
-  onto is marked with a pebble and $\mathcal{M}_{\text{walk}}$ is used to find
-  a new closed walk $\omega'$ starting in $v'$. Then all encoding pebbles are
-  moved to the corresponding distinct vertex in $\omega'$ to preserve their
-  states. (Note that $\mathcal{M}_{\text{walk}}$ gives a walk with at least
-  $2^{m_{1}}$ distinct vertices for every starting vertex).
-  \begin{figure}
-    \begin{center}
-      \resizebox{0.6\textwidth}{!}{\input{tikz/tapesim}}
-    \end{center}
-    \caption{Illustration how to simulate the tape of a pebble machine by
-      placing pebbles on a closed walk where $m_{1} = 3$. Note that the first
-      $2^{m_{1}}=2^{3}=8$ distinct vertices are used for the simulation but the
-    walk can be longer (as indicated by the dotted connection from $7$ to $0$).
-  }
-    \label{fig:tapesim}
-  \end{figure}
-  This concludes the intuition on how the tape of a pebble machine can be
-  simulated by a set of pebbles. Each of these pebbles store a state by their
-  placement in $\omega$ and can be managed to read and write from the tape.
-  Furthermore the tape content can be preserved through movements of the
-  simulated machine.
-\end{proof}
-
-As Theorem \ref{thm:pebblewalk} yields a $(c,0,c\cdot\log n)$ pebble machine
-that explores a given graph we can now repeatedly apply the simulation
-from Theorem \ref{thm:simulation} (precisely $\log\log n$ times) and obtain
-a $(c'^{\log\log n}\cdot c, \log\log n\cdot c', c)$-pebble machine exploring
-the graph as the following theorem from \cite{pebbles} states.
+theorem from \cite{pebbles} states.
 \begin{thm}

### 2016-05-13 presentation/main.tex
slides done

@@
 \begin{frame}
-  \frametitle{Outlook}
+  \frametitle{Introduction}
   \begin{itemize}
@@
     \begin{itemize}
+      \item Undirected
       \item Finite, but huge
-      \item Undirected
       \item Indistinguishable vertices:
@@
       An agent following an exploration sequence of the form
-      $(e_{1},\dots,e_{k})^{\ast}$ moves along a closed walk.
+      $(e_{0},\dots,e_{k-1})^{\ast}$ moves along a closed walk.
     \end{lemma}
@@
         There exists an $\mathcal{O}(\log n)$-space algorithm producing a
-        universal exploration sequence $(e_{1},\dots,e_{k})^{\ast}$ for any
+        universal exploration sequence $(e_{0},\dots,e_{k-1})^{\ast}$ for any
         $3$-regular graph with at most $n$ vertices.
@@
   \vspace{0.35\textheight}
-  Slides and text on \url{https://github.com/weltoph/sem-pebbles}.
+  Slides and report on \url{https://github.com/weltoph/sem-pebbles}.
 \end{frame}
